### 2014-06-22 Articles/article.tex
Ajout squelette preuves résultat analytique pour une itération.

\documentclass[english,12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage[autolanguage]{numprint}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%

\title{Sparse associative memories}
\author{L}
\date{
	}
%

\renewcommand{\le}{\leqslant}
\renewcommand{\epsilon}{\varepsilon}
\renewcommand{\Re}{\textrm{Re}}
\renewcommand{\ge}{\geqslant}
%\newcommand{\sgn}{\textrm{le signe de }}
\newcommand{\E}{\mathcal{E}}
\newcommand{\V}{\vect{\mathcal{V}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\z}[1]{\Z/#1\Z}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\U}{\mathbb{U}}
\newcommand{\f}{\widehat{f}}
\newcommand{\e}[1]{e^{-2 \pi i #1}}
\newcommand{\ex}[1]{e^{2 \pi i #1}}
\renewcommand{\L}[1]{L^{#1} (\R )}
\newcommand{\leg}[2]{\left(\dfrac{#1}{#2}\right)}

\newcommand{\inte}[1]{\int_\mathbb{R} #1 d\lambda}
\newcommand{\intex}{\int_\mathbb{R}}
\newcommand{\dl}{d\lambda}
\newcommand{\conv}[2]{#1 \ast #2}

\newcommand{\vect}[1]{\overrightarrow{#1}}
\newcommand{\disp}[1]{\displaystyle{#1}}

\setcounter{secnumdepth}{3} %pour la numérotation subsubsection
\setcounter{tocdepth}{3} %pour la numérotation dans la table de matières
\renewcommand{\theenumi}{\roman{enumi})}
\renewcommand{\thepart}{\Alph{part}}
%\renewcommand{\thechapter}{\arabic{chapter}}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\arabic{subsection}}
\renewcommand{\thesubsubsection}{\alph{subsubsection}}

\newcommand{\fonction}[5]{\begin{array}{cllll}
#1 & : & #2 & \longrightarrow & #3 \\
&    & #4 & \longmapsto & #5 \end{array}}
\newcommand{\fonc}[3]{\begin{array}{lllll}
#1: & #2 & \mapsto & \displaystyle{#3}\end{array}}
\newcommand{\app}[3]{
	#1 : #2 \mapsto \displaystyle{#3}}
\newcommand{\fonct}[3]{\begin{array}{ccccc}
#1: & #2 & \longrightarrow & \displaystyle{#3}\end{array}}
\newcommand{\pent}[1]{\lfloor #1 \rfloor}
\newcommand{\ent}[2]{
	%\comp{#3}{\N}{#1\leqslant #3 \leqslant #2}
	[\![#1\,;\,#2]\!]
	}
\newcommand{\entnb}[1]{
	%\comp{#2}{\N}{#1 \leqslant #2}
	[\![#1\,;\,+\infty[\![
	}
\newcommand{\entr}[2]{
	%\comp{#3}{\Z}{#1\leqslant #3 \leqslant #2}
	[\![#1\,;\,#2]\!]
	}
\newcommand{\entrnb}[1]{
	%\comp{#2}{\Z}{#2 \leqslant #1}
	]\!]-\infty\,;\,#1]\!]
	}

% Le point-virgule bien espacé
\newcommand{\pv}{\ensuremath{\, ; }}
% Les intervalles
   % fermé - fermé
   \newcommand{\interff}[2]{\ensuremath{\left[ #1 \pv #2 \right]}}
   % fermé - ouvert
   \newcommand{\interfo}[2]{\ensuremath{\left[ #1 \pv #2 \right[}}
   % ouvert - fermé
   \newcommand{\interof}[2]{\ensuremath{\left] #1 \pv #2 \right]}}
   % ouvert - ouvert
   \newcommand{\interoo}[2]{\ensuremath{\left] #1 \pv #2 \right[}}

\theoremstyle{definition}
\newtheorem{theoreme}{Theorem}
\renewcommand{\thetheoreme}{\arabic{section}.\arabic{theoreme}}

\newcommand{\comp}[3]{\left\{
	#1\,;\, #1\in #2 \, /\, #3
	\right\}}
\newcommand{\param}[2]{\left\{
	#1\, /\, #2
	\right\}}

\begin{document}

	\maketitle%
	%\section*{Introduction}

	number of neurons per cluster $l$

	number of clusters $c$

	number of erased clusters $c_e$

	number of messages : $m$

	number of activities per cluster : $a$

	density : $d$

	edge : $(i, j)$

	probability for $i$ and $j$ to be active in their respective clusters for one message : $\frac{a}{l}$

	probability of the edge	not being added in the network for one message : $1 - \left(\frac{a}{l}\right)^2$

	\[ d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^m \]

	probability for a vertex $v$ to achieve the maximum score, that is to mean $a(c-c_e)$ : $d^	{a(c-c_e)}$

	probability for a vertex $v$	not to achieve the maximum : $1 - d^	{a(c-c_e)}$

	probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum : $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$

	probabilities for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective cluster : $\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)}$

	Whence error rate is : \[P_{err} = 1 -	\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)} \]

	The analytical result agree with the simulations.

	For one iteration, winner takes all is the same as winners take all.

	Winners take all better with errors instead of erasures.

	\nocite{*}
	%\nocite{*}
	%\bibliographystyle{alpha-fr} % Le style est mis entre crochets.
         \bibliography{bibli}
\end{document}

### 2014-06-22 Articles/article.tex
...

@@
 
-	For one iteration, winner takes all is the same as winners take all.
+	For one iteration, winner takes all is the same as $a$-winners take all.
 
-	Winners take all better with errors instead of erasures.
+	For multiple iterations $a$-winner take all is an improvement.
+
+	"$a$-Winners take all" better than "winner takes all" with errors instead of erasures.
 

### 2014-06-22 test.jl

@@ -15,7 +15,7 @@ function choisit(d, s)
 		if !haskey(field, "values")
 			res
 		else
-			cat(1, res, field["values"])
+			cat(1, field["values"], res)
 		end
 	end
 end

### 2014-06-22 Articles/article.tex
Simulations + correction article.tex

@@
 
+	gap with density in simulations : under $1$ percent
+
 	probability for a vertex $v$ to achieve the maximum score, that is to mean $a(c-c_e)$ : $d^	{a(c-c_e)}$
@@
 
-	The analytical result agree with the simulations.
+	The simulations agree with the analytical result.
 
-	For one iteration, winner takes all is the same as $a$-winners take all.
+	For one iteration (for erasures, not for errors), winner takes all is the same as $a$-winners take all.
 

### 2014-06-23 Articles/article.tex
...
Essai psi : bof

@@
 \newcommand{\leg}[2]{\left(\dfrac{#1}{#2}\right)}
-
-\newcommand{\inte}[1]{\int_\mathbb{R} #1 d\lambda}
-\newcommand{\intex}{\int_\mathbb{R}}
-\newcommand{\dl}{d\lambda}
-\newcommand{\conv}[2]{#1 \ast #2}
 
@@
 
+	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
+
+	\newpage
+	Spéculations en Français :
+
+	Peut-être un intérêt pour cluter based associative memories build from unreliable storage : si une arête porte moins d'info, on peut peut-être en supprimer plus (mais rajout ?!)
+
+	Marche un petit peu, mais pas forcément significatif : à tester plus en détail
+
 	\nocite{*}

### 2014-06-23 parse.jl

@@ -39,9 +39,9 @@ function parse_commandline()
 			   default = 4
 
 			   "--proba-cons", "-p"
-			   help = "Probability of adding connection."
+			   help = "Probability of adding connection or dropping connection after learning."
 			   arg_type = Float64
-			   default = 1.0
+			   default = 0.0
 
 			   "--proba-des"
 			   help = "Probability of dropping connection."

### 2014-06-23 sam.jl

@@ -110,7 +110,7 @@ end
 
 # l, c, m and useBitArray have the same meaning as above
 # messages is an array that represents the messages the output network is storing.
-function create_network(l, c, m, messages, sparseMessages, p_cons = 1.0, degree = 0, activities = 1)# ; useBitArray = false )
+function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree = 0, activities = 1)# ; useBitArray = false )
 	const n = l * c
 	#if !useBitArray
 		network = zeros(Bool,n,n)
@@ -159,6 +159,21 @@ function create_network(l, c, m, messages, sparseMessages, p_cons = 1.0, degree 
 		end
 	end
 
+	if p_cons > 0.0
+		for j=1:n
+			for i=1:n
+				if rand(Float64) <= p_cons
+					# Bon opérateur pour faire cette opération sur les booléens et les entiers à la fois ? (Au cas où on changerait le type du réseau.)
+					network[i, j] = (if network[i, j] == 1
+										0
+									else
+										1
+									end)
+				end
+			end
+		end
+	end
+
 	for j=1:c
 		network[(j-1)*l+1:j*l, (j-1)*l+1:j*l] = 0
 	end
@@ -186,7 +201,7 @@ end
 	#end
 
 # This function is a commodity for interactive purpose.
-function create_both(l, c, m, p_cons = 1.0, degree = 0, activities = 1) # ; useBitArray = false)
+function create_both(l, c, m, p_cons = 0.0, degree = 0, activities = 1) # ; useBitArray = false)
 	@time messages, sparseMessages, l2, alphabet_size = create_messages(l, c, m, activities) #, useBitArray = useBitArray)
 	@time network = create_network(l2, c, m, messages, sparseMessages, p_cons, degree, activities) #, useBitArray = useBitArray)
 	return (messages, sparseMessages, network, l2, alphabet_size)
@@ -351,7 +366,7 @@ end
 # fsum is the rule to use in order to recover the message. It modifies "input" in place.
 # returns the error rate of the procedure and the mean of the number of iterations
 # Careful : declare_degree is not the degree per nodes ! The degree will be c-1-declared_degree
[…]

### 2014-06-23 test.jl

@@ -25,14 +25,14 @@ function init_file(fileprefix, dir = "results")
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
 	const suffix = ".csv" #"$(fsum)__$(fcorrupt)"
 	const filename = "$(dir)/$(fileprefix)$suffix"
-	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy\n"
+	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta\n"
 	open(filename, "a") do file
 		write(file, firstline)
 	end
 	return filename
 end
 
-function enregistre(filename ; trials=10, l=128, c=8, m=5000, ugamma = 1, erasures=4 , iterations = 4, tests=1000, fsum=Sam.sum_of_sum!, fcorrupt = Sam.erase_clusters!, nowrite = false, dir = "results", p_cons = 1.0, p_des = 0.0, degree = degree, activities = 1, winners = 1, pool_size = 1)
+function enregistre(filename ; trials=10, l=128, c=8, m=5000, ugamma = 1, erasures=4 , iterations = 4, tests=1000, fsum=Sam.sum_of_sum!, fcorrupt = Sam.erase_clusters!, nowrite = false, dir = "results", p_cons = 0.0, p_des = 0.0, degree = degree, activities = 1, winners = 1, pool_size = 1)
 	for i=1:trials
 		@time res = Sam.output_test(l, c, m, ugamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners, pool_size)
 		if !nowrite

### 2014-06-23 sam.jl
Correction

@@ -411,7 +411,8 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 		binomial_annoncee =  binomial(l, activities)
 	catch    # Rien à faire.
 	end
-	efficacy = (1 - res[1]) * res[4]
+	pretrieved = 1 - res[1]
+	efficacy = pretrieved * res[4]
 	p = erasures/c
 	b = (fcorrupt == erase_clusters!)
 	cap = (if b 
@@ -419,8 +420,8 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 	else 
 		1 - p * log2(1/p) - (1- p) * log2(1/(1-p)) 
 	end)
-	proportion = m * res[1]
-	eta = ( 1 - res[4] ) * proportion
+	proportion = m * pretrieved
+	eta = res[4] * proportion # efficiency times proportion
 	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities binomial_annoncee winners pool_size efficacy (efficacy/cap) proportion eta]
 end
 

### 2014-06-23 Articles/article.tex
...

@@
 
-	probabilities for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective cluster : $\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)}$
+	probability for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective cluster : $\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)}$
 

### 2014-06-23 test.jl

@@ -20,6 +20,10 @@ function choisit(d, s)
 	end
 end
 
+macro assigne(s, v)
+	esc(:($(convert(Symbol, s)) = $v))
+end
+
 function init_file(fileprefix, dir = "results")
 	#i = hash((l, c, erasures, m, tests, "$fsum", ugamma))
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
@@ -71,7 +75,8 @@ if bconfig
 
 	@time for (iexp, experiment) in enumerate(experiments)
 		for (k, v) in experiment
-			eval(quote $(convert(Symbol, k)) = $v end)
+			#eval(quote $(convert(Symbol, k)) = $v end)
+			@assigne k v
 		end
 		#function_params = experiment["function_params"]
 		#network_params = experiment["network_params"]
@@ -84,7 +89,8 @@ if bconfig
 
 		## On pourrait déclarer tout cela avec de la métaprog :  eval( quote $(convert(Symbol, chaine)) = valeur end) : défaut -> le programme dépend du json mais moins de boulot
 		for (k, v) in network_params
-			eval(quote $(convert(Symbol, string("v", k))) = $(choisit(network_params, k)) end)
+			#eval(quote $(convert(Symbol, string("v", k))) = $(choisit(network_params, k)) end)
+			@assigne string("v", k) choisit(network_params, k)
 		end
 	#	vl = choisit(network_params, "l")
 	#	vc = choisit(network_params, "c")

### 2014-06-23 test.jl
Fin exp + préparation prochaine exp

@@ -75,8 +75,10 @@ if bconfig
 
 	@time for (iexp, experiment) in enumerate(experiments)
 		for (k, v) in experiment
+			@eval  $(convert(Symbol, k)) = $v 
+			
 			#eval(quote $(convert(Symbol, k)) = $v end)
-			@assigne k v
+			#@assigne k v
 		end
 		#function_params = experiment["function_params"]
 		#network_params = experiment["network_params"]
@@ -89,8 +91,10 @@ if bconfig
 
 		## On pourrait déclarer tout cela avec de la métaprog :  eval( quote $(convert(Symbol, chaine)) = valeur end) : défaut -> le programme dépend du json mais moins de boulot
 		for (k, v) in network_params
+			@eval  $(convert(Symbol, string("v", k))) = $(choisit(network_params, k))
+
 			#eval(quote $(convert(Symbol, string("v", k))) = $(choisit(network_params, k)) end)
-			@assigne string("v", k) choisit(network_params, k)
+			#@assigne string("v", k) choisit(network_params, k)
 		end
 	#	vl = choisit(network_params, "l")
 	#	vc = choisit(network_params, "c")

### 2014-06-23 sam.jl
Correction exp (balyage rapide)

@@ -421,7 +421,7 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 		1 - p * log2(1/p) - (1- p) * log2(1/(1-p)) 
 	end)
 	proportion = m * pretrieved
-	eta = res[4] * proportion # efficiency times proportion
+	eta = res[4] * pretrieved # efficiency times proportion # m already in res[4] == eff
 	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities binomial_annoncee winners pool_size efficacy (efficacy/cap) proportion eta]
 end
 

### 2014-06-23 astat.r
Ajout eff alternative pour comparer à l'autre papier.

@@ -37,6 +37,7 @@ spec = matrix(c(
 'ordstep', NA, 2, "double",
 'maxefficiency', 'E', 2, "double",
 'maxactivities', 'A', 2, "double",
+'pcons', 'p', 2, "double",
 'maxabs', NA, 2, "double",
 'maxord', NA, 2, "double",
 'minabs', NA, 2, "double",
@@ -74,6 +75,7 @@ if(!is.null(opt$fsum)) { data = subset(data, fsum == opt$fsum) }
 if(!is.null(opt$fcorrupt)) { data = subset(data, fcorrupt == opt$fcorrupt) }
 if(!is.null(opt$optwinners)) { data = subset(data, winners == activities) }
 if(!is.null(opt$poolsize)) { data = subset(data, poolsize == opt$poolsize) }
+if(!is.null(opt$pcons)) { data = subset(data, pcons == opt$pcons) }
 if(!is.null(opt$minpoolsize)) { data = subset(data, poolsize >= opt$minpoolsize) }
 if(!is.null(opt$maxefficiency)) { data = subset(data, efficiency <= opt$maxefficiency) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }

### 2014-06-23 sam.jl

@@ -308,7 +308,7 @@ function estimate_efficiency(l, c, m, alphabet_size, activities = 1)
 		info_alphabet = sum(log2((l-activities+1) : l)) - sum(log2(1:activities))				
 	end
 
-	2m * (c * info_alphabet - log2(m) + 1)/(c*(c-1)*l^2) ##1 == log2(2) == 1, this is where the term comes from (2nd order)
+	2m * (c * info_alphabet - log2(m) + 1)/(c*(c-1)*l^2),  2m * c * info_alphabet / (c*(c-1)*l^2) ##1 == log2(2) == 1, this is where the term comes from (2nd order)
 end
 
 
@@ -375,7 +375,7 @@ function test_network(l_init = 128, c = 8, m = 5000, gamma = 1, erasures = 4, it
 	println("Messages created and translated.")
 	dens = density(l, c, network)
 	println("Learning done.\nThe density of the network is : $(dens).")
-	eff = estimate_efficiency(l, c, m, alphabet_size, activities)
+	eff, aeff = estimate_efficiency(l, c, m, alphabet_size, activities)
 	println("Approximate efficiency : $eff")
 	const erasedNeuron = (if fsum == sum_of_max! 1 else 0 end)
 	# Computing the number of successful corrections in tests simulations and the total number of iterations (in parallel)
@@ -391,7 +391,7 @@ function test_network(l_init = 128, c = 8, m = 5000, gamma = 1, erasures = 4, it
 	errorRate = 1 - score[1]/tests
 	meanIter = score[2]/tests
 	println("\nError rate is : $errorRate\nMean number of iterations : $meanIter\n")
-	return [ errorRate, meanIter, dens, eff ]
+	return [ errorRate, meanIter, dens, eff, aeff ]
 end
 
 const dict_rules = [ 0 => sum_of_sum!, 1 => sum_of_max!, 2 => mix_of_rules! ]
@@ -422,7 +422,8 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 	end)
 	proportion = m * pretrieved
 	eta = res[4] * pretrieved # efficiency times proportion # m already in res[4] == eff
-	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities binomial_annoncee winners pool_size efficacy (efficacy/cap) proportion eta]
+	aeta = res[5] * pretrieved
[…]

### 2014-06-23 test.jl

@@ -29,7 +29,7 @@ function init_file(fileprefix, dir = "results")
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
 	const suffix = ".csv" #"$(fsum)__$(fcorrupt)"
 	const filename = "$(dir)/$(fileprefix)$suffix"
-	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta\n"
+	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta\n"
 	open(filename, "a") do file
 		write(file, firstline)
 	end

### 2014-06-23 sam.jl
Fin séries expériences, début nouvelle

@@ -400,7 +400,7 @@ const dict_corrupt = [ 0 => erase_clusters!, 1 => corrupt_clusters!, 2 => add_on
 
 function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons = 0.0, p_des = 0.0, degree = 0, activities = 1, winners = 1, pool_size = 1)
 	#res = mean(map( x -> test_network(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners), [1:pool_size])) ### Pas efficace, pourquoi ?
-	res = zeros(4)
+	res = zeros(5)
 	for i=1:pool_size 
 		res += test_network(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners)
 	end

### 2014-06-23 sam.jl
Introduction difficulté de la question.

@@ -423,7 +423,9 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 	proportion = m * pretrieved
 	eta = res[4] * pretrieved # efficiency times proportion # m already in res[4] == eff
 	aeta = res[5] * pretrieved
-	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities binomial_annoncee winners pool_size efficacy (efficacy/cap) proportion eta aeta ]
+	peta = eta * c / (c - erasures)
+	paeta = aeta * c / (c - erasures)
+	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities binomial_annoncee winners pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta]
 end
 
 #function set_proba(pr)

### 2014-06-23 test.jl

@@ -29,7 +29,7 @@ function init_file(fileprefix, dir = "results")
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
 	const suffix = ".csv" #"$(fsum)__$(fcorrupt)"
 	const filename = "$(dir)/$(fileprefix)$suffix"
-	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta\n"
+	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta\n"
 	open(filename, "a") do file
 		write(file, firstline)
 	end

### 2014-06-23 sam.jl
...

@@ -308,7 +308,7 @@ function estimate_efficiency(l, c, m, alphabet_size, activities = 1)
 		info_alphabet = sum(log2((l-activities+1) : l)) - sum(log2(1:activities))				
 	end
 
-	2m * (c * info_alphabet - log2(m) + 1)/(c*(c-1)*l^2),  2m * c * info_alphabet / (c*(c-1)*l^2) ##1 == log2(2) == 1, this is where the term comes from (2nd order)
+	2m * (c * info_alphabet - log2(m) + 1)/(c*(c-1)*l^2),  2m * c * info_alphabet / (c*(c-1)*l^2), info_alphabet ##1 == log2(2) == 1, this is where the term comes from (2nd order)
 end
 
 
@@ -375,7 +375,7 @@ function test_network(l_init = 128, c = 8, m = 5000, gamma = 1, erasures = 4, it
 	println("Messages created and translated.")
 	dens = density(l, c, network)
 	println("Learning done.\nThe density of the network is : $(dens).")
-	eff, aeff = estimate_efficiency(l, c, m, alphabet_size, activities)
+	eff, aeff, info_alphabet = estimate_efficiency(l, c, m, alphabet_size, activities)
 	println("Approximate efficiency : $eff")
 	const erasedNeuron = (if fsum == sum_of_max! 1 else 0 end)
 	# Computing the number of successful corrections in tests simulations and the total number of iterations (in parallel)
@@ -391,7 +391,7 @@ function test_network(l_init = 128, c = 8, m = 5000, gamma = 1, erasures = 4, it
 	errorRate = 1 - score[1]/tests
 	meanIter = score[2]/tests
 	println("\nError rate is : $errorRate\nMean number of iterations : $meanIter\n")
-	return [ errorRate, meanIter, dens, eff, aeff ]
+	return [ errorRate, meanIter, dens, eff, aeff, info_alphabet ]
 end
 
 const dict_rules = [ 0 => sum_of_sum!, 1 => sum_of_max!, 2 => mix_of_rules! ]
@@ -400,7 +400,7 @@ const dict_corrupt = [ 0 => erase_clusters!, 1 => corrupt_clusters!, 2 => add_on
 
 function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons = 0.0, p_des = 0.0, degree = 0, activities = 1, winners = 1, pool_size = 1)
[…]

### 2014-06-23 test.jl

@@ -29,7 +29,7 @@ function init_file(fileprefix, dir = "results")
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
 	const suffix = ".csv" #"$(fsum)__$(fcorrupt)"
 	const filename = "$(dir)/$(fileprefix)$suffix"
-	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta\n"
+	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta\n"
 	open(filename, "a") do file
 		write(file, firstline)
 	end

### 2014-06-23 astat.r
Ultra important : option -O pour tracer seulement lex max !!

@@ -42,6 +42,7 @@ spec = matrix(c(
 'maxord', NA, 2, "double",
 'minabs', NA, 2, "double",
 'minord', NA, 2, "double",
+'onlymax', 'O', 2, "logical",
 'noreg' , NA, 2, "logical"
 ), byrow=TRUE, ncol=4);
 opt = getopt(spec);
@@ -111,6 +112,20 @@ if (is.null(opt$title)) {
 }
 print(titre)
 X11()
+
+
+booleen <- is.null(c(opt$color, opt$size, opt$shape))
+if (!booleen) {
+	data$grp <- paste(data[,opt$color], data[,opt$size], data[,opt$shape])
+}
+
+if(!is.null(opt$onlymax)) {
+	data$sgrp <- paste(data$grp, data[,opt$abs])
+	sel <- ave(data[,opt$ord], data$sgrp, FUN=max) == data[,opt$ord]
+	data <- data[sel,]
+}
+
+
 #if(is.null(opt$lines)) {
 #	opt$lines <- TRUE 
 #} #else { ligne = "o" }
@@ -132,10 +147,6 @@ if(!is.null(opt$shape)) { qpl <- qpl + geom_point(aes(shape = factor(data[,opt$s
 if(!is.null(opt$box)) { qpl <- qpl + geom_boxplot(aes(fill = factor(data[,opt$abs]))) }
 
 
-booleen <- is.null(c(opt$color, opt$size, opt$shape))
-if (!booleen) {
-	data$grp <- paste(data[,opt$color], data[,opt$size], data[,opt$shape])
-}
 if(!is.null(opt$lines)) {
 	if (!booleen) {
 	qpl <- qpl + geom_line(aes(group = factor(data$grp)))
@@ -156,7 +167,7 @@ if(!is.null(opt$ordstep)) {
    qpl <- qpl + scale_y_continuous(aes(breaks = seq(0.0, 1.0, by = 0.1)))#, max(data[,opt$ord]), by = opt$ordstep))#,#pretty_breaks(n = length(data[,opt$abs]))) #min(data[,opt$ord])
 }
 qpl <- qpl + labs(title = titre)
-qpl #+stat_smooth()
+qpl #+ geom_bar()#+stat_smooth()
 #title(titre)
 temp <- data.frame(y = data[,1], x = data[,8])
 # fit non-linear model

### 2014-06-23 astat.r
Exp : conclusion peite amélioration dans ce cas sur de gros bruits.

@@ -25,6 +25,7 @@ spec = matrix(c(
 'winners' , 'W', 2, "integer",
 'poolsize' , 'P', 2, "integer",
 'minpoolsize' , NA, 2, "integer",
+'minpcons' , NA, 2, "double",
 'gamma' , 'g', 2, "integer",
 'iterations' , 'i', 2, "integer",
 'maxiterations' , 'I', 2, "integer",
@@ -77,6 +78,7 @@ if(!is.null(opt$fcorrupt)) { data = subset(data, fcorrupt == opt$fcorrupt) }
 if(!is.null(opt$optwinners)) { data = subset(data, winners == activities) }
 if(!is.null(opt$poolsize)) { data = subset(data, poolsize == opt$poolsize) }
 if(!is.null(opt$pcons)) { data = subset(data, pcons == opt$pcons) }
+if(!is.null(opt$minpcons)) { data = subset(data, pcons >= opt$minpcons) }
 if(!is.null(opt$minpoolsize)) { data = subset(data, poolsize >= opt$minpoolsize) }
 if(!is.null(opt$maxefficiency)) { data = subset(data, efficiency <= opt$maxefficiency) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }

### 2014-06-24 sam.jl
Exp ratées, nouvelles capacitées.

@@ -406,9 +406,9 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 	end
 	res /= pool_size
 
-	binomial_annoncee = 1
+	alphabet_size = 1
 	try
-		binomial_annoncee =  binomial(l, activities)
+		alphabet_size =  binomial(l, activities)
 	catch    # Rien à faire.
 	end
 	info_alphabet = res[6]
@@ -419,16 +419,18 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 	cap = (if b 
 		(1-p) 
 	else 
-		1 - p * log2(1/p) - (1- p) * log2(1/(1-p)) 
+		info_alphabet - p * (1 - 1/alphabet_size) * log2(alphabet_size/p) - (p/alphabet_size + (1- p)) * log2(1/(p/alphabet_size + (1-p))) 
 	end)
 	proportion = m * pretrieved
 	eta = res[4] * pretrieved # efficiency times proportion # m already in res[4] == eff
 	aeta = res[5] * pretrieved
-	peta = eta * c / (c - erasures)
+	peta = eta / cap
+	paeta = aeta / cap
+	ieta = eta / info_alphabet
+	iaeta = aeta / info_alphabet
 	ipeta = peta / info_alphabet
-	paeta = aeta * c / (c - erasures)
 	ipaeta = paeta / info_alphabet
-	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities binomial_annoncee winners pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta]
+	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size winners pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet ]
 end
 
 #function set_proba(pr)

### 2014-06-24 test.jl

@@ -29,7 +29,7 @@ function init_file(fileprefix, dir = "results")
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
 	const suffix = ".csv" #"$(fsum)__$(fcorrupt)"
 	const filename = "$(dir)/$(fileprefix)$suffix"
-	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta\n"
+	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta,ieta,iaeta,infoalphabet\n"
 	open(filename, "a") do file
 		write(file, firstline)
 	end

### 2014-06-24 Articles/article.tex
Fin exp + préparation prochaine exp
...

@@
 
-\title{Sparse associative memories}
+\title{Storing messages with neural multipartite cliques}
 \author{L}
@@
 \newcommand{\pent}[1]{\lfloor #1 \rfloor}
-\newcommand{\ent}[2]{
-	%\comp{#3}{\N}{#1\leqslant #3 \leqslant #2}
-	[\![#1\,;\,#2]\!]
-	}
-\newcommand{\entnb}[1]{
-	%\comp{#2}{\N}{#1 \leqslant #2}
-	[\![#1\,;\,+\infty[\![
-	}
-\newcommand{\entr}[2]{
-	%\comp{#3}{\Z}{#1\leqslant #3 \leqslant #2}
-	[\![#1\,;\,#2]\!]
-	}
-\newcommand{\entrnb}[1]{
-	%\comp{#2}{\Z}{#2 \leqslant #1}
-	]\!]-\infty\,;\,#1]\!]
-	}
 
@@
 	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
+	For one iteration, it is less efficient.
 
@@
 
-	Marche un petit peu, mais pas forcément significatif : à tester plus en détail
+	Marche un petit peu, mais pas forcément significatif : à tester plus en détail.
 
+	Marche mieux pour des bruits importants
+
+	$P(n_{v_c} = n_0) = {a c_k \choose n_0} (1-\psi)^{n_0} \psi ^ { a c_k - n_0 }$
+
+	$P_+ = \psi (1 - d) + (1 - \psi) d$
+
+	$P(n_v = x) = {a c_k \choose x} P_+^x (1-P_+)^{a c_k -x }$
+
+	\[P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \]
+
+	\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]
+
+	Sans tenir compte du choix au hasard si plus sont activés.
 	\nocite{*}
-	%\nocite{*}
-	%\bibliographystyle{alpha-fr} % Le style est mis entre crochets.
-         \bibliography{bibli}
+	\bibliographystyle{plain} % Le style est mis entre crochets.
+         \bibliography{bibli.bib}
 \end{document}

### 2014-06-24 astat.r
Tracé théorique + simulations + calculs

@@ -10,6 +10,7 @@ spec = matrix(c(
 'color', NA, 2, "character",
 'shape', NA, 2, "character",
 'size', NA, 2, "character",
+'lt', 'L', 2, "character",
 'box', NA, 2, "character",
 'fsum', 's', 2, "character",
 'fcorrupt', 'z', 2, "character",
@@ -44,6 +45,7 @@ spec = matrix(c(
 'minabs', NA, 2, "double",
 'minord', NA, 2, "double",
 'onlymax', 'O', 2, "logical",
+'thm', 'T', 2, "logical",
 'noreg' , NA, 2, "logical"
 ), byrow=TRUE, ncol=4);
 opt = getopt(spec);
@@ -118,7 +120,7 @@ X11()
 
 booleen <- is.null(c(opt$color, opt$size, opt$shape))
 if (!booleen) {
-	data$grp <- paste(data[,opt$color], data[,opt$size], data[,opt$shape])
+	data$grp <- paste(data[,opt$color], data[,opt$size], data[,opt$shape], data[,opt$lt])
 }
 
 if(!is.null(opt$onlymax)) {
@@ -151,7 +153,7 @@ if(!is.null(opt$box)) { qpl <- qpl + geom_boxplot(aes(fill = factor(data[,opt$ab
 
 if(!is.null(opt$lines)) {
 	if (!booleen) {
-	qpl <- qpl + geom_line(aes(group = factor(data$grp)))
+	qpl <- qpl + geom_line(aes(group = factor(data$grp)), linetype="dashed")
 #	if(!is.null(opt$color)) {
 #		qpl <- qpl + geom_line(aes(group = factor(data[,opt$color])))
 #	} else if(!is.null(opt$size)) {
@@ -162,6 +164,10 @@ if(!is.null(opt$lines)) {
 		qpl <- qpl + geom_line()
 	}
 }
+
+if(!is.null(opt$lt)) {
+	qpl <- qpl + scale_linetype(breaks = (data[,opt$lt]))
+}
 if(!is.null(opt$step)) {
    qpl <- qpl + scale_x_continuous( breaks = seq(0, max(data[,opt$abs]), by = opt$step))#, labels = abbreviate)#,#pretty_breaks(n = length(data[,opt$abs]))) #
 }
@@ -169,6 +175,18 @@ if(!is.null(opt$ordstep)) {
[…]

### 2014-06-24 astat.r
Courbes théoriques.

@@ -4,6 +4,7 @@ library(getopt)
 library(ggplot2)
 library(scales)
 
+library(plyr)
 
 spec = matrix(c(
 'file', 'f', 1, "character",
@@ -184,7 +185,22 @@ p <- function(d, l, c, ce, a) 1 - (1- d^(a * (c - ce)))^(ce * (l - a))
 po <- function(m, l, c, ce, a) p(dens(m, l, a), l, c, ce, a)
 
 if (!is.null(opt$thm)) {
-	qpl <- qpl + stat_function(fun = function(x) po(x, unique(data$l), unique(data$c), unique(data$erasures), unique(data$activities)))
+	#coefs <- data.frame(l = unique(data$l), c = unique(data$c), erasures = unique(data$erasures), activities = unique(data$activities))
+	#coeflines <- alply(as.matrix(coefs), 1, function(coef) { stat_function(fun=function(x){ po(x, l, c, erasures, 1)}) })
+	#qpl <- qpl + coeflines
+	for (l in unique(data$l)) {
+		for (c in unique(data$c)) {
+			for (erasures in unique(data$erasures)) {
+				for (activities in unique(data$activities)) {
+					print(activities)
+					qpl <- qpl + stat_function(fun = function(x) po(x, l, c, erasures, activities), color = "red")
+					#qpl
+					#message("Press Return To Continue")
+					#invisible(readLines("stdin", n=1))
+				}
+			}
+		}
+	}
 }
 
 qpl #+ geom_bar()#+stat_smooth()

### 2014-06-24 astat.r
Meilleur coloration via le script.

@@ -46,6 +46,7 @@ spec = matrix(c(
 'minabs', NA, 2, "double",
 'minord', NA, 2, "double",
 'onlymax', 'O', 2, "logical",
+'fcolor', NA, 2, "logical",
 'thm', 'T', 2, "logical",
 'noreg' , NA, 2, "logical"
 ), byrow=TRUE, ncol=4);
@@ -136,7 +137,13 @@ if(!is.null(opt$onlymax)) {
 #} #else { ligne = "o" }
 if(!is.null(opt$color)) {
 
-qpl <- qplot(data[,opt$abs], data[,opt$ord], ylab=opt$ord, xlab=opt$abs, main = "", color = data[,opt$color]) + labs(colour = opt$color)# + guides(fill = guide_colourbar(title=opt$color))#+ scale_colour_continuous(name=opt$color) #, size = data[,opt$size])#opt$color) # col="blue")
+if (!is.null(opt$fcolor)) {
+	cdata = factor(data[, opt$color])
+} else {
+	cdata <- data[,opt$color]
+}
+
+qpl <- qplot(data[,opt$abs], data[,opt$ord], ylab=opt$ord, xlab=opt$abs, main = "", color = cdata) + labs(colour = opt$color)# + guides(fill = guide_colourbar(title=opt$color))#+ scale_colour_continuous(name=opt$color) #, size = data[,opt$size])#opt$color) # col="blue")
 } else {qpl <- qplot(data[,opt$abs], data[,opt$ord], ylab=opt$ord, xlab=opt$abs, main = "")  }
 
 

### 2014-06-24 astat.r
Courbes

@@ -15,6 +15,8 @@ spec = matrix(c(
 'box', NA, 2, "character",
 'fsum', 's', 2, "character",
 'fcorrupt', 'z', 2, "character",
+'xlab', 'x', 2, "character",
+'ylab', 'y', 2, "character",
 'title', NA, 2, "character",
 'abs', NA, 2, "character",
 'ord', NA, 2, "character",
@@ -182,6 +184,13 @@ if(!is.null(opt$step)) {
 if(!is.null(opt$ordstep)) {
    qpl <- qpl + scale_y_continuous(aes(breaks = seq(0.0, 1.0, by = 0.1)))#, max(data[,opt$ord]), by = opt$ordstep))#,#pretty_breaks(n = length(data[,opt$abs]))) #min(data[,opt$ord])
 }
+if(!is.null(opt$xlab)) {
+	qpl <- qpl + xlab(opt$xlab)
+}
+if(!is.null(opt$ylab)) {
+	qpl <- qpl + ylab(opt$ylab)
+}
+
 qpl <- qpl + labs(title = titre)
 
 
@@ -200,7 +209,7 @@ if (!is.null(opt$thm)) {
 			for (erasures in unique(data$erasures)) {
 				for (activities in unique(data$activities)) {
 					print(activities)
-					qpl <- qpl + stat_function(fun = function(x) po(x, l, c, erasures, activities), color = "red")
+					qpl <- qpl + stat_function(fun = function(x) po(x, l, c, erasures, activities), color = "black")
 					#qpl
 					#message("Press Return To Continue")
 					#invisible(readLines("stdin", n=1))

### 2014-06-24 astat.r
Test formule

@@ -50,6 +50,7 @@ spec = matrix(c(
 'onlymax', 'O', 2, "logical",
 'fcolor', NA, 2, "logical",
 'thm', 'T', 2, "logical",
+'thd', NA, 2, "logical",
 'noreg' , NA, 2, "logical"
 ), byrow=TRUE, ncol=4);
 opt = getopt(spec);
@@ -214,6 +215,18 @@ if (!is.null(opt$thm)) {
 					#message("Press Return To Continue")
 					#invisible(readLines("stdin", n=1))
 				}
+			}
+		}
+	}
+}
+if (!is.null(opt$thd)) {
+	#coefs <- data.frame(l = unique(data$l), c = unique(data$c), erasures = unique(data$erasures), activities = unique(data$activities))
+	#coeflines <- alply(as.matrix(coefs), 1, function(coef) { stat_function(fun=function(x){ po(x, l, c, erasures, 1)}) })
+	#qpl <- qpl + coeflines
+	for (l in unique(data$l)) {
+		for (c in unique(data$c)) {
+			for (activities in unique(data$activities)) {
+				qpl <- qpl + stat_function(fun = function(x) dens(x, l, activities), color = "black")
 			}
 		}
 	}

### 2014-06-25 Articles/article.tex
Tracé théorique + simulations + calculs
...

@@
-\documentclass[english,12pt]{article}
+\documentclass[english,11pt,twocolumn]{article}
 \usepackage[utf8]{inputenc}
@@
 %
+%\usepackage[style=numeric,backend=bibtex]{biblatex}
+\pagestyle{myheadings}
 
-\title{Storing messages with neural multipartite cliques}
-\author{L}
+\title{Storing messages with multipartite neural cliques}
+\author{???}
 \date{
@@
 \renewcommand{\thetheoreme}{\arabic{section}.\arabic{theoreme}}
+\providecommand{\keywords}[1]{\textbf{Index terms---} #1}
 
@@
 
-	\maketitle%
-	%\section*{Introduction}
+	\maketitle
+
+	 \begin{abstract}
+	 ???
+	 \end{abstract}
+
+	\keywords{associative memory, error correcting code}
+
+	\section{Introduction}
+
+	\section{Networks of neural cliques}
+
+	\subsection{Learning messages}
+
+		\subsection{Retrieving messages}
+
+		\subsubsection{The "winner takes all" rule}
+
+		\subsubsection{The "$a$ winners take all" rule}
+
+		less biologically plausible rule
+
+		same algorithmic complexity
+
+	\section{Retrieval performance}
+
+		\subsection{Analytical results}
 
@@
 
-	The simulations agree with the analytical result.
+	The simulations agree with the analytical results for density and error rate.
 
@@
 
+	\subsection{Simulations}
+		Improves the retrieval rate for multiple iterations and/or corrupted messages.
+	\begin{figure}
+		\includegraphics[width=8.5cm]{densiteexemple.pdf}
+		\caption{Theoretical and empirical densities}
+	\end{figure}
+
+	\begin{figure}
+		\includegraphics[width=8.5cm]{comparaison_regles_pool5_a2c4l512e2}
+		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messagges, analytical result in continuous black}
+		\end{figure}
+
 	\newpage
@@
 	Peut-être un intérêt pour cluter based associative memories build from unreliable storage : si une arête porte moins d'info, on peut peut-être en supprimer plus (mais rajout ?!)
-
-	Marche un petit peu, mais pas forcément significatif : à tester plus en détail.
 
@@
 
-	\[P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \]
+	% À corriger avec sommes multiparties
+	%\[P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \]
 
-	\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]
+	%\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]
 
 	Sans tenir compte du choix au hasard si plus sont activés.
+
+	\section{Conclusion}
+
+	%Marche mieux pouur de petits c --> le faire sur le sparse ?
 	\nocite{*}

### 2014-06-25 astat.r

@@ -29,6 +29,7 @@ spec = matrix(c(
 'winners' , 'W', 2, "integer",
 'poolsize' , 'P', 2, "integer",
 'minpoolsize' , NA, 2, "integer",
+'minwinners' , NA, 2, "integer",
 'minpcons' , NA, 2, "double",
 'gamma' , 'g', 2, "integer",
 'iterations' , 'i', 2, "integer",
@@ -87,6 +88,7 @@ if(!is.null(opt$poolsize)) { data = subset(data, poolsize == opt$poolsize) }
 if(!is.null(opt$pcons)) { data = subset(data, pcons == opt$pcons) }
 if(!is.null(opt$minpcons)) { data = subset(data, pcons >= opt$minpcons) }
 if(!is.null(opt$minpoolsize)) { data = subset(data, poolsize >= opt$minpoolsize) }
+if(!is.null(opt$minwinners)) { data = subset(data, winners >= opt$minwinners) }
 if(!is.null(opt$maxefficiency)) { data = subset(data, efficiency <= opt$maxefficiency) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }

### 2014-06-25 sam.jl

@@ -430,7 +430,7 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 	iaeta = aeta / info_alphabet
 	ipeta = peta / info_alphabet
 	ipaeta = paeta / info_alphabet
-	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size winners pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet ]
+	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet ]
 end
 
 #function set_proba(pr)

### 2014-06-25 Articles/article.tex
...

@@
 
+	\subsection{Simulations}
+		Improves the retrieval rate for multiple iterations and/or corrupted messages.
+
 		The simulations agree with the analytical results for density and error rate.
@@
 
-	For multiple iterations $a$-winner take all is an improvement.
+	For multiple iterations $a$-winners take all is a significant improvement.
 
-	"$a$-Winners take all" better than "winner takes all" with errors instead of erasures.
+		"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
 
@@
 	For one iteration, it is less efficient.
-
-	\subsection{Simulations}
-		Improves the retrieval rate for multiple iterations and/or corrupted messages.
 	\begin{figure}

### 2014-06-25 astat.r
...

@@ -31,6 +31,7 @@ spec = matrix(c(
 'minpoolsize' , NA, 2, "integer",
 'minwinners' , NA, 2, "integer",
 'minpcons' , NA, 2, "double",
+'maxpcons' , NA, 2, "double",
 'gamma' , 'g', 2, "integer",
 'iterations' , 'i', 2, "integer",
 'maxiterations' , 'I', 2, "integer",
@@ -87,6 +88,7 @@ if(!is.null(opt$optwinners)) { data = subset(data, winners == activities) }
 if(!is.null(opt$poolsize)) { data = subset(data, poolsize == opt$poolsize) }
 if(!is.null(opt$pcons)) { data = subset(data, pcons == opt$pcons) }
 if(!is.null(opt$minpcons)) { data = subset(data, pcons >= opt$minpcons) }
+if(!is.null(opt$maxpcons)) { data = subset(data, pcons <= opt$maxpcons) }
 if(!is.null(opt$minpoolsize)) { data = subset(data, poolsize >= opt$minpoolsize) }
 if(!is.null(opt$minwinners)) { data = subset(data, winners >= opt$minwinners) }
 if(!is.null(opt$maxefficiency)) { data = subset(data, efficiency <= opt$maxefficiency) }

### 2014-06-25 astat.r
...

@@ -51,6 +51,7 @@ spec = matrix(c(
 'minord', NA, 2, "double",
 'onlymax', 'O', 2, "logical",
 'fcolor', NA, 2, "logical",
+'fsize', NA, 2, "logical",
 'thm', 'T', 2, "logical",
 'thd', NA, 2, "logical",
 'noreg' , NA, 2, "logical"
@@ -155,7 +156,13 @@ qpl <- qplot(data[,opt$abs], data[,opt$ord], ylab=opt$ord, xlab=opt$abs, main = 
 
 
 if(!is.null(opt$jitter)) { qpl <- qpl + geom_jitter() }
-if(!is.null(opt$size)) { qpl <- qpl + geom_point(aes(size = data[,opt$size])) + labs(size = opt$size) } # + scale_size(name=opt$size)  }
+if(!is.null(opt$size)) { 
+	if(!is.null(opt$fsize)) {
+		sdata = factor(data[, opt$size])
+	} else {
+		sdata = data[,opt$size]
+	}
+	qpl <- qpl + geom_point(aes(size = sdata)) + labs(size = opt$size) } # + scale_size(name=opt$size)  }
 if(!is.null(opt$shape)) { qpl <- qpl + geom_point(aes(shape = factor(data[,opt$shape])), size = 3) + labs(shape = opt$shape) }# + scale_shape(name=opt$shape)  }
 #if(!is.null(opt$color)) { qpl <- qpl + geom_point(colour = data[opt$color]) }
 

### 2014-06-25 astat.r
correction script

@@ -81,7 +81,13 @@ if(!is.null(opt$iterations)) { data = subset(data, iterations == opt$iterations)
 if(!is.null(opt$maxiterations)) { data = subset(data, maxiterations == opt$maxiterations) }
 if(!is.null(opt$erasures)) { data = subset(data, erasures == opt$erasures) }
 if(!is.null(opt$activities)) { data = subset(data, activities == opt$activities) }
-if(!is.null(opt$winners)) { data = subset(data, winners == opt$winners) }
+if(!is.null(opt$winners)) { 
+	if(opt$winners == 0) {
+		data = subset(data, winners == activities | winners == 0)
+	} else {
+		data = subset(data, winners == opt$winners)
+	}
+}
 if(!is.null(opt$tests)) { data = subset(data, tests == opt$tests) }
 if(!is.null(opt$fsum)) { data = subset(data, fsum == opt$fsum) }
 if(!is.null(opt$fcorrupt)) { data = subset(data, fcorrupt == opt$fcorrupt) }

### 2014-06-26 sam.jl
...

@@ -59,7 +59,7 @@ function create_messages(l, c, m, activities = 1)#; useBitArray = false)
 
 	const n = l * c
 	#if !useBitArray
-		#sparseMessages = spzeros(Uint8, m,n)
+		#sparseMessages = spzeros(Uint8, n,m)
 
 		sparseMessages = zeros(Bool,n, m)
 	#else	

### 2014-06-26 astat.r
...

@@ -44,6 +44,7 @@ spec = matrix(c(
 'ordstep', NA, 2, "double",
 'maxefficiency', 'E', 2, "double",
 'maxactivities', 'A', 2, "double",
+'mmiterations', NA, 2, "double",
 'pcons', 'p', 2, "double",
 'maxabs', NA, 2, "double",
 'maxord', NA, 2, "double",
@@ -101,6 +102,7 @@ if(!is.null(opt$minwinners)) { data = subset(data, winners >= opt$minwinners) }
 if(!is.null(opt$maxefficiency)) { data = subset(data, efficiency <= opt$maxefficiency) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }
+if(!is.null(opt$mmiterations)) { data = subset(data, maxiterations <= opt$mmiterations) }
 if(!is.null(opt$maxabs)) { data = subset(data, data[, opt$abs ] <= opt$maxabs) }
 if(!is.null(opt$minabs)) { data = subset(data, data[, opt$abs ] >= opt$minabs) }
 if(!is.null(opt$maxord)) { data = subset(data, data[, opt$ord ] <= opt$maxord) }

### 2014-06-26 test.jl

@@ -37,6 +37,7 @@ function init_file(fileprefix, dir = "results")
 end
 
 function enregistre(filename ; trials=10, l=128, c=8, m=5000, ugamma = 1, erasures=4 , iterations = 4, tests=1000, fsum=Sam.sum_of_sum!, fcorrupt = Sam.erase_clusters!, nowrite = false, dir = "results", p_cons = 0.0, p_des = 0.0, degree = degree, activities = 1, winners = 1, pool_size = 1)
+	@assert erasures <= c
 	for i=1:trials
 		@time res = Sam.output_test(l, c, m, ugamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners, pool_size)
 		if !nowrite

### 2014-06-27 astat.r
...

@@ -51,6 +51,7 @@ spec = matrix(c(
 'minabs', NA, 2, "double",
 'minord', NA, 2, "double",
 'onlymax', 'O', 2, "logical",
+'onlydrop', NA, 2, "logical",
 'fcolor', NA, 2, "logical",
 'fsize', NA, 2, "logical",
 'thm', 'T', 2, "logical",
@@ -107,6 +108,7 @@ if(!is.null(opt$maxabs)) { data = subset(data, data[, opt$abs ] <= opt$maxabs) }
 if(!is.null(opt$minabs)) { data = subset(data, data[, opt$abs ] >= opt$minabs) }
 if(!is.null(opt$maxord)) { data = subset(data, data[, opt$ord ] <= opt$maxord) }
 if(!is.null(opt$minord)) { data = subset(data, data[, opt$ord ] >= opt$minord) }
+if(!is.null(opt$onlydrop)) { data = subset(data, onlydrop == "true" | pcons == 0.0) } else { data = subset(data, !(onlydrop == "true") | pcons == 0.0) }
 #data <- subset(data, (is.null(opt$neurons) | l == opt$neurons) & (is.null(opt$clusters) | c == opt$clusters) & (is.null(opt$gamma) | gamma == opt$gamma) & (is.null(opt$messages) | m == opt$messages) )
 #data <- subset(x, (is.null(opt$neurons) || l == opt$neurons) & (is.null(opt$clusters) || c == opt$clusters) & (is.null(opt$gamma) || gamma == opt$gamma) & (is.null(opt$messages) || m == opt$messages) )
 #data <- subset(data, (l==opt$neurons & c==opt$clusters & m==opt$messages & gamma==opt$gamma))
@@ -257,19 +259,19 @@ temp <- data.frame(y = data[,1], x = data[,8])
 # fit non-linear model
 tryCatch({
 if(is.null(opt$noreg)) {
-mod <- nls(y ~ 1/(1+exp(a + b * x)), data = temp, start = list(a = 0, b = 0))
-#
-coef = coef(mod)
-a = coef[1]
-b = coef[2]
-print(coef)
-print("Middle :")
-print(-a/b)
-# add fitted curve
-#lines(temp$x, predict(mod, list(x = temp$x)))
-func <-function(x) 1/(1+exp(a+ b * x))
-#curve(func, from = 0, to = max(data$c), n = 300, add=TRUE, col=opt$color)
[…]

### 2014-06-27 parse.jl

@@ -109,6 +109,10 @@ function parse_commandline()
 			   help = "Scan on numbers of messages (hardcoded at the moment)."
 			   action = :store_true
 
+			   "--only_drop"
+			   help = "pcons is now only dropping and not adding edges."
+			   action = :store_true
+
 			   "--file"
 			   help = "Prefix of the output file."
 			   default = "clique_results"

### 2014-06-27 sam.jl

@@ -110,7 +110,7 @@ end
 
 # l, c, m and useBitArray have the same meaning as above
 # messages is an array that represents the messages the output network is storing.
-function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree = 0, activities = 1)# ; useBitArray = false )
+function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree = 0, activities = 1, only_drop = false)# ; useBitArray = false )
 	const n = l * c
 	#if !useBitArray
 		network = zeros(Bool,n,n)
@@ -164,7 +164,7 @@ function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree 
 			for i=1:n
 				if rand(Float64) <= p_cons
 					# Bon opérateur pour faire cette opération sur les booléens et les entiers à la fois ? (Au cas où on changerait le type du réseau.)
-					network[i, j] = (if network[i, j] == 1
+					network[i, j] = (if network[i, j] == 1 || only_drop
 										0
 									else
 										1
@@ -201,9 +201,9 @@ end
 	#end
 
 # This function is a commodity for interactive purpose.
-function create_both(l, c, m, p_cons = 0.0, degree = 0, activities = 1) # ; useBitArray = false)
+function create_both(l, c, m, p_cons = 0.0, degree = 0, activities = 1, only_drop = false) # ; useBitArray = false)
 	@time messages, sparseMessages, l2, alphabet_size = create_messages(l, c, m, activities) #, useBitArray = useBitArray)
-	@time network = create_network(l2, c, m, messages, sparseMessages, p_cons, degree, activities) #, useBitArray = useBitArray)
+	@time network = create_network(l2, c, m, messages, sparseMessages, p_cons, degree, activities, only_drop) #, useBitArray = useBitArray)
 	return (messages, sparseMessages, network, l2, alphabet_size)
 end
 
@@ -366,9 +366,9 @@ end
 # fsum is the rule to use in order to recover the message. It modifies "input" in place.
 # returns the error rate of the procedure and the mean of the number of iterations
 # Careful : declare_degree is not the degree per nodes ! The degree will be c-1-declared_degree
[…]

### 2014-06-27 test.jl

@@ -29,17 +29,17 @@ function init_file(fileprefix, dir = "results")
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
 	const suffix = ".csv" #"$(fsum)__$(fcorrupt)"
 	const filename = "$(dir)/$(fileprefix)$suffix"
-	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta,ieta,iaeta,infoalphabet\n"
+	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta,ieta,iaeta,infoalphabet,onlydrop\n"
 	open(filename, "a") do file
 		write(file, firstline)
 	end
 	return filename
 end
 
-function enregistre(filename ; trials=10, l=128, c=8, m=5000, ugamma = 1, erasures=4 , iterations = 4, tests=1000, fsum=Sam.sum_of_sum!, fcorrupt = Sam.erase_clusters!, nowrite = false, dir = "results", p_cons = 0.0, p_des = 0.0, degree = degree, activities = 1, winners = 1, pool_size = 1)
+function enregistre(filename ; trials=10, l=128, c=8, m=5000, ugamma = 1, erasures=4 , iterations = 4, tests=1000, fsum=Sam.sum_of_sum!, fcorrupt = Sam.erase_clusters!, nowrite = false, dir = "results", p_cons = 0.0, p_des = 0.0, degree = degree, activities = 1, winners = 1, pool_size = 1, only_drop = false)
 	@assert erasures <= c
 	for i=1:trials
-		@time res = Sam.output_test(l, c, m, ugamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners, pool_size)
[…]

### 2014-06-27 astat.r
Formulte trouvée ??

@@ -28,6 +28,7 @@ spec = matrix(c(
 'erasures' , 'e', 2, "integer",
 'winners' , 'W', 2, "integer",
 'poolsize' , 'P', 2, "integer",
+'degree' , 'd', 2, "integer",
 'minpoolsize' , NA, 2, "integer",
 'minwinners' , NA, 2, "integer",
 'minpcons' , NA, 2, "double",
@@ -95,6 +96,7 @@ if(!is.null(opt$fsum)) { data = subset(data, fsum == opt$fsum) }
 if(!is.null(opt$fcorrupt)) { data = subset(data, fcorrupt == opt$fcorrupt) }
 if(!is.null(opt$optwinners)) { data = subset(data, winners == activities) }
 if(!is.null(opt$poolsize)) { data = subset(data, poolsize == opt$poolsize) }
+if(!is.null(opt$degree)) { data = subset(data, degree == opt$degree) }
 if(!is.null(opt$pcons)) { data = subset(data, pcons == opt$pcons) }
 if(!is.null(opt$minpcons)) { data = subset(data, pcons >= opt$minpcons) }
 if(!is.null(opt$maxpcons)) { data = subset(data, pcons <= opt$maxpcons) }

### 2014-06-27 astat.r
...

@@ -56,6 +56,7 @@ spec = matrix(c(
 'fcolor', NA, 2, "logical",
 'fsize', NA, 2, "logical",
 'thm', 'T', 2, "logical",
+'ther', NA, 2, "logical",
 'thd', NA, 2, "logical",
 'noreg' , NA, 2, "logical"
 ), byrow=TRUE, ncol=4);
@@ -215,7 +216,6 @@ if(!is.null(opt$ylab)) {
 	qpl <- qpl + ylab(opt$ylab)
 }
 
-qpl <- qpl + labs(title = titre)
 
 
 dens <- function (m, l, a) 1 - (1-(a/l)^2)^m
@@ -224,6 +224,52 @@ p <- function(d, l, c, ce, a) 1 - (1- d^(a * (c - ce)))^(ce * (l - a))
 
 po <- function(m, l, c, ce, a) p(dens(m, l, a), l, c, ce, a)
 
+
+pvgc <- function (n, d, c, ce)  { x = n - (c-ce); choose(ce, x) * d^x * (1-d)^(ce-x) }
+pvge <- function (n, d, c, ce) {  x = n - (c-ce); choose(ce-1, x) * d^x * (1-d)^(ce-1-x) }
+pv<- function (x, d, c, ce) { choose(c-1, x) * d^x * (1-d)^(c-1-x) }
+pvabe <- function(n, d, c, ce) { x = n - 1 ; choose(c-1, x) * d^x * (1-d)^(c-1-x) }
+pcpar <- function(n, d, c, ce, l) { pvgc(n,d,c,ce) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce))) )^(l-1) }
+pepar<- function(n, d, c, ce, l) { pvge(n,d,c,ce) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce))) )^(l-2) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce)))) }
+ptotal <- function (m, c, ce, l) {
+ d= 1- (1-1/l^2)^m
+ sum( sapply(1:c, function (x) pcpar(x, d, c, ce, l)))^(c-ce) * sum(sapply(1:c, function(x) pepar(x, d, c, ce, l)))^ce
+}
+
+
+
+#pvgc <- function (n, d, c, ce, g)  { x = n -( (c-ce)-1) - g; choose(ce, x) * d^x * (1-d)^(ce-x) }
[…]

### 2014-06-27 astat.r
théorie

@@ -236,8 +236,6 @@ ptotal <- function (m, c, ce, l) {
  sum( sapply(1:c, function (x) pcpar(x, d, c, ce, l)))^(c-ce) * sum(sapply(1:c, function(x) pepar(x, d, c, ce, l)))^ce
 }
 
-
-
 #pvgc <- function (n, d, c, ce, g)  { x = n -( (c-ce)-1) - g; choose(ce, x) * d^x * (1-d)^(ce-x) }
 #pvge <- function (n, d, c, ce, g) {  x = n - (c-ce); choose(ce-1, x) * d^x * (1-d)^(ce-1-x) }
 #pv<- function (x, d, c, ce, g) { choose(c-1, x) * d^x * (1-d)^(c-1-x) }
@@ -248,7 +246,6 @@ ptotal <- function (m, c, ce, l) {
 # d= dens(m, l, 1)
 # sum( sapply(1:c, function (x) pcpar(x, d, c, ce, l, g)))^(c-ce) * sum(sapply(1:c, function(x) pepar(x, d, c, ce, l, g)))^ce
 #}
-
 #qplot(m, 1-sapply(m, function(x) ptotal(x, 4, 1, 512))) + geom_line()
 
 if (!is.null(opt$ther)) {
@@ -264,7 +261,9 @@ if (!is.null(opt$ther)) {
 					print(erasures)
 					print(gamma)
 					print("Ok hein")
-					qpl <- qpl + stat_function(fun = function(x) { 1 - ptotal(x, l, c, erasures) }, color = "black")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
+					qpl <- qpl + stat_function(fun = function(x) { 1 - ptotal(x, c, erasures, l) }, color = "black", geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
+					tempd = data.frame(m = data$m, errorrate=1-sapply(data$m, function(x) { 1 - ptotal(x, c, erasures, l) }))
+					#qpl <- qpl + geom_point(data=tempd, color = "red")
 				}
 			}
 		}

### 2014-06-27 Articles/article.tex
...
théorie
écriture forumle

@@
 
+	\begin{figure}
+		\includegraphics[width=8.5cm]{comp_erreurs_a2l512c4er1}
+		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messagges, analytical result in continuous black}
+	\end{figure}
+
 	\newpage
@@
 
+	\newpage
+
+	Formula for errors insted of erasures :
+
+	$P(n_{gc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
+
+	$P(n_{ge} = (c - c_e) + \gamma + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$
+
+	$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$
+
+	$P(n_{be} = x) = P(n_{bc} = x) = {c - 1 \choose x} d^x (1-d)^{c- 1 -x}$
+
+	\begin{align*}
+	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
+	\end{align*}
+
+	$P_{err} = 1 - P_{retrieve}$
+
 	\section{Conclusion}

### 2014-06-27 astat.r
amélioration gamma

@@ -73,6 +73,7 @@ data = read.csv(opt$file, comment.char = "#")
 noms = names(data)
 
 
+X11()
 #if(is.null(opt$color)) { opt$color = "red" ; }
 if(is.null(opt$abs)) { opt$abs = "erasures" ; }
 if(is.null(opt$ord)) { opt$ord = "errorrate" ; }
@@ -138,7 +139,6 @@ if (is.null(opt$title)) {
 	titre <- opt$title
 }
 print(titre)
-X11()
 
 
 booleen <- is.null(c(opt$color, opt$size, opt$shape))
@@ -225,15 +225,15 @@ p <- function(d, l, c, ce, a) 1 - (1- d^(a * (c - ce)))^(ce * (l - a))
 po <- function(m, l, c, ce, a) p(dens(m, l, a), l, c, ce, a)
 
 
-pvgc <- function (n, d, c, ce)  { x = n - (c-ce); choose(ce, x) * d^x * (1-d)^(ce-x) }
+pvgc <- function (n, d, c, ce, g)  { x = n - (c-ce-1) - g ; choose(ce, x) * d^x * (1-d)^(ce-x) }
 pvge <- function (n, d, c, ce) {  x = n - (c-ce); choose(ce-1, x) * d^x * (1-d)^(ce-1-x) }
 pv<- function (x, d, c, ce) { choose(c-1, x) * d^x * (1-d)^(c-1-x) }
-pvabe <- function(n, d, c, ce) { x = n - 1 ; choose(c-1, x) * d^x * (1-d)^(c-1-x) }
-pcpar <- function(n, d, c, ce, l) { pvgc(n,d,c,ce) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce))) )^(l-1) }
-pepar<- function(n, d, c, ce, l) { pvge(n,d,c,ce) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce))) )^(l-2) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce)))) }
-ptotal <- function (m, c, ce, l) {
+pvabe <- function(n, d, c, ce, g) { x = n - g ; choose(c-1, x) * d^x * (1-d)^(c-1-x) }
[…]

### 2014-06-28 astat.r
Formule gén ?

@@ -6,6 +6,7 @@ library(scales)
 
 library(plyr)
 
+
 spec = matrix(c(
 'file', 'f', 1, "character",
 'color', NA, 2, "character",
@@ -18,6 +19,7 @@ spec = matrix(c(
 'xlab', 'x', 2, "character",
 'ylab', 'y', 2, "character",
 'title', NA, 2, "character",
+'facet', NA, 2, "character",
 'abs', NA, 2, "character",
 'ord', NA, 2, "character",
 'help' , 'h', 0, "logical",
@@ -69,10 +71,27 @@ if ( !is.null(opt$help) ) {
 
 #args = commandArgs()
 
-data = read.csv(opt$file, comment.char = "#")
+#data = read.csv(opt$file, comment.char = "#", as.is = FALSE)
+data = read.csv(opt$file, comment.char = "#")#, na.strings="NA") #stringAsFactors=FALSE)#, as.is= TRUE)
 noms = names(data)
 
+#i <- sapply(data, function (x) is.factor(x) && is.numeric(x))
+#data[i] <- lapply(data[i], function (x) as.numeric(levels(x))[x])
 
+# Pour réparer les putains de conneries de R
+#repare <- function(x) { data[,x] <- as.numeric(levels(data[,x]))[data[,x]] } #ne marche pas !?
+#repare("errorrate")
+# Comme rien n'y fait, allons y comme des brutes
+#data$errorrate <- as.numeric(levels(data$errorrate))[data$errorrate]
+#data$eta <- as.numeric(levels(data$eta))[data$eta]
+#data$ipeta <- as.numeric(levels(data$ipeta))[data$ipeta]
+#data$ipaeta <- as.numeric(levels(data$ipaeta))[data$ipaeta]
+#data$c <- as.numeric(levels(data$c))[data$c]
+#data$l <- as.numeric(levels(data$l))[data$l]
+#data$winners <- as.numeric(levels(data$winners))[data$winners]
+## Solution la plus élégante trouvée : repassée à la version précédente de R, whaaaa !
+
+print(is.factor(data$errorrate))
 X11()
[…]

### 2014-06-28 astat.r
ajout dans script R : courbes se ressemblent

@@ -248,16 +248,34 @@ p <- function(d, l, c, ce, a) 1 - (1- d^(a * (c - ce)))^(ce * (l - a))
 po <- function(m, l, c, ce, a) p(dens(m, l, a), l, c, ce, a)
 
 
-pvgc <- function (n, d, c, ce, g)  { x = n - (c-ce-1) - g ; choose(ce, x) * d^x * (1-d)^(ce-x) }
-pvge <- function (n, d, c, ce) {  x = n - (c-ce); choose(ce-1, x) * d^x * (1-d)^(ce-1-x) }
-pv<- function (x, d, c, ce) { choose(c-1, x) * d^x * (1-d)^(c-1-x) }
-pvabe <- function(n, d, c, ce, g) { x = n - g ; choose(c-1, x) * d^x * (1-d)^(c-1-x) }
-pcpar <- function(n, d, c, ce, l,g) { pvgc(n,d,c,ce, g) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce))) )^(l-1) }
-pepar<- function(n, d, c, ce, l,g) { pvge(n,d,c,ce) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce))) )^(l-2) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g)))) }
-ptotal <- function (m, c, ce, l, g) {
- d= 1- (1-1/l^2)^m
- sum( sapply(1:(c+g-1), function (x) pcpar(x, d, c, ce, l,g)))^(c-ce) * sum(sapply(1:(c+g-1), function(x) pepar(x, d, c, ce, l,g)))^ce
+pvgc <- function (n, d, c, ce, g, a)  { x = n - a*(c-ce-1) - g ; choose(a * ce, x) * d^x * (1-d)^(a*ce-x) }
+pvge <- function (n, d, c, ce, a) {  x = n - a*(c-ce); choose(a*(ce-1), x) * d^x * (1-d)^(a *(ce-1)-x) }
+pv<- function (x, d, c, ce, a) { choose(a*(c-1), x) * d^x * (1-d)^(a*(c-1)-x) }
+pvabe <- function(n, d, c, ce, g, a) { x = n - g ; choose(a*(c-1), x) * d^x * (1-d)^(a*(c-1)-x) }
+
+psupc <- function(n, d, c, ce, l, g, a) sum(sapply((n+1):(a*(c-1)+g), function(x) pvgc(x,d,c,ce,g,a)))
[…]

### 2014-06-28 Articles/article.tex
Explication des indices.
amélioration gamma
Ajout formule en latex

@@
 
+	gc : good (à remplacer par right) neuron in correct cluster
+
+	ge : good neuron in erroneous cluster
+
+	abe : bad activated neuron in erroneous cluster
+
+	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster
+
+	bc : bad neuron in correct cluster
+
 	$P(n_{gc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
@@
 
+	generalisation to multiple activities per cluster :
+
+	$P(n_{gc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
+
+	$P(n_{ge} = a(c - c_e) + \gamma + x) = {a c_e - 1 \choose x} d^x (1-d)^{a c_e-1-x}$
+
+	$P(n_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$
+
+	$P(n_{be} = x) = P(n_{bc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
+
+	\begin{align*}
+	P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ]\left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1} { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
+	\end{align*}
+
 	$P_{err} = 1 - P_{retrieve}$

### 2014-06-28 Articles/article.tex
correction formule

@@
 	\begin{align*}
-	P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ]\left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1} { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
+	P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ]\left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a-1} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
 	\end{align*}

### 2014-06-28 Articles/article.tex
correction formule, mais approximation de non recouvrement

--- 2014-06-28 Articles/article.tex
@@
 
+	%à changer : prendre en compte les $a$ neurones activés : problème des recouvrements !! on est trop optimiste si grand nombre d'activités (ou pessimiste ?)
+
 	generalisation to multiple activities per cluster :
@@
 	\begin{align*}
-	P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ]\left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1} { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
+	P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ]\left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2a} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right]^a \right ]^{c_e}
 	\end{align*}

### 2014-06-28 astat.r

@@ -258,7 +258,8 @@ psupe <- function(n, d, c, ce, l, g, a) sum(sapply((n+1):(a*(c-1)+g), function(x
 
 pcpar <- function(n, d, c, ce, l, g, a) { (sum(sapply(0:(a-1), function(x) choose(a, x) * psupc(n,d,c,ce,l,g,a)^x * pvgc(n,d,c,ce,g,a)^(a-x) ))) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce, a))) )^(l-a) }
 
-pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce,a))) )^(l-a-1) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g,a)))) }
+#pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce,a))) )^(l-a-1) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g,a)))) }
+pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce,a))) )^max(0,(l-2*a)) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g,a))))^a }
 
 ptotal <- function (m, c, ce, l, g, a) {
 	d= 1- (1-(a/l)^2)^m

### 2014-06-28 Articles/article.tex
ajout formule résilience

@@
 	\newpage
+	a
+	\newpage
 	Spéculations en Français :
@@
 
+		a priori for noise on edges :
+
+	\[P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a c_k} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \]
+
+	\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a c_k} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]
+
+	\newpage
+	a
 	\newpage

### 2014-06-29 Articles/article.tex
...

@@
 		\includegraphics[width=8.5cm]{comparaison_regles_pool5_a2c4l512e2}
-		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messagges, analytical result in continuous black}
+		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
 		\end{figure}
@@
 	\begin{figure}
-		\includegraphics[width=8.5cm]{comp_erreurs_a2l512c4er1}
-		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messagges, analytical result in continuous black}
+		\includegraphics[width=8.5cm]{remplacement_figure3g1}
+		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
 	\end{figure}
@@
 
-	$P(n_{ge} = a(c - c_e) + \gamma + x) = {a c_e - 1 \choose x} d^x (1-d)^{a c_e-1-x}$
+	$P(n_{ge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
 

### 2014-06-29 astat.r

@@ -33,6 +33,8 @@ spec = matrix(c(
 'degree' , 'd', 2, "integer",
 'minpoolsize' , NA, 2, "integer",
 'minwinners' , NA, 2, "integer",
+'maxwinners' , NA, 2, "integer",
+'maxgamma' , NA, 2, "integer",
 'minpcons' , NA, 2, "double",
 'maxpcons' , NA, 2, "double",
 'gamma' , 'g', 2, "integer",
@@ -91,6 +93,10 @@ noms = names(data)
 #data$winners <- as.numeric(levels(data$winners))[data$winners]
 ## Solution la plus élégante trouvée : repassée à la version précédente de R, whaaaa !
 
+
+data[data$winners == 0,]$winners <-  data[data$winners == 0,]$activities
+
+
 print(is.factor(data$errorrate))
 X11()
 #if(is.null(opt$color)) { opt$color = "red" ; }
@@ -123,6 +129,8 @@ if(!is.null(opt$minpcons)) { data = subset(data, pcons >= opt$minpcons) }
 if(!is.null(opt$maxpcons)) { data = subset(data, pcons <= opt$maxpcons) }
 if(!is.null(opt$minpoolsize)) { data = subset(data, poolsize >= opt$minpoolsize) }
 if(!is.null(opt$minwinners)) { data = subset(data, winners >= opt$minwinners) }
+if(!is.null(opt$maxwinners)) { data = subset(data, winners <= opt$maxwinners) }
+if(!is.null(opt$maxgamma)) { data = subset(data, gamma <= opt$maxgamma) }
 if(!is.null(opt$maxefficiency)) { data = subset(data, efficiency <= opt$maxefficiency) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }
@@ -312,7 +320,7 @@ if (!is.null(opt$ther)) {
 						newd = data
 						newd$errorrate = sapply(data$m, function (x) { 1 - ptotal(x, ci, erasures, l, gamma, activities) })
 						#qpl <- qpl + geom_point(data=tempd, color = "red")
-						qpl <- qpl + geom_line(aes(y = newd$errorrate), color = "blue")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
[…]

### 2014-06-30 Articles/article.tex
correction Xi

@@
 \usepackage[autolanguage]{numprint}
+\usepackage[affil-it]{authblk}
 %\usepackage[squaren,Gray]{SIunits}
@@
 \title{Storing messages with multipartite neural cliques}
-\author{???}
+\author[]{Nissim Zerbib}
+\affil{Département d'Informatique, École normale supérieure, Paris, France}
+
+\author[]{Vincent Gripon}
+\affil{Département d'Électronique, Télécom Bretagne, Brest, France}
+
+\author{?}
+
 \date{
@@
 	 \begin{abstract}
-	 ???
+	 	We extend recently introduced associative memories based on cliques to multipartite cliques.
+We propose a variant of the classic retrieving rule.
+We study their relative performance for retrieving partially erased and corrupted messages.
+We provide both analytical and simulation results showing improvements of capacity.
 	 \end{abstract}
 
-	\keywords{associative memory, error correcting code}
+	\keywords{associative memory, error correcting code, cliques, multipartite cliques, neural networks}
 
@@
 
-		\subsection{Analytical results}
+	\subsection{Retrieving partially erased messages}
+
+	\subsubsection{Analytical result}
 
@@
 
-	\subsection{Simulations}
+	\subsubsection{Simulations}
 		Improves the retrieval rate for multiple iterations and/or corrupted messages.
@@
 	\begin{figure}
-		\includegraphics[width=8.5cm]{comparaison_regles_pool5_a2c4l512e2}
+		\includegraphics[width=8.5cm]{remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
 		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
@@
 
+	\newpage
+	a
+	\newpage
+
+	\subsection{Retrieving corrupted messages}
 	\begin{figure}
@@
 
-	\newpage
-	a
-	\newpage
 	Spéculations en Français :
@@
 
-	$P(n_{ge} = (c - c_e) + \gamma + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$
+	$P(n_{ge} = (c - c_e) + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$
 
@@
 
-	\begin{align*}
-	P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ]\left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2a} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right]^a \right ]^{c_e}
-	\end{align*}
+	%\begin{align*}
+	$P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
+	$
+	%\end{align*}
 
@@
 	\nocite{*}
-	\bibliographystyle{plain} % Le style est mis entre crochets.
+	\bibliographystyle{numeric} % Le style est mis entre crochets.
          \bibliography{bibli.bib}

### 2014-06-30 astat.r

@@ -10,6 +10,9 @@ library(plyr)
 spec = matrix(c(
 'file', 'f', 1, "character",
 'color', NA, 2, "character",
+'ncolor', NA, 2, "character",
+'nshape', NA, 2, "character",
+'nsize', NA, 2, "character",
 'shape', NA, 2, "character",
 'size', NA, 2, "character",
 'lt', 'L', 2, "character",
@@ -194,6 +197,9 @@ if (!is.null(opt$fcolor)) {
 qpl <- qplot(data[,opt$abs], data[,opt$ord], ylab=opt$ord, xlab=opt$abs, main = "", color = cdata) + labs(colour = opt$color)# + guides(fill = guide_colourbar(title=opt$color))#+ scale_colour_continuous(name=opt$color) #, size = data[,opt$size])#opt$color) # col="blue")
 } else {qpl <- qplot(data[,opt$abs], data[,opt$ord], ylab=opt$ord, xlab=opt$abs, main = "")  }
 
+if(!is.null(opt$ncolor)) {
+	qpl <- qpl + labs(colour = opt$ncolor)
+}
 
 if(!is.null(opt$facet)) {
 	qpl <- qpl + facet_wrap(as.formula(paste("~", opt$facet)))
@@ -210,8 +216,14 @@ if(!is.null(opt$size)) {
 if(!is.null(opt$shape)) { qpl <- qpl + geom_point(aes(shape = factor(data[,opt$shape])), size = 3) + labs(shape = opt$shape) }# + scale_shape(name=opt$shape)  }
 #if(!is.null(opt$color)) { qpl <- qpl + geom_point(colour = data[opt$color]) }
 
+if(!is.null(opt$nsize)) {
+	qpl <- qpl + labs(size = opt$nsize)
+}
 
 
+if(!is.null(opt$nshape)) {
+	qpl <- qpl + labs(shape = opt$nshape)
+}
 
 # Ajouter factor group si besoin est.
 if(!is.null(opt$box)) { qpl <- qpl + geom_boxplot(aes(fill = factor(data[,opt$abs]))) }
@@ -365,7 +377,8 @@ if (!is.null(opt$thd)) {
 	}
 }
 
-qpl <- qpl + labs(title = titre)
+
+qpl <- qpl + labs(title = titre) + guides(colour = guide_legend(nrow = 2))
 qpl #+ geom_bar()#+stat_smooth()
 #title(titre)
 temp <- data.frame(y = data[,1], x = data[,8])

### 2014-06-30 astat.r
...

@@ -64,6 +64,7 @@ spec = matrix(c(
 'fsize', NA, 2, "logical",
 'thm', 'T', 2, "logical",
 'ther', NA, 2, "logical",
+'thpsi', NA, 2, "logical",
 'thd', NA, 2, "logical",
 'noreg' , NA, 2, "logical"
 ), byrow=TRUE, ncol=4);
@@ -279,7 +280,7 @@ psupe <- function(n, d, c, ce, l, g, a) sum(sapply((n+1):(a*(c-1)+g), function(x
 pcpar <- function(n, d, c, ce, l, g, a) { (sum(sapply(0:(a-1), function(x) choose(a, x) * psupc(n,d,c,ce,l,g,a)^x * pvgc(n,d,c,ce,g,a)^(a-x) ))) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce, a))) )^(l-a) }
 
 #pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce,a))) )^(l-a-1) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g,a)))) }
-pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce,a))) )^max(0,(l-2*a)) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g,a))))^a }
+pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce,a))) )^max(0,(l-2*a)) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g,a))))^a }
 
 ptotal <- function (m, c, ce, l, g, a) {
 	d= 1- (1-(a/l)^2)^m

### 2014-06-30 sam.jl

@@ -3,7 +3,7 @@
 module Sam
 
 
-#Floyd algorithm
+#Floyd algorithm : contrib ?
 function rand_combination(n, m)
 	s = Set()
 	for j=n-m+1:n

### 2014-06-30 astat.r
réorganisation

@@ -84,7 +84,7 @@ noms = names(data)
 #i <- sapply(data, function (x) is.factor(x) && is.numeric(x))
 #data[i] <- lapply(data[i], function (x) as.numeric(levels(x))[x])
 
-# Pour réparer les putains de conneries de R
+# Pour réparer les erreurs dues à la mise à jour de R
 #repare <- function(x) { data[,x] <- as.numeric(levels(data[,x]))[data[,x]] } #ne marche pas !?
 #repare("errorrate")
 # Comme rien n'y fait, allons y comme des brutes

### 2014-06-30 astat.r
Ajout courbe

@@ -122,6 +122,7 @@ if(!is.null(opt$winners)) {
 		data = subset(data, winners == opt$winners)
 	}
 }
+#data = subset(data, maxiterations == 1 | maxiterations == 4)
 if(!is.null(opt$tests)) { data = subset(data, tests == opt$tests) }
 if(!is.null(opt$fsum)) { data = subset(data, fsum == opt$fsum) }
 if(!is.null(opt$fcorrupt)) { data = subset(data, fcorrupt == opt$fcorrupt) }

### 2014-07-01 astat.r
Formules psi

@@ -289,6 +289,28 @@ ptotal <- function (m, c, ce, l, g, a) {
 }
 
 
+
+
+##############
+
+pcpsi <- function(n, c, ce, a, psi) choose(a * (c- ce), n) * (1-psi)^n * psi^(a*(c-ce) - n)
+pplus <- function (d, psi) psi * (1-d) + (1- psi) * d
+
+pvpsi <- function(x, d, c, ce, a, psi) {
+	p = pplus(d, psi) ;
+	choose(a * (c - ce), c) * p^x * (1-p)^(a*(c-ce) - x)
+}
+pcsuppsi <- function(n, c, ce, a, psi) sum(sapply((n+1):(a*(c-ce)), function(x) pcpsi(x, c, ce, a, psi)))
+
+pvinfpsi <- function(n,d, c, ce, a, psi) sum(sapply(0:(n-1), function(x) pvpsi(x, d, c, ce, a, psi)))
+
+pcparpsi <- function(n, d, c, ce, l, a, psi) { (sum(sapply(0:(a-1), function(x) choose(a, x) * pcsuppsi(n, c, ce, a, psi)^x * pcpsi(n, c, ce, a, psi)^(a-x)))) * pvinfpsi(n,d, c, ce, a, psi)^(l-a) }
+
+ptotalpsi <- function (m, c, ce, l, a, psi) {
+	d = dens(m, l, a)
+	sum( sapply(1:(a*(c-ce)), function (x) pcparpsi(x, d, c, ce, l,a, psi)))^(c-ce)
+}
+
 #pvgc <- function (n, d, c, ce, g)  { x = n - (c-ce-1) - g ; choose(ce, x) * d^x * (1-d)^(ce-x) }
 #pvge <- function (n, d, c, ce) {  x = n - (c-ce); choose(ce-1, x) * d^x * (1-d)^(ce-1-x) }
 #pv<- function (x, d, c, ce) { choose(c-1, x) * d^x * (1-d)^(c-1-x) }

### 2014-07-01 Articles/article.tex
réorganisation
Ajout courbe
///
...

@@
 We study their relative performance for retrieving partially erased and corrupted messages.
-We provide both analytical and simulation results showing improvements of capacity.
+We provide both analytical and simulation results showing improvements of capacity over.
 	 \end{abstract}
@@
 
+	$\eta_m = (P_{retrieve} m ) \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \frac{c}{(c-c_e) \log_2{l \choose a }}$
+
+	$\eta_{max} = \max_x \eta_x $
+
 	\subsubsection{Simulations}
@@
 
+		\begin{figure}
+		\includegraphics[width=8.5cm]{remplacement_figure4g1}
+		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
+	\end{figure}
+
 	Spéculations en Français :
@@
 	% À corriger avec sommes multiparties
-	%\[P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \]
+	%$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$
 
-	%\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]
+	%$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$
 
@@
 		a priori for noise on edges :
+	\newpage
+	l
+	\newpage
+	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
 
-	\[P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a c_k} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \]
-
-	\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a c_k} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]
+	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$
 
@@
 
-	Formula for errors insted of erasures :
+	Formula for errors instead of erasures :
 

### 2014-07-01 astat.r

@@ -281,7 +281,7 @@ psupe <- function(n, d, c, ce, l, g, a) sum(sapply((n+1):(a*(c-1)+g), function(x
 pcpar <- function(n, d, c, ce, l, g, a) { (sum(sapply(0:(a-1), function(x) choose(a, x) * psupc(n,d,c,ce,l,g,a)^x * pvgc(n,d,c,ce,g,a)^(a-x) ))) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce, a))) )^(l-a) }
 
 #pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:n-1, function(x) pv(x,d,c,ce,a))) )^(l-a-1) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g,a)))) }
-pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce,a))) )^max(0,(l-2*a)) * (sum (sapply(0:n-1, function(x) pvabe(x, d, c, ce,g,a))))^a }
+pepar<- function(n, d, c, ce, l, g, a) {  (sum(sapply(0:(a-1), function(x) choose(a, x) * psupe(n,d,c,ce,l,g,a)^x * pvge(n,d,c,ce,a)^(a-x) ))) * ( sum (sapply(0:(n-1), function(x) pv(x,d,c,ce,a))) )^max(0,(l-2*a)) * (sum (sapply(0:(n-1), function(x) pvabe(x, d, c, ce,g,a))))^a }
 
 ptotal <- function (m, c, ce, l, g, a) {
 	d= 1- (1-(a/l)^2)^m
@@ -297,18 +297,18 @@ pcpsi <- function(n, c, ce, a, psi) choose(a * (c- ce), n) * (1-psi)^n * psi^(a*
 pplus <- function (d, psi) psi * (1-d) + (1- psi) * d
 
 pvpsi <- function(x, d, c, ce, a, psi) {
-	p = pplus(d, psi) ;
[…]

### 2014-07-02 Articles/article.tex
rédaction preuve

@@
 
-	probability for $i$ and $j$ to be active in their respective clusters for one message : $\frac{a}{l}$
-
-	probability of the edge	not being added in the network for one message : $1 - \left(\frac{a}{l}\right)^2$
+	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$, providing messages are independent, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$.
+Thus the density $d$ can be expressed like this :
 
@@
 
-	gap with density in simulations : under $1$ percent
-
-	probability for a vertex $v$ to achieve the maximum score, that is to mean $a(c-c_e)$ : $d^	{a(c-c_e)}$
+	Thanks to the memory effect $\gamma$, activated neurons in a non-erased cluster stays activated and are the only ones doing so in their cluster.
+For neurons in erased clusters, the maximum attainable score is $a(c - c_e)$.
+Neurons corresponding to the original message achieve this score.
+Besides the probability for a neuron $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^	{a(c-c_e)}$.
 
@@
 
-	probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum : $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$
+	Since neurons representing messages are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$.
 
-	probability for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective cluster : $\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)}$
+	Scores in clusters being also independent, the probability for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective clusters is $\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)}$.
 
-	Whence error rate is : \[P_{err} = 1 -	\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)} \]
+	Whence error rate in retrieving messages is : \[P_{err} = 1 -	\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)} \]
 
@@
 	\subsubsection{Simulations}
+		gap of theoretical density with density in simulations : under $1$ percent
 		Improves the retrieval rate for multiple iterations and/or corrupted messages.
@@
 	\newpage
-	a
+	p
 	\newpage

### 2014-07-02 Articles/article.tex
...

@@
 		gap of theoretical density with density in simulations : under $1$ percent
-		Improves the retrieval rate for multiple iterations and/or corrupted messages.
+
+		New rule : Improves the retrieval rate for multiple iterations and/or corrupted messages.
 
@@
 	\begin{figure}
-		\includegraphics[width=8.5cm]{densiteexemple.pdf}
+		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
 		\caption{Theoretical and empirical densities}
@@
 	\begin{figure}
-		\includegraphics[width=8.5cm]{remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
+		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
 		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
@@
 	\begin{figure}
-		\includegraphics[width=8.5cm]{remplacement_figure3g1}
+		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
 		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
@@
 		\begin{figure}
-		\includegraphics[width=8.5cm]{remplacement_figure4g1}
+		\includegraphics[width=8.5cm]{Courbes/remplacement_figure4g1}
 		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
@@
 
+	Formula for errors instead of erasures :
+
+	gc : good (à remplacer par right/wrong ?) neuron in correct cluster
+
+	ge : good neuron in erroneous cluster
+
+	abe : bad activated neuron in erroneous cluster
+
+	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster
+
+	bc : bad neuron in correct cluster
+
+	$P(n_{gc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
+
+	$P(n_{ge} = (c - c_e) + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$
+
+	$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$
+
+	$P(n_{be} = x) = P(n_{bc} = x) = {c - 1 \choose x} d^x (1-d)^{c- 1 -x}$
+
+	$
+	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
+	$
+
+	%à changer : prendre en compte les $a$ neurones activés : problème des recouvrements !! on est trop optimiste si grand nombre d'activités (ou pessimiste ?)
+
+	generalisation to multiple activities per cluster :
+	\newpage
+	a
+	\newpage
+
+	$P(n_{gc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
+
+	$P(n_{ge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
+
+	$P(n_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$
+
+	$P(n_{be} = x) = P(n_{bc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
+
+	%\begin{align*}
+	$P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
+	$
+	%\end{align*}
+
+	$P_{err} = 1 - P_{retrieve}$
+
+	\newpage
+	a
+	\newpage
+
+	\section{Conclusion}
+
+	%Marche mieux pouur de petits c --> le faire sur le sparse ?
+
+	\section{Resilience}
 	Spéculations en Français :
@@
 		a priori for noise on edges :
-	\newpage
-	l
-	\newpage
+
 	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
@@
 	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$
-
-	\newpage
-	a
-	\newpage
-
-	Formula for errors instead of erasures :
-
-	gc : good (à remplacer par right) neuron in correct cluster
-
-	ge : good neuron in erroneous cluster
-
-	abe : bad activated neuron in erroneous cluster
-
-	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster
-
-	bc : bad neuron in correct cluster
-
-	$P(n_{gc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
-
-	$P(n_{ge} = (c - c_e) + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$
-
-	$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$
-
-	$P(n_{be} = x) = P(n_{bc} = x) = {c - 1 \choose x} d^x (1-d)^{c- 1 -x}$
-
-	\begin{align*}
-	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
-	\end{align*}
-
-	%à changer : prendre en compte les $a$ neurones activés : problème des recouvrements !! on est trop optimiste si grand nombre d'activités (ou pessimiste ?)
-
-	generalisation to multiple activities per cluster :
-
-	$P(n_{gc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
-
-	$P(n_{ge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
-
-	$P(n_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$
-
-	$P(n_{be} = x) = P(n_{bc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
-
-	%\begin{align*}
-	$P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
-	$
-	%\end{align*}
-
-	$P_{err} = 1 - P_{retrieve}$
-
-	\section{Conclusion}
-
-	%Marche mieux pouur de petits c --> le faire sur le sparse ?
 	\nocite{*}

### 2014-07-02 astat.r

@@ -122,7 +122,7 @@ if(!is.null(opt$winners)) {
 		data = subset(data, winners == opt$winners)
 	}
 }
-#data = subset(data, maxiterations == 1 | maxiterations == 4)
+data = subset(data, maxiterations == 1 | maxiterations == 4)
 if(!is.null(opt$tests)) { data = subset(data, tests == opt$tests) }
 if(!is.null(opt$fsum)) { data = subset(data, fsum == opt$fsum) }
 if(!is.null(opt$fcorrupt)) { data = subset(data, fcorrupt == opt$fcorrupt) }

### 2014-07-02 sam.jl

@@ -401,8 +401,9 @@ const dict_corrupt = [ 0 => erase_clusters!, 1 => corrupt_clusters!, 2 => add_on
 function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons = 0.0, p_des = 0.0, degree = 0, activities = 1, winners = 1, pool_size = 1, only_drop = false)
 	#res = mean(map( x -> test_network(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners), [1:pool_size])) ### Pas efficace, pourquoi ?
 	res = zeros(6)
+	const real_gamma = (if gamma == -1 activities else gamma end)
 	for i=1:pool_size 
-		res += test_network(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners)
+		res += test_network(l, c, m, real_gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners)
 	end
 	res /= pool_size
 
@@ -430,7 +431,7 @@ function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt
 	iaeta = aeta / info_alphabet
 	ipeta = peta / info_alphabet
 	ipaeta = paeta / info_alphabet
-	return [ res[1] res[2] res[3] l c m gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop]
+	return [ res[1] res[2] res[3] l c m real_gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop]
 end
 
 #function set_proba(pr)

### 2014-07-02 astat.r
...

@@ -421,7 +421,7 @@ if (!is.null(opt$thd)) {
 }
 
 
-qpl <- qpl + labs(title = titre) + guides(colour = guide_legend(nrow = 2))
+qpl <- qpl + labs(title = titre) #+ guides(colour = guide_legend(nrow = 2))
 qpl #+ geom_bar()#+stat_smooth()
 #title(titre)
 temp <- data.frame(y = data[,1], x = data[,8])

### 2014-07-02 sam.jl

@@ -401,7 +401,7 @@ const dict_corrupt = [ 0 => erase_clusters!, 1 => corrupt_clusters!, 2 => add_on
 function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons = 0.0, p_des = 0.0, degree = 0, activities = 1, winners = 1, pool_size = 1, only_drop = false)
 	#res = mean(map( x -> test_network(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners), [1:pool_size])) ### Pas efficace, pourquoi ?
 	res = zeros(6)
-	const real_gamma = (if gamma == -1 activities else gamma end)
+const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) actvities + 1 else gamma end)
 	for i=1:pool_size 
 		res += test_network(l, c, m, real_gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners)
 	end

### 2014-07-02 sam.jl
exp

@@ -401,7 +401,7 @@ const dict_corrupt = [ 0 => erase_clusters!, 1 => corrupt_clusters!, 2 => add_on
 function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons = 0.0, p_des = 0.0, degree = 0, activities = 1, winners = 1, pool_size = 1, only_drop = false)
 	#res = mean(map( x -> test_network(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners), [1:pool_size])) ### Pas efficace, pourquoi ?
 	res = zeros(6)
-const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) actvities + 1 else gamma end)
+const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) activities + 1 else gamma end)
 	for i=1:pool_size 
 		res += test_network(l, c, m, real_gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners)
 	end

### 2014-07-03 Articles/article.tex
...
..

@@
 	 \begin{abstract}
-	 	We extend recently introduced associative memories based on cliques to multipartite cliques.
+	 	We extend recently introduced associative memories based on clustered cliques to multipartite cliques.
 We propose a variant of the classic retrieving rule.
-We study their relative performance for retrieving partially erased and corrupted messages.
-We provide both analytical and simulation results showing improvements of capacity over.
+We study its performance relatively to the former one for retrieving partially erased and corrupted messages.
+We provide both analytical and simulation results showing improvements in networks capacities.
 	 \end{abstract}
@@
 
+	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ and $m = | \mathcal{M} |$.
+Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or neurons.
+
+	Each message $x = (x_i)_{1 \le i \le c}$ is mapped to $y = (y_i)_{1 \le i \le c}$ where $y_i$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).
+
+	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $1 \le j \le l$ and $1 \le i \le c$, the neuron $j$ in the cluster $i$ is activated if and only if $y_{i,j} = 1$ ; then adding all connections between activated neurons excepting for neurons sharing the same cluster.
+Thus we obtain a multipartite clique between activated neurons of message.
+
 	\subsection{Retrieving messages}
@@
 		\subsubsection{The "$a$ winners take all" rule}
+		$a$-rank
 
@@
 		same algorithmic complexity
+
+		$w = a$
 
@@
 
-	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$, providing messages are independent, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$.
+	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are independent, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$.
 Thus the density $d$ can be expressed like this :
@@
 
-	Thanks to the memory effect $\gamma$, activated neurons in a non-erased cluster stays activated and are the only ones doing so in their cluster.
+	Thanks to the memory effect $\gamma$, activated neurons in a non-erased cluster stay activated and are the only ones doing so in their cluster.
 For neurons in erased clusters, the maximum attainable score is $a(c - c_e)$.
@@
 
-	probability for a vertex $v$	not to achieve the maximum : $1 - d^	{a(c-c_e)}$
+	%probability for a vertex $v$	not to achieve the maximum : $1 - d^	{a(c-c_e)}$
 
@@
 	\subsubsection{Simulations}
-		gap of theoretical density with density in simulations : under $1$ percent
+		gap of theoretical density with density in simulations : under $1$ percent, see Figure \ref{densiteth}
 
@@
 
+	See Figure \ref{erasuresth}
+
 		"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
@@
 	For one iteration, it is less efficient.
-	\begin{figure}
+	\begin{figure}[!htb]
 		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
 		\caption{Theoretical and empirical densities}
+			\label{densiteth}
 	\end{figure}
 
-	\begin{figure}
+	\begin{figure}[!htb]
 		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
 		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
+			\label{erasuresth}
 		\end{figure}
@@
 	\newpage
+	$\,$
+	\newpage
 
 	\subsection{Retrieving corrupted messages}
-	\begin{figure}
-		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
-		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
-	\end{figure}
 
-		\begin{figure}
-		\includegraphics[width=8.5cm]{Courbes/remplacement_figure4g1}
-		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
-	\end{figure}
-
+	\subsubsection{Analytical result}	
 	Formula for errors instead of erasures :
@@
 
+	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$.
+
 	$P(n_{gc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
+
+	Correct neurons in corrupted clusters achieve at least a score of $a(c - c_e)$.
 
@@
 
-	$
+	\begin{align}
 	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
-	$
+	\end{align}
 
@@
 	generalisation to multiple activities per cluster :
-	\newpage
-	a
-	\newpage
 
@@
 
-	%\begin{align*}
-	$P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
-	$
-	%\end{align*}
+	\newpage
+	$\,$
+	\newpage	
+	\begin{align*}
+	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
+	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
+	\end{align*}
 
@@
 
+	See \ref{corruptth}
+
 	\newpage
-	a
+	$\,$
 	\newpage
+
+	\subsubsection{Simulations}
+	\begin{figure}[!htb]
+		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
+		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
+		\label{corruptth}
+	\end{figure}
+
+		\begin{figure}
+		\includegraphics[width=8.5cm]{Courbes/remplacement_figure4g1}
+		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
+	\end{figure}
 
@@
 	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$
+
+	\newpage
+	$\,$
+	\newpage
+	\begin{figure}
+		\includegraphics[width=8.5cm]{Courbes/1comppsic4l512g1}
+		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
+	\end{figure}
+
 	\nocite{*}

### 2014-07-03 astat.r

@@ -355,8 +355,10 @@ if (!is.null(opt$ther)) {
 						qpl <- qpl + stat_function(fun = function(x) { 1 - ptotal(x, ci, erasures, l, gamma, activities) }, color = "black")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
 						newd = data
 						newd$errorrate = sapply(data$m, function (x) { 1 - ptotal(x, ci, erasures, l, gamma, activities) })
+						newd$Theory <- factor("Analytical error\n (corruptions)")
 						#qpl <- qpl + geom_point(data=tempd, color = "red")
-						qpl <- qpl + geom_line(aes(y = newd$errorrate), color = "black")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
+						#qpl <- qpl + geom_line(aes(y = newd$errorrate,  linetype = newd), data = newd, color = "black")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
+						qpl <- qpl + geom_line(aes(y = newd$errorrate,  color = "Analytical\n result\n (corruptions,\n 1 iter)"))
 					}
 				}
 			}
@@ -398,7 +400,7 @@ if (!is.null(opt$thm)) {
 			for (erasures in unique(data$erasures)) {
 				for (activities in unique(data$activities)) {
 					print(activities)
-					qpl <- qpl + stat_function(fun = function(x) po(x, l, ci, erasures, activities), color = "black")
+					qpl <- qpl + stat_function(fun = function(x) po(x, l, ci, erasures, activities), aes(color = "Analytical\n result\n (erasures,\n 1 iter)"))
 					#qpl
 					#message("Press Return To Continue")
 					#invisible(readLines("stdin", n=1))

### 2014-07-04 Articles/article.tex
modif

@@
 	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $1 \le j \le l$ and $1 \le i \le c$, the neuron $j$ in the cluster $i$ is activated if and only if $y_{i,j} = 1$ ; then adding all connections between activated neurons excepting for neurons sharing the same cluster.
-Thus we obtain a multipartite clique between activated neurons of message.
+Thus we obtain a multipartite clique between activated neurons representing a message.
+The parameter $a$ describing the number of activated neurons per cluster will be called number of activities.
 
@@
 
+		Retrieving messages occurs by message passing.
+
 		\subsubsection{The "winner takes all" rule}
 
+		take only maximum score
+
 		\subsubsection{The "$a$ winners take all" rule}
+
 		$a$-rank
@@
 
-		$w = a$
+		$w = a$	is optimal
 

### 2014-07-04 astat.r
...

@@ -37,6 +37,7 @@ spec = matrix(c(
 'minpoolsize' , NA, 2, "integer",
 'minwinners' , NA, 2, "integer",
 'maxwinners' , NA, 2, "integer",
+'maxm' , 'M', 2, "integer",
 'maxgamma' , NA, 2, "integer",
 'minpcons' , NA, 2, "double",
 'maxpcons' , NA, 2, "double",
@@ -52,6 +53,7 @@ spec = matrix(c(
 'ordstep', NA, 2, "double",
 'maxefficiency', 'E', 2, "double",
 'maxactivities', 'A', 2, "double",
+'minactivities', NA, 2, "double",
 'mmiterations', NA, 2, "double",
 'pcons', 'p', 2, "double",
 'maxabs', NA, 2, "double",
@@ -135,10 +137,11 @@ if(!is.null(opt$maxpcons)) { data = subset(data, pcons <= opt$maxpcons) }
 if(!is.null(opt$minpoolsize)) { data = subset(data, poolsize >= opt$minpoolsize) }
 if(!is.null(opt$minwinners)) { data = subset(data, winners >= opt$minwinners) }
 if(!is.null(opt$maxwinners)) { data = subset(data, winners <= opt$maxwinners) }
+if(!is.null(opt$maxm)) { data = subset(data, m <= opt$maxm) }
 if(!is.null(opt$maxgamma)) { data = subset(data, gamma <= opt$maxgamma) }
 if(!is.null(opt$maxefficiency)) { data = subset(data, efficiency <= opt$maxefficiency) }
 if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }
-if(!is.null(opt$maxactivities)) { data = subset(data, activities <= opt$maxactivities) }
+if(!is.null(opt$minactivities)) { data = subset(data, activities >= opt$minactivities) }
 if(!is.null(opt$mmiterations)) { data = subset(data, maxiterations <= opt$mmiterations) }
 if(!is.null(opt$maxabs)) { data = subset(data, data[, opt$abs ] <= opt$maxabs) }
 if(!is.null(opt$minabs)) { data = subset(data, data[, opt$abs ] >= opt$minabs) }

### 2014-07-04 sam.jl

@@ -397,6 +397,13 @@ end
 const dict_rules = [ 0 => sum_of_sum!, 1 => sum_of_max!, 2 => mix_of_rules! ]
 const dict_corrupt = [ 0 => erase_clusters!, 1 => corrupt_clusters!, 2 => add_one_in_clusters!, 3 => add_some_in_clusters! ]
 
+function xlog2(x)
+	if x == 0
+		0
+	else
+		x * log2(x)
+	end
+end
 
 function output_test(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons = 0.0, p_des = 0.0, degree = 0, activities = 1, winners = 1, pool_size = 1, only_drop = false)
 	#res = mean(map( x -> test_network(l, c, m, gamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners), [1:pool_size])) ### Pas efficace, pourquoi ?
@@ -431,7 +438,9 @@ const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) activities 
 	iaeta = aeta / info_alphabet
 	ipeta = peta / info_alphabet
 	ipaeta = paeta / info_alphabet
-	return [ res[1] res[2] res[3] l c m real_gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop]
+	rceta = eta * exp(-(-exp((log(m-1)- (c-ce) * info_alphabet))))
+	psieta = rceta / (1 + xlog2(pcons) + xlog2(1-pcons))
+	return [ res[1] res[2] res[3] l c m real_gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop rceta psieta ]
 end
 
 #function set_proba(pr)

### 2014-07-04 test.jl

@@ -29,7 +29,7 @@ function init_file(fileprefix, dir = "results")
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
 	const suffix = ".csv" #"$(fsum)__$(fcorrupt)"
 	const filename = "$(dir)/$(fileprefix)$suffix"
-	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta,ieta,iaeta,infoalphabet,onlydrop\n"
+	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta,ieta,iaeta,infoalphabet,onlydrop,rceta,psieta\n"
 	open(filename, "a") do file
 		write(file, firstline)
 	end

### 2014-07-04 sam.jl
corrigé

@@ -438,7 +438,7 @@ const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) activities 
 	iaeta = aeta / info_alphabet
 	ipeta = peta / info_alphabet
 	ipaeta = paeta / info_alphabet
-	rceta = eta * exp(-(-exp((log(m-1)- (c-ce) * info_alphabet))))
+	rceta = eta * exp(exp((log(m-1)- (c-erasures) * info_alphabet)))
 	psieta = rceta / (1 + xlog2(pcons) + xlog2(1-pcons))
 	return [ res[1] res[2] res[3] l c m real_gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop rceta psieta ]
 end

### 2014-07-05 astat.r
...

@@ -307,7 +307,9 @@ pcsuppsi <- function(n, c, ce, a, psi) sum(sapply((n+1):(a*(c-ce)), function(x) 
 
 pvinfpsi <- function(n,d, c, ce, a, psi) sum(sapply(0:(n-1), function(x) pvpsi(x, d, c, ce, a, psi)))
 
-pcparpsi <- function(n, d, c, ce, l, a, psi) { (sum(sapply(n:(a *(c-ce)), function(x)  pcpsi(n, c, ce, a, psi)))) * pvinfpsi(n,d, c, ce, a, psi)^(l-a) }#(sum(sapply(0:(a-1), function(x) choose(a, x) * pcsuppsi(n, c, ce, a, psi)^x * pcpsi(n, c, ce, a, psi)^(a-x)))) * (pvinfpsi(n,d, c, ce, a, psi))^(l-a) }
+pcparpsi <- function(n, d, c, ce, l, a, psi) { (sum(sapply(0:(a-1), function(x) choose(a, x) * pcsuppsi(n, c, ce, a, psi)^x * pcpsi(n, c, ce, a, psi)^(a-x)))) * (pvinfpsi(n,d, c, ce, a, psi))^(l-a) }
+
+										#	function(x)  pcpsi(n, c, ce, a, psi)^a))) * pvinfpsi(n,d, c, ce, a, psi)^(l-a) }#(sum(sapply(0:(a-1), function(x) choose(a, x) * pcsuppsi(n, c, ce, a, psi)^x * pcpsi(n, c, ce, a, psi)^(a-x)))) * (pvinfpsi(n,d, c, ce, a, psi))^(l-a) }
 
 ptotalpsi <- function (m, c, ce, l, a, psi) {
 	d = dens(m, l, a)
@@ -377,7 +379,7 @@ if (!is.null(opt$thpsi)) {
 				for(psi in unique(data$pcons)) {
 					for(activities in unique(data$activities)) {
 						newd = data
-						newd$errorrate = sapply(data$m, function (x) { 1 - ptotalpsi(x, ci, erasures, l, activities, psi) })
+						newd$errorrate = sapply(data$m, function (x) { ((1 - ptotalpsi(x, ci, erasures, l, activities, psi)/activities^2)) })
 						qpl <- qpl + geom_line(aes(y = newd$errorrate), color = "black")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
 					}
 				}

### 2014-07-05 sam.jl

@@ -439,7 +439,7 @@ const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) activities 
 	ipeta = peta / info_alphabet
 	ipaeta = paeta / info_alphabet
 	rceta = eta * exp(exp((log(m-1)- (c-erasures) * info_alphabet)))
-	psieta = rceta / (1 + xlog2(pcons) + xlog2(1-pcons))
+	psieta = rceta / (1 + xlog2(p_cons) + xlog2(1-p_cons))
 	return [ res[1] res[2] res[3] l c m real_gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop rceta psieta ]
 end
 

### 2014-07-06 Articles/article.tex
...

@@
 
-	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are independent, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$.
-Thus the density $d$ can be expressed like this :
+	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$.
+Since messages are independent, the density $d$ can be expressed like this :
 
@@
 
-	$\eta_m = (P_{retrieve} m ) \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \frac{c}{(c-c_e) \log_2{l \choose a }}$
+	$\eta_m = (P_{retrieve} m ) \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)}$
+	%\frac{c}{(c-c_e) \log_2{l \choose a }}
 
@@
 
+	To be really precise : (ne pas oublier de tenir compte changement des lois)
+	\begin{align*}
+	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
+	 &\times \left [ \sum_{y = 0}^a \left( \frac{{l-y \choose a} - \sum_{z = y+1}^{a} {l-z \choose a }}{{l \choose a}}\right)\sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a - y} P(n_{abc} < n)^{a - y} \right ]^{c_e}
+	\end{align*}
+
 	$P_{err} = 1 - P_{retrieve}$
@@
 	Marche mieux pour des bruits importants
+
+	$P(n_{v_c} = n_0 + \gamma ) = {a (c_k-1) \choose n_0} (1-\psi)^{n_0} \psi ^ { a (c_k-1) - n_0 }$
 

### 2014-07-06 sam.jl

@@ -398,8 +398,8 @@ const dict_rules = [ 0 => sum_of_sum!, 1 => sum_of_max!, 2 => mix_of_rules! ]
 const dict_corrupt = [ 0 => erase_clusters!, 1 => corrupt_clusters!, 2 => add_one_in_clusters!, 3 => add_some_in_clusters! ]
 
 function xlog2(x)
-	if x == 0
-		0
+	if x == 0.0
+		0.0
 	else
 		x * log2(x)
 	end

### 2014-07-06 sam.jl
correction mesures

@@ -438,7 +438,7 @@ const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) activities 
 	iaeta = aeta / info_alphabet
 	ipeta = peta / info_alphabet
 	ipaeta = paeta / info_alphabet
-	rceta = eta * exp(exp((log(m-1)- (c-erasures) * info_alphabet)))
+	rceta = eta * exp(exp2((log2(m-1)- (c-erasures) * info_alphabet)))
 	psieta = rceta / (1 + xlog2(p_cons) + xlog2(1-p_cons))
 	return [ res[1] res[2] res[3] l c m real_gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop rceta psieta ]
 end

### 2014-07-06 Articles/article.tex
correction mesures
peite modif

@@
 We propose a variant of the classic retrieving rule.
-We study its performance relatively to the former one for retrieving partially erased and corrupted messages.
-We provide both analytical and simulation results showing improvements in networks capacities.
+We study its performance relatively to the former one for retrieving partially erased or corrupted messages.
+We provide both analytical and simulation results showing improvements in both networks capacities and resilience.
 	 \end{abstract}
@@
 		\begin{figure}
-		\includegraphics[width=8.5cm]{Courbes/remplacement_figure4g1}
-		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
+		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
+		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
 	\end{figure}
@@
 	\begin{figure}
-		\includegraphics[width=8.5cm]{Courbes/1comppsic4l512g1}
-		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
+		\includegraphics[width=8.5cm]{Courbes/4portant_psi_c8l256e4}
+		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
 	\end{figure}

### 2014-07-06 astat.r

@@ -37,6 +37,7 @@ spec = matrix(c(
 'minpoolsize' , NA, 2, "integer",
 'minwinners' , NA, 2, "integer",
 'maxwinners' , NA, 2, "integer",
+'maxerasures' , NA, 2, "integer",
 'maxm' , 'M', 2, "integer",
 'maxgamma' , NA, 2, "integer",
 'minpcons' , NA, 2, "double",
@@ -137,6 +138,7 @@ if(!is.null(opt$maxpcons)) { data = subset(data, pcons <= opt$maxpcons) }
 if(!is.null(opt$minpoolsize)) { data = subset(data, poolsize >= opt$minpoolsize) }
 if(!is.null(opt$minwinners)) { data = subset(data, winners >= opt$minwinners) }
 if(!is.null(opt$maxwinners)) { data = subset(data, winners <= opt$maxwinners) }
+if(!is.null(opt$maxerasures)) { data = subset(data, erasures <= opt$maxerasures) }
 if(!is.null(opt$maxm)) { data = subset(data, m <= opt$maxm) }
 if(!is.null(opt$maxgamma)) { data = subset(data, gamma <= opt$maxgamma) }
 if(!is.null(opt$maxefficiency)) { data = subset(data, efficiency <= opt$maxefficiency) }

### 2014-07-06 astat.r
Ajout lettres grecques

@@ -260,10 +260,10 @@ if(!is.null(opt$ordstep)) {
    qpl <- qpl + scale_y_continuous(breaks = seq(0.0, 1.0, by = 0.1))#, max(data[,opt$ord]), by = opt$ordstep))#,#pretty_breaks(n = length(data[,opt$abs]))) #min(data[,opt$ord])
 }
 if(!is.null(opt$xlab)) {
-	qpl <- qpl + xlab(opt$xlab)
+	qpl <- qpl + xlab(opt$xlab)#expression(psi))#opt$xlab)
 }
 if(!is.null(opt$ylab)) {
-	qpl <- qpl + ylab(opt$ylab)
+	qpl <- qpl + ylab(opt$ylab)#expression(eta))#opt$ylab)
 }
 
 

### 2014-07-07 Articles/article.tex
Ajout lettres grecques
....

@@
 
-	edge : $(i, j)$
+	%edge : $(i, j)$
 
 	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$.
-Since messages are independent, the density $d$ can be expressed like this :
+Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed like this :
 
@@
 Neurons corresponding to the original message achieve this score.
-Besides the probability for a neuron $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^	{a(c-c_e)}$.
+Besides the probability for a neuron $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.
 
@@
 
+		\begin{figure}[!htb]
+		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
+		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
+	\end{figure}
+
 	\newpage
@@
 
+	Knowing the density of the network, we can compute the laws for scores achieved by different neurons in different clusters.
+Subscript $g$ will indicate a neuron being part of the message (it should be activated), subscript $b$ the contrary (the neuron should not be activated).
+Subscript $a$ means the neuron is activated.
+Subscript $c$ corresponds to a correct cluster, $e$ to an erroneous cluster.
 	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
+	Being connected to a given activated neuron occurs with probability $d$.
+However corrects neurons see their scores shift, as well as activated neurons respectively thanks to being part of the original message and the memory effect $\gamma$.
+We can express those probability laws as :
 
-	$P(n_{gc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
+	$P(n_{agc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
 
@@
 
+	A message is retrieved after one iteration, if and only if correct neurons achieve strictly the best scores.
+
 	\begin{align}
-	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
+	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
 	\end{align}
@@
 
-	$P(n_{gc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
+	$P(n_{agc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
 
@@
 	\newpage
-	$\,$
-	\newpage	
+
 	\begin{align*}
-	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
+	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
 	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
@@
 		\label{corruptth}
-	\end{figure}
-
-		\begin{figure}
-		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
-		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
 	\end{figure}
@@
 	\begin{figure}
-		\includegraphics[width=8.5cm]{Courbes/4portant_psi_c8l256e4}
+		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
 		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
@@
 
+	Absolute values of slopes diminish for increasing number of activities (resilience is better)
+
 	\nocite{*}
-	\bibliographystyle{numeric} % Le style est mis entre crochets.
-         \bibliography{bibli.bib}
+	\bibliographystyle{plain} % Le style est mis entre crochets.
+         \bibliography{bibli}
 \end{document}

### 2014-07-07 Articles/article.tex
...

@@
 \usepackage{float}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage[autolanguage]{numprint}
@@
 		$w = a$	is optimal
+		\begin{algorithm}
+		\caption{$a$-sum of sum}
+		\label{asumsum}
+		\begin{algorithmic}
+		\Require{}
+		\Statex
+		\While{step < I}
+		\If {$i\geq maxval$}
+   	 	\State $i\gets 0$
+		\Else
+    		\If {$i+k\leq maxval$}
+        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
+    		\EndIf
+		\EndIf
+		\EndWhile
+		\end{algorithmic}
+		\end{algorithm}
 
@@
 
-	$\eta_m = (P_{retrieve} m ) \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)}$
+	We define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
+A perfect associative memory would use exactly the same number of bits than the original messages and recover messages by maximum likelihood (ambiguities causing errors).
+Efficiency is the amount of information retrieved divided by the hardness of the problem.
+
+	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)}$
 	%\frac{c}{(c-c_e) \log_2{l \choose a }}

### 2014-07-07 Articles/article.tex
...

@@
 
+	The network is a symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits.
+Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \approx m(c \log_2{l \choose a } - \log_2(m) + 1) $.
+The information effectively stored in the network is $P_{retrieve} \times m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2}$.
+
+	Ambiguities would occur in a perfect associative memory if at least two messages would be identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{m-1}$.
+
 	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)}$
@@
 	\subsubsection{Simulations}
-		gap of theoretical density with density in simulations : under $1$ percent, see Figure \ref{densiteth}
+		Theoretical and empirical densities match very closely, see Figure \ref{densiteth} %gap of theoretical density with density in simulations : under $1$ percent,
 

### 2014-07-07 Articles/article.tex
...

@@
 \renewcommand{\thesubsubsection}{\alph{subsubsection}}
+
+\newcommand*\Let[2]{\State #1 $\gets$ #2}
+\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
+\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}
 
@@
 		\While{step < I}
-		\If {$i\geq maxval$}
+		\Let{a}{b}
+		\If {$i\ge maxval$}
    	 	\State $i\gets 0$
@@
 
-	Ambiguities would occur in a perfect associative memory if at least two messages would be identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{m-1}$.
+	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{m-1}$.
 
@@
 
-		New rule : Improves the retrieval rate for multiple iterations and/or corrupted messages.
+		The variant rule improves the retrieval rate for multiple iterations and/or corrupted messages.
 
-		The simulations agree with the analytical results for density and error rate.
+		The simulations agree with the analytical results for both density and error rate.
 
@@
 
-	To be really precise : (ne pas oublier de tenir compte changement des lois)
+	To be really precise : (ne pas oublier de tenir compte changement des lois, formule inexacte pour l'instant)
 	\begin{align*}
@@
 	\section{Resilience}
-	Spéculations en Français :
+	%Spéculations en Français 
+	%Peut-être un intérêt pour cluter based associative memories build from unreliable storage : si une arête porte moins d'info, on peut peut-être en supprimer plus (mais rajout ?!)
 
-	Peut-être un intérêt pour cluter based associative memories build from unreliable storage : si une arête porte moins d'info, on peut peut-être en supprimer plus (mais rajout ?!)
+	As information is shared accross connections with multiple activated neurons per cluster, they are more resilient to network damages.
 
-	Marche mieux pour des bruits importants
+	%Marche mieux pour des bruits importants
 
@@
 	\newpage
-	$\,$
-	\newpage
+	%$\,$
+	%\newpage
 	\begin{figure}
@@
 
+	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
+
+	$\eta_\psi = max_x \eta_{x, \psi}$
+
 	\nocite{*}

### 2014-07-07 Articles/article.tex
Autre formule.
...

@@
 \usepackage{algpseudocode}
+
 \usepackage[autolanguage]{numprint}
@@
 \newcommand*\Let[2]{\State #1 $\gets$ #2}
-\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
-\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}
+\algrenewcommand\algorithmicrequire{\textbf{Input:}}
+\algrenewcommand\algorithmicensure{\textbf{Output:}}
 
@@
 		\begin{algorithm}
-		\caption{$a$-sum of sum}
-		\label{asumsum}
+		\caption{$a$-sum of sum \label{asumsum}}
+
 		\begin{algorithmic}
@@
 		\Statex
-		\While{step < I}
+		\While{$s < I$}
 		\Let{a}{b}
@@
 
-	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)}$
+	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
 	%\frac{c}{(c-c_e) \log_2{l \choose a }}
@@
 
-	generalisation to multiple activities per cluster :
+	Generalisation to multiple activities per cluster :
+
+	For example an \textbf{a}ctivated \textbf{g}ood neuron in a \textbf{c}orrect cluster starts with a base score of $ a(c - c_e - 1) + \gamma$.
+The probability it has to be connected to a random activated neuron in an erroneous cluster is $d$.
+Thereby its law is :
 
 	$P(n_{agc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
+
+	The other laws are also easily expressed :
 
@@
 	\end{figure}
+
+		$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$
 
@@
 	\begin{figure}
+
 		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
-		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
+		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
 	\end{figure}
 
-	Absolute values of slopes diminish for increasing number of activities (resilience is better)
+	We compute values represented on figure \ref{comppsi} by scanning on the number of messages, so as to find the maximum efficiency.
+
+	After a transition, efficiencies seem to follow a linear decreasing low according to $\psi$.
+
+	Absolute values of slopes diminish for increasing number of activities per cluster. We can conclude multipartite cliques improve the resilience of the network.
 
@@
 
-	$\eta_\psi = max_x \eta_{x, \psi}$
+	$\eta_\psi = max_x \, \eta_{x, \psi}$
 

### 2014-07-07 Articles/article.tex
...

@@
 
+		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $a$-th position in the ordered array of scores.
+
 		$a$-rank
 
-		less biologically plausible rule
+		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $a$-th element in an array of $n$ elements is $O(n)$ in complexity.
 
-		same algorithmic complexity
+		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$)
 
-		$w = a$	is optimal
 		\begin{algorithm}
@@
 
-		\begin{algorithmic}
-		\Require{}
+		\begin{algorithmic}[1]
+		\Require{i}
+		\Procedure{Euclid}{$a,b$}
 		\Statex
@@
 		\EndWhile
+		\EndProcedure
 		\end{algorithmic}
@@
 
-	\begin{align}
-	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
-	\end{align}
+%	\begin{align}
+%	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
+%	\end{align}
+
+	\begin{align*}
+	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n)  P(n_{bc} < n)^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) P(n_{bc} < n)^{l-2} P(n_{abc} < n) \right ]^{c_e}
+	\end{align*}
 
@@
 		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
-		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
+		\caption{Comparison of efficiencies between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
 	\end{figure}

### 2014-07-07 astat.r
La personne ayant codée seq en R mérite le pire des sorts ! 1:0 = c(1,0), que c'est brillant !

@@ -305,10 +305,16 @@ pvpsi <- function(x, d, c, ce, a, psi) {
 	pp = pplus(d, psi) ;
 	choose(a * (c - ce), x) * pp^x * (1-pp)^(a*(c-ce) - x)
 }
-pcsuppsi <- function(n, c, ce, a, psi) sum(sapply((n+1):(a*(c-ce)), function(x) pcpsi(x, c, ce, a, psi)))
-
-pvinfpsi <- function(n,d, c, ce, a, psi) sum(sapply(0:(n-1), function(x) pvpsi(x, d, c, ce, a, psi)))
-
+pcsuppsi <- function(n, c, ce, a, psi) {
+	if( n >= a * (c-ce)) { 0 } else {
+	sum(sapply((n+1):(a*(c-ce)), function(x) pcpsi(x, c, ce, a, psi)))
+	}
+}
+pvinfpsi <- function(n,d, c, ce, a, psi) {
+	if(n<1) { 0 } else {
+		sum(sapply(0:(n-1), function(x) pvpsi(x, d, c, ce, a, psi)))
+	}
+}
 pcparpsi <- function(n, d, c, ce, l, a, psi) { (sum(sapply(0:(a-1), function(x) choose(a, x) * pcsuppsi(n, c, ce, a, psi)^x * pcpsi(n, c, ce, a, psi)^(a-x)))) * (pvinfpsi(n,d, c, ce, a, psi))^(l-a) }
 
 										#	function(x)  pcpsi(n, c, ce, a, psi)^a))) * pvinfpsi(n,d, c, ce, a, psi)^(l-a) }#(sum(sapply(0:(a-1), function(x) choose(a, x) * pcsuppsi(n, c, ce, a, psi)^x * pcpsi(n, c, ce, a, psi)^(a-x)))) * (pvinfpsi(n,d, c, ce, a, psi))^(l-a) }

### 2014-07-07 astat.r
Correction

@@ -387,7 +387,7 @@ if (!is.null(opt$thpsi)) {
 				for(psi in unique(data$pcons)) {
 					for(activities in unique(data$activities)) {
 						newd = data
-						newd$errorrate = sapply(data$m, function (x) { ((1 - ptotalpsi(x, ci, erasures, l, activities, psi)/activities^2)) })
+						newd$errorrate = sapply(data$m, function (x) { ((1 - ptotalpsi(x, ci, erasures, l, activities, psi))) })
 						qpl <- qpl + geom_line(aes(y = newd$errorrate), color = "black")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
 					}
 				}

### 2014-07-09 sam.jl
...

@@ -438,6 +438,7 @@ const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) activities 
 	iaeta = aeta / info_alphabet
 	ipeta = peta / info_alphabet
 	ipaeta = paeta / info_alphabet
+	# Deux mesures importantes
 	rceta = eta * exp(exp2((log2(m-1)- (c-erasures) * info_alphabet)))
 	psieta = rceta / (1 + xlog2(p_cons) + xlog2(1-p_cons))
 	return [ res[1] res[2] res[3] l c m real_gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop rceta psieta ]

### 2014-07-09 Articles/article.tex
La personne ayant codée seq en R mérite le pire des sorts ! 1:0 = c(1,0), que c'est brillant !
Ajout formule théorique.
..;
...
....

@@
 
-		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $a$-th position in the ordered array of scores.
+		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)
 
-		$a$-rank
+		%$a$-rank
 
-		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $a$-th element in an array of $n$ elements is $O(n)$ in complexity.
+		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $w$-th element in an array of $n$ elements is $O(n)$ in complexity.
 
-		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$)
+		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).
 
 		\begin{algorithm}
-		\caption{$a$-sum of sum \label{asumsum}}
+		\caption{$w$-sum of sum \label{asumsum}}
 
 		\begin{algorithmic}[1]
-		\Require{i}
-		\Procedure{Euclid}{$a,b$}
-		\Statex
+		\Require{$v$ a binary array of length $n = c\cdot l$}
+		\Procedure{Sum of sum}{$v, w$}
+		%\Statex
 		\While{$s < I$}
@@
 	%edge : $(i, j)$
+	Suppose we are trying to recover a message where $c_e$ clusters have been erased.
 
@@
 	% À corriger avec sommes multiparties
-	%$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$
+	$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$
 
-	%$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$
+	% Approx : ?! $P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$
 
-	Sans tenir compte du choix au hasard si plus sont activés.
+	Sans tenir compte du choix au hasard si plus sont activés. Pour une itération $\gamma = \infty$. Pour plusieurs $\gamma = 1$.
 
@@
 
-	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
+	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] P(n_v < n)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
 
@@
 	%\newpage
+	\begin{figure}[!htb]
+		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
+		\caption{2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
+		\label{psith}
+	\end{figure}
+
 	\begin{figure}
 
-		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
+		\includegraphics[scale=0.50]{Courbes/5portant_psi_c8l256e4}
 		\caption{Comparison of efficiencies between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
@@
 
+	\section{Maximum theoretical efficiency}
+		\begin{align*}
+			H(M) \approx m c \log_2 {l \choose a}\\
+			d = 1 - \left (1- \left(\frac{a}{l}\right)^2 \right)^m\\
+			m \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{l})^2)} \sim - \frac{l^2 \log_2(1-d) \log 2}{a^2}\\
+			\log_2 {l \choose a} = k c\\
+			\eta \sim c \log_2 {l \choose a} \log2(1-d) \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}\\
+			\eta \sim - 2 k  \log_2 ((1-d)a^{-2}\log 2\\
+			P_{\exists e} \le {l \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}\\
+			k^* = -\frac{a^2}{2} \log_2 (d)\\
+			\eta \sim \log_2 d \log_2 (1-d) \log 2\\
+			\eta_{max} \rightarrow \log 2
+		\end{align*}
+
 	\nocite{*}

### 2014-07-09 astat.r

@@ -101,6 +101,8 @@ noms = names(data)
 ## Solution la plus élégante trouvée : repassée à la version précédente de R, whaaaa !
 
 
+#data = subset(data, (gamma == 1 & maxiterations == 4) || (gamma > 50 & maxiterations == 1))
+
 data[data$winners == 0,]$winners <-  data[data$winners == 0,]$activities
 
 

### 2014-07-09 Articles/article.tex
Début description algo
...

@@
 		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).
-
+		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
 		\begin{algorithm}
@@
 		\begin{algorithmic}[1]
-		\Require{$v$ a binary array of length $n = c\cdot l$}
-		\Procedure{Sum of sum}{$v, w$}
+		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the weight matrix representing the network}
+		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
 		%\Statex
-		\While{$s < I$}
-		\Let{a}{b}
-		\If {$i\ge maxval$}
-   	 	\State $i\gets 0$
-		\Else
-    		\If {$i+k\leq maxval$}
-        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
-    		\EndIf
-		\EndIf
-		\EndWhile
+		\For{$s$ from $1$ to S}
+		\State $s = \gamma v + W v$
+		\For{$i$ from $1$ to $c$}
+			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
+			\For{$j$ from $1$ to $l$}
+			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
+			\EndFor
+		\EndFor
+		\EndFor
+		\State\Return v
 		\EndProcedure

### 2014-07-10 Articles/article.tex
...

@@
 		\For{$s$ from $1$ to S}
-		\State $s = \gamma v + W v$
+		\State $s \gets \gamma v + W v$
 		\For{$i$ from $1$ to $c$}
@@
 		\EndFor
-		\State\Return v
+		%\State\Return v
 		\EndProcedure
@@
 
-	number of neurons per cluster $l$
+	%number of neurons per cluster $l$
 
-	number of clusters $c$
+	%number of clusters $c$
 
-	number of erased clusters $c_e$
+	%number of erased clusters $c_e$
 
-	number of messages : $m$
+	%number of messages : $m$
 
-	number of activities per cluster : $a$
+	%number of activities per cluster : $a$
 
-	density : $d$
+	%density : $d$
 
@@
 
-	\[ d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^m \]
+	\begin{align}
+		\label{formula_density}
+		d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^m 
+	\end{align}
 
@@
 
-	The network is a symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits.
+	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits.
 Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \approx m(c \log_2{l \choose a } - \log_2(m) + 1) $.
@@
 
-	$\eta_{max} = \max_x \eta_x $
+	The maximum information that can be stored in the network is therefore $\eta = \max_x \eta_x $.
 
 	\subsubsection{Simulations}
-		Theoretical and empirical densities match very closely, see Figure \ref{densiteth} %gap of theoretical density with density in simulations : under $1$ percent,
+		Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent,
 
-		The variant rule improves the retrieval rate for multiple iterations and/or corrupted messages.
+		Simulations agree with the analytical results for error rate, see Figure \ref{erasuresth}.
 
-		The simulations agree with the analytical results for both density and error rate.
-
-	For one iteration (for erasures, not for errors), winner takes all is the same as $a$-winners take all.
+	For one iteration (for erasures, not for errors), "winner takes all" is the same as "$a$-winners take all".
 
 	For multiple iterations $a$-winners take all is a significant improvement.
+	%The variant of the rule significantly improves the retrieval rate over multiple iterations. (For one iteration, is is the same as taking only maximum scores.)
 
-	See Figure \ref{erasuresth}
+	%See Figure \ref{erasuresth}
 
-		"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
-
-	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
-	For one iteration, it is less efficient.
 	\begin{figure}[!htb]
@@
 
+		Figure \ref{comperth} shows improvements in capacities over unipartite cliques network. The more the problem is difficult, the more redundancies introduced by multipartite cliques are useful.
+
 		\begin{figure}[!htb]
@@
 		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
+		\label{comperth}
 	\end{figure}
-
-	\newpage
-	p
-	\newpage
-	$\,$
-	\newpage
+%	
+%	\newpage
+%	$\,$
+%	\newpage
+%	$\,$
+%	\newpage
 
@@
 
-	Knowing the density of the network, we can compute the laws for scores achieved by different neurons in different clusters.
+	Knowing the density of the network, which follows formula (\ref{formula_density}), we can compute the laws of probabilities for scores achieved by different type of neurons in different clusters.
+We can divide neurons in 5 groups.
 Subscript $g$ will indicate a neuron being part of the message (it should be activated), subscript $b$ the contrary (the neuron should not be activated).
-Subscript $a$ means the neuron is activated.
+Subscript $a$ means the neuron is already activated.
 Subscript $c$ corresponds to a correct cluster, $e$ to an erroneous cluster.
 	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
-	Being connected to a given activated neuron occurs with probability $d$.
-However corrects neurons see their scores shift, as well as activated neurons respectively thanks to being part of the original message and the memory effect $\gamma$.
+	Being connected to a given activated neuron in a corrupted cluster occurs with probability $d$, since errors are identically distributed.
+Moreover corrects neurons see their scores shift, as do all activated neurons respectively thanks to being part of the original message and the memory effect $\gamma$.
 We can express those probability laws as :
@@
 
+	Activated neurons benefits of the memory effect $\gamma$ :	
 	$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$
@@
 
-	\newpage
-
 	\begin{align*}
@@
 
-	To be really precise : (ne pas oublier de tenir compte changement des lois, formule inexacte pour l'instant)
-	\begin{align*}
-	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
-	 &\times \left [ \sum_{y = 0}^a \left( \frac{{l-y \choose a} - \sum_{z = y+1}^{a} {l-z \choose a }}{{l \choose a}}\right)\sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a - y} P(n_{abc} < n)^{a - y} \right ]^{c_e}
-	\end{align*}
+%	To be really precise : (ne pas oublier de tenir compte changement des lois, formule inexacte pour l'instant)
+%	\begin{align*}
+%	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
+%	 &\times \left [ \sum_{y = 0}^a \left( \frac{{l-y \choose a} - \sum_{z = y+1}^{a} {l-z \choose a }}{{l \choose a}}\right)\sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a - y} P(n_{abc} < n)^{a - y} \right ]^{c_e}
+%	\end{align*}
 
 	$P_{err} = 1 - P_{retrieve}$
-
-	See \ref{corruptth}
 
@@
 	\subsubsection{Simulations}
+	See Figure \ref{corruptth}
+	"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
+
+	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
+	For one iteration, it is less efficient.
 	\begin{figure}[!htb]
@@
 		$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$
-
-	\section{Conclusion}
-
-	%Marche mieux pouur de petits c --> le faire sur le sparse ?
 
@@
 
+		Multipartite cliques don't improve theoretical efficiency (for not accepting messages that weren't previously seen by the network)
+
+	\section{Conclusion}
+
+	%Marche mieux pouur de petits c --> le faire sur le sparse ?
+
 	\nocite{*}

### 2014-07-10 Articles/article.tex
...

@@
 We provide both analytical and simulation results showing improvements in both networks capacities and resilience.
+We compute asymptotic capacities of these networks.
 	 \end{abstract}
@@
 
-	Whence error rate in retrieving messages is : \[P_{err} = 1 -	\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)} \]
+	Whence error rate in retrieving messages is : 
+	\begin{align}	
+	P_{err} = 1 -	\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)} 
+	\end{align}
 
@@
 	\subsubsection{Analytical result}	
-	Formula for errors instead of erasures :
-
-	gc : good (à remplacer par right/wrong ?) neuron in correct cluster
-
-	ge : good neuron in erroneous cluster
-
-	abe : bad activated neuron in erroneous cluster
-
-	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster
-
-	bc : bad neuron in correct cluster
+%	Formula for errors instead of erasures : 
+%	
+%	gc : good (à remplacer par right/wrong ?) neuron in correct cluster
+%	
+%	ge : good neuron in erroneous cluster
+%	
+%	abe : bad activated neuron in erroneous cluster
+%	
+%	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster
+%	
+%	bc : bad neuron in correct cluster
+	Messages can be corrupted, our models for errors is : fix $c_e$ the number of erroneous clusters, we draw at random $c_e$ clusters and in each of these draw at random, uniformly, a new letter in the alphabet that will replace the old one (it could be the same).
 
@@
 We can express those probability laws as :
+	For example an \textbf{a}ctivated \textbf{g}ood neuron in a \textbf{c}orrect cluster starts with a base score of $ a(c - c_e - 1) + \gamma$.
+The probability it has to be connected to a random activated neuron in an erroneous cluster is $d$.
+Thereby its law is :
 
-	$P(n_{agc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
+	%$P(n_{agc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
+	$P(n_{agc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
 
 	Correct neurons in corrupted clusters achieve at least a score of $a(c - c_e)$. 
+	$P(n_{ge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
 
-	$P(n_{ge} = (c - c_e) + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$
+	%$P(n_{ge} = (c - c_e) + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$
 
-	Activated neurons benefits of the memory effect $\gamma$ :	
-	$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$
+	Activated neurons benefits of the memory effect $\gamma$ :	\\
+	$P(n_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$
+	%$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$
 
-	$P(n_{be} = x) = P(n_{bc} = x) = {c - 1 \choose x} d^x (1-d)^{c- 1 -x}$
+	%$P(n_{be} = x) = P(n_{bc} = x) = {c - 1 \choose x} d^x (1-d)^{c- 1 -x}$
+	Finally $P(n_{be} = x) = P(n_{bc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
 
@@
 
-	\begin{align*}
-	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n)  P(n_{bc} < n)^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) P(n_{bc} < n)^{l-2} P(n_{abc} < n) \right ]^{c_e}
-	\end{align*}
+%	\begin{align*}
+%	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{agc} = n)  P(n_{bc} < n)^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) P(n_{bc} < n)^{l-2} P(n_{abc} < n) \right ]^{c_e}
+%	\end{align*}
 
@@
 
-	Generalisation to multiple activities per cluster :
-
-	For example an \textbf{a}ctivated \textbf{g}ood neuron in a \textbf{c}orrect cluster starts with a base score of $ a(c - c_e - 1) + \gamma$.
-The probability it has to be connected to a random activated neuron in an erroneous cluster is $d$.
-Thereby its law is :
-
-	$P(n_{agc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
-
-	The other laws are also easily expressed :
-
-	$P(n_{ge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
-
-	$P(n_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$
-
-	$P(n_{be} = x) = P(n_{bc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
-
-	\begin{align*}
+	\begin{align}
 	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
-	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
-	\end{align*}
+	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e}
+	\end{align}
 
@@
 	\subsubsection{Simulations}
-	See Figure \ref{corruptth}
+	See Figure \ref{corruptth} compares the two rules.
 	"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
 
-	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
-	For one iteration, it is less efficient.
 	\begin{figure}[!htb]
@@
 	\section{Maximum theoretical efficiency}
-		\begin{align*}
-			H(M) \approx m c \log_2 {l \choose a}\\
-			d = 1 - \left (1- \left(\frac{a}{l}\right)^2 \right)^m\\
-			m \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{l})^2)} \sim - \frac{l^2 \log_2(1-d) \log 2}{a^2}\\
-			\log_2 {l \choose a} = k c\\
-			\eta \sim c \log_2 {l \choose a} \log2(1-d) \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}\\
-			\eta \sim - 2 k  \log_2 ((1-d)a^{-2}\log 2\\
-			P_{\exists e} \le {l \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}\\
-			k^* = -\frac{a^2}{2} \log_2 (d)\\
-			\eta \sim \log_2 d \log_2 (1-d) \log 2\\
-			\eta_{max} \rightarrow \log 2
-		\end{align*}
+		It was shown in \cite{oo}, asymptotic capacities of clique networks is $\log 2$. We generalise this result to multipartite cliques.
+		The entropy of the messages set can be approximated as $H(M) \approx m c \log_2 {l \choose a}$.
+From $d = 1 - \left (1- \left(\frac{a}{l}\right)^2 \right)^m$, we can deduce $m \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{l})^2)} \sim - \frac{l^2 \log_2(1-d) \log 2}{a^2}$.
+		We set $\log_2 {l \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$).
+It follows that $\eta \sim c \log_2 {l \choose a} \log2(1-d) \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
+
+		$\eta \sim - 2 k  \log_2 ((1-d)a^{-2}\log 2$.
+
+		We can bound the probability $P_{\exists e}$ for a message being "present" in the network, that is to mean adding it will not add any edge to the network.
+By union-bound $P_{\exists e} \le {l \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}$.
+
+		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]
 

### 2014-07-10 Articles/article.tex
...

@@
 
-		\subsubsection{The "$a$ winners take all" rule}
+		\subsubsection{The "$w$-winners take all" rule}
 
-		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)
+		To fully exploit the local regularity of the code (constant weight of $w$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)
 
@@
 		\begin{algorithmic}[1]
-		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the weight matrix representing the network}
+		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network}
 		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
@@
 
-	As information is shared accross connections with multiple activated neurons per cluster, they are more resilient to network damages.
+	As information is shared accross connections with multiple activated neurons per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
+$v_c$ will indicate a correct neuron that should be activated, $v$ the other type of neurons.
 
-	%Marche mieux pour des bruits importants
+	Our deviation model is drawn from \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}.
 
-	$P(n_{v_c} = n_0 + \gamma ) = {a (c_k-1) \choose n_0} (1-\psi)^{n_0} \psi ^ { a (c_k-1) - n_0 }$
+	$P(n_{v_c} = x + \gamma ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$
 
-	$P(n_{v_c} = n_0) = {a c_k \choose n_0} (1-\psi)^{n_0} \psi ^ { a c_k - n_0 }$
+	$P(n_{v_c} = x) = {a c_k \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e) - x }$
 
@@
 
-	\begin{figure}
+	\begin{figure}[!htb]
 
@@
 
+	Figure \ref{comppsi} seems to indicate a linear relationship (after a transition for multiple activities) between $\eta_\psi -\eta_0$ and $\psi$.
 	\section{Maximum theoretical efficiency}
 		It was shown in \cite{oo}, asymptotic capacities of clique networks is $\log 2$. We generalise this result to multipartite cliques.
-		The entropy of the messages set can be approximated as $H(M) \approx m c \log_2 {l \choose a}$.
+
+		The entropy of the messages set can be approximated as $H(\mathcal{M}) \approx m c \log_2 {l \choose a}$.
 From $d = 1 - \left (1- \left(\frac{a}{l}\right)^2 \right)^m$, we can deduce $m \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{l})^2)} \sim - \frac{l^2 \log_2(1-d) \log 2}{a^2}$.
@@
 	\nocite{*}
-	\bibliographystyle{plain} % Le style est mis entre crochets.
+	\bibliographystyle{numeric} % Le style est mis entre crochets.
          \bibliography{bibli}

### 2014-07-10 Articles/article.tex
...

@@
 
-	Our deviation model is drawn from \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}.
+	Our deviation model is the same as \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}, that is random binary noise on edges.
+
+	%gamma = infini meilleur sur une itération
 
@@
 
-	$P_+ = \psi (1 - d) + (1 - \psi) d$
+	The probability for an edge to be present in the network after damages is : $P_+ = \psi (1 - d) + (1 - \psi) d$.
 
@@
 
-	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$
-
+	%P(\mbox{no other vertex activated in any cluster})
+	\begin{align*}
+	P_{retrieve}=  \Bigg ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ]\\
+	\left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \Bigg)^{c_e}	
+	\end{align*}
 	\newpage

### 2014-07-10 Articles/article.tex
...

@@
 	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits.
-Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \approx m(c \log_2{l \choose a } - \log_2(m) + 1) $.
+Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + 1 + o(1)) $.
 The information effectively stored in the network is $P_{retrieve} \times m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2}$.
@@
 
-	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
+	$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
 	%\frac{c}{(c-c_e) \log_2{l \choose a }}
@@
 
-		$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$
+		$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$
 

### 2014-07-10 Articles/article.tex
...

@@
 \newcommand{\leg}[2]{\left(\dfrac{#1}{#2}\right)}
+
+\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
 
@@
 Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or neurons.
+Messages are considered independent and identically distributed.
 
@@
 
-	\begin{align}
+	\begin{align*}
 	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
-	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e}
-	\end{align}
+	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e} \numberthis \label{from_err_th}
+	\end{align*}
 
@@
 
-	As information is shared accross connections with multiple activated neurons per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
+	As information is shared across connections with multiple activated neurons per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
 $v_c$ will indicate a correct neuron that should be activated, $v$ the other type of neurons.
@@
 	%gamma = infini meilleur sur une itération
+	With probability $1 - \psi$, the correct vertex is still connected to a given activated neuron in an intact cluster.
+Thus $P(n_{v_c} = x ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$
 
-	$P(n_{v_c} = x + \gamma ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$
-
-	$P(n_{v_c} = x) = {a c_k \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e) - x }$
+	%$P(n_{v_c} = x) = {a c_k \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e) - x }$
 
 	The probability for an edge to be present in the network after damages is : $P_+ = \psi (1 - d) + (1 - \psi) d$.
-
-	$P(n_v = x) = {a c_k \choose x} P_+^x (1-P_+)^{a c_k -x }$
+So for other neurons $P(n_v = x) = {a (c - c_e) \choose x} P_+^x (1-P_+)^{a (c - c_e) -x }$.
 
 	% À corriger avec sommes multiparties
-	$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$
-
+%	$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$
+%	
 	% Approx : ?! $P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

### 2014-07-10 Articles/article.tex
résol bug bibtex

@@
 
-		a priori for noise on edges :
-
+	If $\gamma$ is big,
 	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] P(n_v < n)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
@@
 		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
-		\caption{2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
+		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
 		\label{psith}
@@
 	\nocite{*}
-	\bibliographystyle{numeric} % Le style est mis entre crochets.
-         \bibliography{bibli}
+	\bibliographystyle{plain} % Le style est mis entre crochets.
+         \bibliography{bibli.bib}{}
 \end{document}

### 2014-07-10 Articles/article.tex
...

@@
 
-	Each message $x = (x_i)_{1 \le i \le c}$ is mapped to $y = (y_i)_{1 \le i \le c}$ where $y_i$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).
+	Each message $x = (x_i)_{1 \le i \le c}$ is mapped to $y = (y_i)_{1 \le i \le c}$ where $y_i$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}
 
@@
 		\caption{$w$-sum of sum \label{asumsum}}
-
 		\begin{algorithmic}[1]
@@
 	%edge : $(i, j)$
+	We generalise results on erasures obtained in \cite{GriBer20117} to multipartie cliques.
+
 	Suppose we are trying to recover a message where $c_e$ clusters have been erased.
@@
 		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
-		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
+		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
 			\label{erasuresth}
@@
 %	bc : bad neuron in correct cluster
-	Messages can be corrupted, our models for errors is : fix $c_e$ the number of erroneous clusters, we draw at random $c_e$ clusters and in each of these draw at random, uniformly, a new letter in the alphabet that will replace the old one (it could be the same).
+
+	We provide a formula for error rate in case of messages with corrupted clusters.
+
+	Messages can be corrupted, our models for errors is : given $c_e$ the number of erroneous clusters, we draw at random $c_e$ clusters and in each of these draw at random, uniformly, a new letter in the alphabet that will replace the old one (it could be the same).
 
@@
 	Our deviation model is the same as \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}, that is random binary noise on edges.
+We generalise results of \cite{LedGriRabGro20145} to multipartite cliques.
 
@@
 	\section{Maximum theoretical efficiency}
-		It was shown in \cite{oo}, asymptotic capacities of clique networks is $\log 2$. We generalise this result to multipartite cliques.
+		It was shown in \cite{oo} that maximal asymptotic capacity of clique networks is $\log 2$. We generalise this result to multipartite cliques.
 
@@
 
-		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]
+		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $P_{\exists e}$ and $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]
 
@@
 
-	%Marche mieux pouur de petits c --> le faire sur le sparse ?
+	%Marche mieux pour de petits c --> le faire sur le sparse ?
 

### 2014-07-11 Articles/article.tex
...

@@
 	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ and $m = | \mathcal{M} |$.
-Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or neurons.
+Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or units.
 Messages are considered independent and identically distributed.
@@
 
-	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $1 \le j \le l$ and $1 \le i \le c$, the neuron $j$ in the cluster $i$ is activated if and only if $y_{i,j} = 1$ ; then adding all connections between activated neurons excepting for neurons sharing the same cluster.
-Thus we obtain a multipartite clique between activated neurons representing a message.
-The parameter $a$ describing the number of activated neurons per cluster will be called number of activities.
+	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $1 \le j \le l$ and $1 \le i \le c$, the unit $j$ in the cluster $i$ is activated if and only if $y_{i,j} = 1$ ; then adding all connections between activated units excepting for units sharing the same cluster.
+Thus we obtain a multipartite clique between activated units representing a message.
+The parameter $a$ describing the number of activated units per cluster will be called number of activities.
 
@@
 
-		To fully exploit the local regularity of the code (constant weight of $w$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)
+		To fully exploit the local regularity of the code (constant weight of $w$), we make a small modification the classic retrieving rule	by keeping activated all units that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)
 
@@
 
-	Thanks to the memory effect $\gamma$, activated neurons in a non-erased cluster stay activated and are the only ones doing so in their cluster.
-For neurons in erased clusters, the maximum attainable score is $a(c - c_e)$.
-Neurons corresponding to the original message achieve this score.
-Besides the probability for a neuron $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.
+	Thanks to the memory effect $\gamma$, activated units in a non-erased cluster stay activated and are the only ones doing so in their cluster.
+For units in erased clusters, the maximum attainable score is $a(c - c_e)$.
+Units corresponding to the original message achieve this score.
+Besides the probability for a unit $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.
 
@@
 
-	Since neurons representing messages are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$.
+	Since units representing messages are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$.
 
@@
 		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
-		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
+		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
 			\label{erasuresth}
@@
 		\includegraphics[width=8.5cm]{Courbes/5portant_erasures_c8l256}
-		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5}
+		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 units per cluster, 1000 sampled messages, pools of 5}
 		\label{comperth}
@@
 %	
-%	gc : good (à remplacer par right/wrong ?) neuron in correct cluster
+%	gc : good (à remplacer par right/wrong ?) unit in correct cluster
 %	
-%	ge : good neuron in erroneous cluster
+%	ge : good unit in erroneous cluster
 %	
-%	abe : bad activated neuron in erroneous cluster
+%	abe : bad activated unit in erroneous cluster
 %	
-%	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster
+%	be : others bad (à remplacer par wrong ou incorrect etc.) units in erroneous cluster
 %	
-%	bc : bad neuron in correct cluster
+%	bc : bad unit in correct cluster
 
@@
 
-	Knowing the density of the network, which follows formula (\ref{formula_density}), we can compute the laws of probabilities for scores achieved by different type of neurons in different clusters.
-We can divide neurons in 5 groups.
-Subscript $g$ will indicate a neuron being part of the message (it should be activated), subscript $b$ the contrary (the neuron should not be activated).
-Subscript $a$ means the neuron is already activated.
+	Knowing the density of the network, which follows formula (\ref{formula_density}), we can compute the laws of probabilities for scores achieved by different type of units in different clusters.
+We can divide units in 5 groups.
+Subscript $g$ will indicate a unit being part of the message (it should be activated), subscript $b$ the contrary (the unit should not be activated).
+Subscript $a$ means the unit is already activated.
 Subscript $c$ corresponds to a correct cluster, $e$ to an erroneous cluster.
-	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
-	Being connected to a given activated neuron in a corrupted cluster occurs with probability $d$, since errors are identically distributed.
-Moreover corrects neurons see their scores shift, as do all activated neurons respectively thanks to being part of the original message and the memory effect $\gamma$.
+	Correct units in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
+	Being connected to a given activated unit in a corrupted cluster occurs with probability $d$, since errors are identically distributed.
+Moreover corrects units see their scores shift, as do all activated units respectively thanks to being part of the original message and the memory effect $\gamma$.
 We can express those probability laws as :
-	For example an \textbf{a}ctivated \textbf{g}ood neuron in a \textbf{c}orrect cluster starts with a base score of $ a(c - c_e - 1) + \gamma$.
-The probability it has to be connected to a random activated neuron in an erroneous cluster is $d$.
+	For example an \textbf{a}ctivated \textbf{g}ood unit in a \textbf{c}orrect cluster starts with a base score of $ a(c - c_e - 1) + \gamma$.
+The probability it has to be connected to a random activated unit in an erroneous cluster is $d$.
 Thereby its law is :
@@
 
-	Correct neurons in corrupted clusters achieve at least a score of $a(c - c_e)$. 
+	Correct units in corrupted clusters achieve at least a score of $a(c - c_e)$. 
 	$P(n_{ge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
@@
 
-	Activated neurons benefits of the memory effect $\gamma$ :	\\
+	Activated units benefits of the memory effect $\gamma$ :	\\
 	$P(n_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$
@@
 
-	A message is retrieved after one iteration, if and only if correct neurons achieve strictly the best scores.
+	A message is retrieved after one iteration, if and only if correct units achieve strictly the best scores.
 
@@
 
-	%à changer : prendre en compte les $a$ neurones activés : problème des recouvrements !! on est trop optimiste si grand nombre d'activités (ou pessimiste ?)
+	%à changer : prendre en compte les $a$ unites activés : problème des recouvrements !! on est trop optimiste si grand nombre d'activités (ou pessimiste ?)
 
@@
 		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
-		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
+		\caption{2 activities per cluster, 4 clusters, 512 units per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
 		\label{corruptth}
@@
 
-	As information is shared across connections with multiple activated neurons per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
-$v_c$ will indicate a correct neuron that should be activated, $v$ the other type of neurons.
+	As information is shared across connections with multiple activated units per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
+$v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.
 
@@
 	%gamma = infini meilleur sur une itération
-	With probability $1 - \psi$, the correct vertex is still connected to a given activated neuron in an intact cluster.
+	With probability $1 - \psi$, the correct vertex is still connected to a given activated unit in an intact cluster.
 Thus $P(n_{v_c} = x ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$
@@
 	The probability for an edge to be present in the network after damages is : $P_+ = \psi (1 - d) + (1 - \psi) d$.
-So for other neurons $P(n_v = x) = {a (c - c_e) \choose x} P_+^x (1-P_+)^{a (c - c_e) -x }$.
+So for other units $P(n_v = x) = {a (c - c_e) \choose x} P_+^x (1-P_+)^{a (c - c_e) -x }$.
 
@@
 		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
-		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
+		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
 		\label{psith}
@@
 		\includegraphics[scale=0.50]{Courbes/5portant_psi_c8l256e4}
-		\caption{Comparison of efficiencies between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
+		\caption{Comparison of efficiencies between different number of activities per cluster :  8 clusters, 256 units per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
 	\end{figure}

### 2014-07-11 Articles/article.tex
...

@@
 We study its performance relatively to the former one for retrieving partially erased or corrupted messages.
-We provide both analytical and simulation results showing improvements in both networks capacities and resilience.
+We provide both analytical and simulation results showing improvements in both networks efficiencies and resilience to damages.
 We compute asymptotic capacities of these networks.
@@
 
-	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $1 \le j \le l$ and $1 \le i \le c$, the unit $j$ in the cluster $i$ is activated if and only if $y_{i,j} = 1$ ; then adding all connections between activated units excepting for units sharing the same cluster.
+	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $i$ and $j$ such as $1 \le j \le l$ and $1 \le i \le c$, the unit $j$ in the cluster $i$ is activated if and only if $y_i[j] = 1$ ; then adding all connections between activated units excepting for units sharing the same cluster.
 Thus we obtain a multipartite clique between activated units representing a message.
@@
 
-		Retrieving messages occurs by message passing.
+		Retrieving messages occurs by message passing. We adapt the rule first developed in \cite{GriBer20117} to multipartite cliques.
 
-		\subsubsection{The "winner takes all" rule}
-
-		take only maximum score
-
-		\subsubsection{The "$w$-winners take all" rule}
+%		\subsubsection{The "winner takes all" rule}
+%		
+%		take only maximum score
+%	
+%		\subsubsection{The "$w$-winners take all" rule}
 
@@
 
-		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $w$-th element in an array of $n$ elements is $O(n)$ in complexity.
+		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $w$-th greater element in an array of $n$ elements is $O(n)$ in complexity.
 
@@
 
-	Suppose we are trying to recover a message where $c_e$ clusters have been erased.
+	Suppose we are trying to recover a message where $c_e$ clusters have been erased (i.e. all units in those clusters are set to $0$).
 
@@
 	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits.
-Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + 1 + o(1)) $.
-The information effectively stored in the network is $P_{retrieve} \times m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2}$.
+Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula).
+The information effectively stored in the network is $P_{retrieve} \times  \frac{2m \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.
 
@@
 
-	$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
+	$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
 	%\frac{c}{(c-c_e) \log_2{l \choose a }}
@@
 
+	The probability for all good neurons of a correct cluster (resp.
+of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_c (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp.
+$P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k}$)
+
+%	\begin{align*}
+%	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
+%	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e} \numberthis \label{from_err_th}
+%	\end{align*}
 		\begin{align*}
-	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
-	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e} \numberthis \label{from_err_th}
+	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_g(x) P(n_{bc} < x)^{l-a} \right ]^{c - c_e}\\ 
+	 &\times \left [ \sum_{x = 1}^{a(c-1) +\gamma} P_e(x) P(n_{be} < x)^{l-2a} P(n_{abe} < x)^a \right ]^{c_e} \numberthis \label{from_err_th}
 	\end{align*}
@@
 	$P_{err} = 1 - P_{retrieve}$
-
-	\newpage
-	$\,$
-	\newpage
 
@@
 
-		$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$
+		$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$
 
@@
 
+	\newpage
+
 	%P(\mbox{no other vertex activated in any cluster})
@@
 		\includegraphics[scale=0.50]{Courbes/5portant_psi_c8l256e4}
-		\caption{Comparison of efficiencies between different number of activities per cluster :  8 clusters, 256 units per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
+		\caption{Comparison of evolutions of efficiency with increasing damages between different number of activities per cluster :  8 clusters, 256 units per cluster%, 1000 sampled messages, pools of 5 networks
+		\label{comppsi}}
 	\end{figure}
@@
 
-	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
+	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
 
@@
 		We set $\log_2 {l \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$).
-It follows that $\eta \sim c \log_2 {l \choose a} \log2(1-d) \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
+It follows that $\eta \sim \frac{m c \log_2 {l \choose a}}{l^2 {c \choose 2}} \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
 
-		$\eta \sim - 2 k  \log_2 ((1-d)a^{-2}\log 2$.
+		$\eta \sim - 2 k  a^{-2}\log 2 \times \log_2 (1-d)$.
 
-		We can bound the probability $P_{\exists e}$ for a message being "present" in the network, that is to mean adding it will not add any edge to the network.
+		We can bound the probability $P_{\exists e}$ for a message being "wrongly present" in the network, that is to mean adding it will not add any edge to the network albeit it is not in $\mathcal{M}$.
 By union-bound $P_{\exists e} \le {l \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}$.

### 2014-07-11 sam.jl

@@ -308,7 +308,7 @@ function estimate_efficiency(l, c, m, alphabet_size, activities = 1)
 		info_alphabet = sum(log2((l-activities+1) : l)) - sum(log2(1:activities))				
 	end
 
-	2m * (c * info_alphabet - log2(m) + 1)/(c*(c-1)*l^2),  2m * c * info_alphabet / (c*(c-1)*l^2), info_alphabet ##1 == log2(2) == 1, this is where the term comes from (2nd order)
+	2m * (c * info_alphabet - log2(m) + 1/log(2))/(c*(c-1)*l^2),  2m * c * info_alphabet / (c*(c-1)*l^2), info_alphabet ##1 == log2(2) == 1, this is where the term comes from (2nd order)
 end
 
 

### 2014-07-11 Articles/article.tex
...

@@
 
-		To fully exploit the local regularity of the code (constant weight of $w$), we make a small modification the classic retrieving rule	by keeping activated all units that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)
+		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all units that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)
 
@@
 
-		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).
+		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$).
 		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
@@
 		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
-		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
+		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result (for one iteration) in continuous black}
 			\label{erasuresth}
@@
 	The probability for all good neurons of a correct cluster (resp.
-of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_c (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp.
+of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_{ac} (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp.
 $P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k}$)
@@
 		\begin{align*}
-	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_g(x) P(n_{bc} < x)^{l-a} \right ]^{c - c_e}\\ 
+	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_{ac}(x) P(n_{bc} < x)^{l-a} \right ]^{c - c_e}\\ 
 	 &\times \left [ \sum_{x = 1}^{a(c-1) +\gamma} P_e(x) P(n_{be} < x)^{l-2a} P(n_{abe} < x)^a \right ]^{c_e} \numberthis \label{from_err_th}
 	\end{align*}
+
+	with the approximation that there is few activated units that should be kept active in an erronenous cluster.
 

### 2014-07-11 Articles/article.tex
...

@@
 
+		Associative memories
+
+		Recently, a new type of associative memories was proposed by Gripon and Berrou \cite{GriBer20117}.
+
+		GBNN can also be used to retrieve messages from erroneous versions of them. We derive a formula for error rate in case of errors on messages.
+
+		Fault tolerance of those networks was extensively studied in \cite{LedGriRabGro20145}. We extend this to multipartite cliques and show significant improvements in resilience to faults.
+
 	\section{Networks of neural cliques}
@@
 Messages are considered independent and identically distributed.
+
+	Our goal is to store messages so as to be able to retrieve them from partial or erroneous versions of them.
 
@@
 
-	As information is shared across connections with multiple activated units per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
+	As information on a message is shared across connections with multiple activated units per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
 $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.

### 2014-07-11 Articles/article.tex
...

@@
 	\begin{figure}[!htb]
-		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
+		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
 		\caption{Theoretical and empirical densities}
@@
 
-	If $\gamma$ is big,
-	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] P(n_v < n)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
+	The probability for all correct units to achieve a score equal or greater than $x$, with at least one achieving a score of $x$ is $P_c (x) =\sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = x)^k P(n_{v_c} > x)^{a-k} $
 
-	\newpage
+	If $\gamma$ is big enough,
+	$P(\mbox{no other vertex activated in this cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
 
 	%P(\mbox{no other vertex activated in any cluster})
-	\begin{align*}
-	P_{retrieve}=  \Bigg ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ]\\
-	\left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \Bigg)^{c_e}	
-	\end{align*}
-	\newpage
-	%$\,$
-	%\newpage
+%	\begin{align*}
+%	P_{retrieve}=  \Bigg ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ]\\
+%	\left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \Bigg)^{c_e}	
+%	\end{align*}
+
+	\begin{align}
+	P_{retrieve}=  \left( \sum_{x = 1}^{a ( c- c_e)} P_c(x) P(n_v <x)^{l-a} \right )^{c_e}
+	\label{psi_formula_th}
+	\end{align}
+
 	\begin{figure}[!htb]
@@
 
-	Absolute values of slopes diminish for increasing number of activities per cluster. We can conclude multipartite cliques improve the resilience of the network.
+	Absolute values of slopes diminish for increasing number of activities per cluster. We can conclude usage of multipartite cliques improve the resilience of the network.
 

### 2014-07-11 sam.jl

@@ -55,7 +55,7 @@ end
 # m : number of messages
 # optional useBitArray : if set to true, the function is using a BitMatrix instead of a boolean array (the size of a boolean is a byte) ; as of the writing of this code, this hurts execution time (by a factor of around 2 or 3). It should only be used if memory is a bottleneck.
 # create_messages generate m random messages, and store them in sparseMessages according to the neural scheme ; then returns both messages and sparseMessages in a tuple
-function create_messages(l, c, m, activities = 1)#; useBitArray = false)
+function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = false)
 
 	const n = l * c
 	#if !useBitArray
@@ -110,7 +110,7 @@ end
 
 # l, c, m and useBitArray have the same meaning as above
 # messages is an array that represents the messages the output network is storing.
-function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree = 0, activities = 1, only_drop = false)# ; useBitArray = false )
+function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree = 0, activities = 1, only_drop = false, csparse = 0)# ; useBitArray = false )
 	const n = l * c
 	#if !useBitArray
 		network = zeros(Bool,n,n)
@@ -201,9 +201,9 @@ end
 	#end
 
 # This function is a commodity for interactive purpose.
-function create_both(l, c, m, p_cons = 0.0, degree = 0, activities = 1, only_drop = false) # ; useBitArray = false)
-	@time messages, sparseMessages, l2, alphabet_size = create_messages(l, c, m, activities) #, useBitArray = useBitArray)
-	@time network = create_network(l2, c, m, messages, sparseMessages, p_cons, degree, activities, only_drop) #, useBitArray = useBitArray)
+function create_both(l, c, m, p_cons = 0.0, degree = 0, activities = 1, only_drop = false, csparse = 0) # ; useBitArray = false)
+	@time messages, sparseMessages, l2, alphabet_size = create_messages(l, c, m, activities, csparse) #, useBitArray = useBitArray)
+	@time network = create_network(l2, c, m, messages, sparseMessages, p_cons, degree, activities, only_drop, csparse) #, useBitArray = useBitArray)
[…]

### 2014-07-11 test.jl

@@ -29,17 +29,17 @@ function init_file(fileprefix, dir = "results")
 	#	"#Clique network parameters : fsum=$(fsum), fcorrupt=$(fcorrupt)\n"
 	const suffix = ".csv" #"$(fsum)__$(fcorrupt)"
 	const filename = "$(dir)/$(fileprefix)$suffix"
-	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta,ieta,iaeta,infoalphabet,onlydrop,rceta,psieta\n"
+	firstline = isfile(filename) ? "" : "errorrate,iterations,density,l,c,m,gamma,erasures,maxiterations,tests,efficiency,fsum,fcorrupt,pcons,pdes,degree,activities,alphabetsize,winners,poolsize,efficacy,refficacy,retrievedproportion,eta,aeta,peta,paeta,ipeta,ipaeta,ieta,iaeta,infoalphabet,onlydrop,rceta,psieta,csparse\n"
 	open(filename, "a") do file
 		write(file, firstline)
 	end
 	return filename
 end
 
-function enregistre(filename ; trials=10, l=128, c=8, m=5000, ugamma = 1, erasures=4 , iterations = 4, tests=1000, fsum=Sam.sum_of_sum!, fcorrupt = Sam.erase_clusters!, nowrite = false, dir = "results", p_cons = 0.0, p_des = 0.0, degree = degree, activities = 1, winners = 1, pool_size = 1, only_drop = false)
+function enregistre(filename ; trials=10, l=128, c=8, m=5000, ugamma = 1, erasures=4 , iterations = 4, tests=1000, fsum=Sam.sum_of_sum!, fcorrupt = Sam.erase_clusters!, nowrite = false, dir = "results", p_cons = 0.0, p_des = 0.0, degree = degree, activities = 1, winners = 1, pool_size = 1, only_drop = false, csparse = 0)
 	@assert erasures <= c
 	for i=1:trials
-		@time res = Sam.output_test(l, c, m, ugamma, erasures, iterations, tests, fsum, fcorrupt, p_cons, p_des, degree, activities, winners, pool_size, only_drop)
[…]

### 2014-07-12 sam.jl
Modif sparse début

@@ -59,9 +59,11 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 
 	const n = l * c
 	#if !useBitArray
-		#sparseMessages = spzeros(Uint8, n,m)
-
-		sparseMessages = zeros(Bool,n, m)
+	if csparse == 0 || csparse == c
+		sparseMessages = zeros(Bool, n, m)
+	else
+		sparseMessages = spzeros(Uint8, n, m)
+	end
 	#else	
 	#	sparseMessages = falses(m,n)
 	#end
@@ -113,8 +115,12 @@ end
 function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree = 0, activities = 1, only_drop = false, csparse = 0)# ; useBitArray = false )
 	const n = l * c
 	#if !useBitArray
+	est_sparse = !(csparse == 0 || csparse == c)
+	if !est_sparse
 		network = zeros(Bool,n,n)
-		#network = spzeros(Uint8,n,n)
+	else
+		network = spzeros(Uint8,n,n)
+	end
 	#else
 	#	network = falses(n, n) 
 	#end
@@ -133,7 +139,11 @@ function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree 
 		else
 			const ind_n = [1:n]
 			for i=1:m
-				activations = ind_n[reshape(sparseMessages[:, i], n) .> 0]
+				if !est_sparse
+					activations = ind_n[reshape(sparseMessages[:, i], n) .> 0]
+				else
+					activations = ind_n[reshape(reshape(sparseMessages[:, i], n, 1) .> 0, n)]
+				end
 				network[activations, activations] = 1
 			end
 		end
@@ -371,6 +381,7 @@ function test_network(l_init = 128, c = 8, m = 5000, gamma = 1, erasures = 4, it
 	@time const messages, sparseMessages, network, l_t, alphabet_size = create_both(l_init, c, m, p_cons, degree, activities, only_drop, csparse)#, useBitArray = useBitArray)
 	const l = l_t
 	const n = l * c
+	const est_sparse = !(csparse == 0 || csparse == c)
 	const winners = (if declared_winners <= 0 activities else declared_winners end)
 	println("Messages created and translated.")
 	dens = density(l, c, network)
@@ -380,7 +391,11 @@ function test_network(l_init = 128, c = 8, m = 5000, gamma = 1, erasures = 4, it
[…]

### 2014-07-16 sam.jl
Réseau sparse

@@ -21,6 +21,10 @@ function rand_combination(n, m)
 	res
 end
 
+function skelet_rand_combination(n, m)
+	[1:n][rand_combination(n, m)]
+end
+
 function alphabet_table(l, activities)
 	table = cell(binomial(l, activities))
 	comb = combinations(1:l, activities)
@@ -58,8 +62,9 @@ end
 function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = false)
 
 	const n = l * c
+	const est_sparse = (csparse != c)
 	#if !useBitArray
-	if csparse == 0 || csparse == c
+	if !est_sparse
 		sparseMessages = zeros(Bool, n, m)
 	else
 		sparseMessages = spzeros(Uint8, n, m)
@@ -70,7 +75,7 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 	if activities <= 1  # bad "if" but the goal is to keep different test files functioning
 		messages = rand(1:l,m,c)
 		for i=1:m
-			for j=1:c
+			for j= (if !est_sparse 1:c else skelet_rand_combination(c, csparse) end)
 				sparseMessages[(j-1)*l+messages[i,j], i] = 1
 			end
 		end
@@ -101,7 +106,7 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 		#end
 		#graine = vcat(ones(Bool, activities), zeros(Bool, l - activities))
 		for i = 1:m
-			for j=1:c
+			for j= (if !est_sparse 1:c else skelet_rand_combination(c, csparse) end)
 				sparseMessages[(j-1)*l+1:j*l, i] = rand_combination(l, activities)#shuffle(graine)
 			end
 		end
@@ -115,7 +120,7 @@ end
 function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree = 0, activities = 1, only_drop = false, csparse = 0)# ; useBitArray = false )
 	const n = l * c
 	#if !useBitArray
-	est_sparse = !(csparse == 0 || csparse == c)
+	est_sparse = (csparse != c)
 	if !est_sparse
 		network = zeros(Bool,n,n)
 	else
@@ -246,18 +251,28 @@ end
 # gamma is the memory parameter
 # indexes is not used in this function (Trouver une façon de s'en débarasser ?)
 # applies of one pass of the sum of sum rule
[…]

### 2014-07-16 sam.jl
OK

@@ -73,10 +73,20 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 	#	sparseMessages = falses(m,n)
 	#end
 	if activities <= 1  # bad "if" but the goal is to keep different test files functioning
-		messages = rand(1:l,m,c)
-		for i=1:m
-			for j= (if !est_sparse 1:c else skelet_rand_combination(c, csparse) end)
-				sparseMessages[(j-1)*l+messages[i,j], i] = 1
+		messages = rand(1:l,m,(if !est_sparse c else csparse end))
+		if !est_sparse
+			for i=1:m
+				for j=1:c
+					sparseMessages[(j-1)*l+messages[i,j], i] = 1
+				end
+			end
+		else
+			for i=1:m
+				k = 1
+				for j= skelet_rand_combination(c, csparse)
+					sparseMessages[(j-1)*l+messages[i,k], i] = 1
+					k += 1
+				end
 			end
 		end
 		return (messages, sparseMessages, l, l)
@@ -131,7 +141,7 @@ function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree 
 	#end
 #	if p_cons == 1.0  # repetition for cache efficiency in the case one activate all the connections.
 	if degree <= 0
-		if activities <= 1
+		if activities <= 1 && !est_sparse
 			for i=1:m
 				for j=1:c
 					for k=1:c
@@ -326,14 +336,14 @@ function mix_of_rules!(l, c, network, input, gamma, indexes, degree = 0, activit
 	sum_of_max!(l, c, network, input, gamma, indexes, degree, activities, winners)
 end
 
-function estimate_efficiency(l, c, m, alphabet_size, activities = 1) 
+function estimate_efficiency(l, c, m, alphabet_size, activities = 1, csparse = 0) 
 	if alphabet_size > 1
 		info_alphabet = log2(alphabet_size)
 	else
 		info_alphabet = sum(log2((l-activities+1) : l)) - sum(log2(1:activities))				
 	end
 
-	2m * (c * info_alphabet - log2(m) + 1/log(2))/(c*(c-1)*l^2),  2m * c * info_alphabet / (c*(c-1)*l^2), info_alphabet ##1 == log2(2) == 1, this is where the term comes from (2nd order)
[…]

### 2014-07-16 sam.jl
Correction sparse, reste accélération messages

@@ -67,7 +67,7 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 	if !est_sparse
 		sparseMessages = zeros(Bool, n, m)
 	else
-		sparseMessages = spzeros(Uint8, n, m)
+		sparseMessages = spzeros(Bool, n, m)
 	end
 	#else	
 	#	sparseMessages = falses(m,n)
@@ -134,7 +134,7 @@ function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree 
 	if !est_sparse
 		network = zeros(Bool,n,n)
 	else
-		network = spzeros(Uint8,n,n)
+		network = spzeros(Bool,n,n)
 	end
 	#else
 	#	network = falses(n, n) 
@@ -151,6 +151,8 @@ function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree 
 					end
 				end
 			end
+		elseif est_sparse
+			network = sparseMessages * sparseMessages'
 		else
 			const ind_n = [1:n]
 			for i=1:m
@@ -262,8 +264,8 @@ end
 # indexes is not used in this function (Trouver une façon de s'en débarasser ?)
 # applies of one pass of the sum of sum rule
 function sum_of_sum!(l, c, network, input, gamma, indexes, degree = 0, activities= 1, winners = 1, csparse = 0)
-	prod = gamma * input + network * input
 	if csparse == c
+		prod = gamma * input + network * input
 		for i=1:c
 			if winners <= 1
 				maxi = maximum(prod[(i-1)*l+1:i*l]) 
@@ -277,6 +279,8 @@ function sum_of_sum!(l, c, network, input, gamma, indexes, degree = 0, activitie
 			end
 		end
 	else
+		cinput = int(input)
+		prod = gamma * cinput + network * cinput
 		positive_activations = nonzeros(prod)
 		maxi = (if length(positive_activations) < (csparse * winners) 0 else select(positive_activations, (csparse * winners), rev = true) end)
 		for i=1:c
@@ -342,8 +346,8 @@ function estimate_efficiency(l, c, m, alphabet_size, activities = 1, csparse = 0
 	else
 		info_alphabet = sum(log2((l-activities+1) : l)) - sum(log2(1:activities))				
 	end
-
[…]

### 2014-07-16 Articles/article.tex
...

@@
 
-	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ and $m = | \mathcal{M} |$.
+	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and $m = | \mathcal{M} |$.
 Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or units.
@@
 		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$).
-		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
-		\begin{algorithm}
+		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
+		\begin{algorithm}[!htb]
 		\caption{$w$-sum of sum \label{asumsum}}
 		\begin{algorithmic}[1]
-		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network}
+		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
 		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
 		%\Statex
-		\For{$s$ from $1$ to S}
+		\For{$s$ from $1$ to $S$}
 		\State $s \gets \gamma v + W v$
@@
 	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$.
-Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed like this :
+Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed as :
 
@@
 
-	We define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
+	In order to compare different networks using different alphabets, we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
 A perfect associative memory would use exactly the same number of bits than the original messages and recover messages by maximum likelihood (ambiguities causing errors).
@@
 
-	The maximum information that can be stored in the network is therefore $\eta = \max_x \eta_x $.
+	The maximum information that can be stored in the network is therefore $\eta = \max_x \eta_x $, which we will define as the efficiency of the network.
 
@@
 
-	The probability for all good neurons of a correct cluster (resp.
+	The probability for all good units of a correct cluster (resp.
 of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_{ac} (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp.
-$P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k}$)
+$P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = x)^k P(n_{ge} > x)^{a-k}$)
 
@@
 	\section{Resilience}
+	\subsection{Analytical result}
 	%Spéculations en Français 
@@
 
-	As information on a message is shared across connections with multiple activated units per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
+	As information on a message is shared across connections with multiple activated units per cluster, such networks are more resilient to damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
 $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.
@@
 	%gamma = infini meilleur sur une itération
-	With probability $1 - \psi$, the correct vertex is still connected to a given activated unit in an intact cluster.
+	We assume $\gamma = \infty$ for one iteration as it prevents activated neurons to be deactivated.
+	With probability $1 - \psi$, one correct vertex is still connected to a given activated unit in an intact cluster.
 Thus $P(n_{v_c} = x ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$
@@
 
-	Sans tenir compte du choix au hasard si plus sont activés. Pour une itération $\gamma = \infty$. Pour plusieurs $\gamma = 1$.
+	%Sans tenir compte du choix au hasard si plus sont activés. Pour une itération $\gamma = \infty$. Pour plusieurs $\gamma = 1$.
 
@@
 
-	If $\gamma$ is big enough,
-	$P(\mbox{no other vertex activated in this cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
+	%If $\gamma$ is big enough,
+	It follows that $P(\mbox{no other vertex activated in one cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{l-a}$.%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
 
@@
 
+	\subsection{Simulations}
 	\begin{figure}[!htb]
@@
 	\section{Maximum theoretical efficiency}
-		It was shown in \cite{oo} that maximal asymptotic capacity of clique networks is $\log 2$. We generalise this result to multipartite cliques.
+		It was shown in \cite{Palm1980} that maximal asymptotic capacity of Willshaw networks is $\log 2$. We adapt this result to multipartite clique clustered networks.
 

### 2014-07-16 sam.jl

@@ -115,9 +115,11 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 		#	end
 		#end
 		#graine = vcat(ones(Bool, activities), zeros(Bool, l - activities))
-		for i = 1:m
-			for j= (if !est_sparse 1:c else skelet_rand_combination(c, csparse) end)
-				sparseMessages[(j-1)*l+1:j*l, i] = rand_combination(l, activities)#shuffle(graine)
+		const ind_l = [1:l]
+		for i=1:m
+			for j = (if !est_sparse 1:c else skelet_rand_combination(c, csparse) end)
+				#sparseMessages[(j-1)*l+1:j*l, i] = rand_combination(l, activities)#shuffle(graine)
+				sparseMessages[(j-1)*l + ind_l[rand_combination(l, activities)], i] = 1
 			end
 		end
 		###############" Attention les messages n'ont plus aucun rapport avec les sparseMessages !!!!!!!

### 2014-07-16 Articles/article.tex
...

@@
 	\subsection{Simulations}
+
+	With random noise on edges, hardness of the problem must take into account the capacity of the binary symmetric channel (the closer $\psi$ is of $0.5$, the harder the problem is).
+Our new is efficiency is written as :
+	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
+
+	$\eta_\psi = max_x \, \eta_{x, \psi}$
 	\begin{figure}[!htb]
@@
 
-	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
-
-	$\eta_\psi = max_x \, \eta_{x, \psi}$
-
 	Figure \ref{comppsi} seems to indicate a linear relationship (after a transition for multiple activities) between $\eta_\psi -\eta_0$ and $\psi$.
@@
 
-		Multipartite cliques don't improve theoretical efficiency (for not accepting messages that weren't previously seen by the network)
+		Multipartite cliques don't improve theoretical asymptotic efficiency (for not accepting messages that weren't previously seen by the network).
 

### 2014-07-16 sam.jl

@@ -4,7 +4,7 @@ module Sam
 
 
 #Floyd algorithm : contrib ?
-function rand_combination(n, m)
+function floyd_combination(n, m)
 	s = Set()
 	for j=n-m+1:n
 		t = rand(1:j)
@@ -14,11 +14,20 @@ function rand_combination(n, m)
 			push!(s, j)
 		end
 	end
+	s
+end
+
+function rand_combination(n, m)
+	s = floyd_combination(n, m)
 	res = zeros(Bool, n)
 	for i in s
 		res[i] = 1
 	end
 	res
+end
+
+function skelet2_rand_combination(n, m)
+	int(collect(floyd_combination(n, m)))
 end
 
 function skelet_rand_combination(n, m)
@@ -119,7 +128,8 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 		for i=1:m
 			for j = (if !est_sparse 1:c else skelet_rand_combination(c, csparse) end)
 				#sparseMessages[(j-1)*l+1:j*l, i] = rand_combination(l, activities)#shuffle(graine)
-				sparseMessages[(j-1)*l + ind_l[rand_combination(l, activities)], i] = 1
+				#sparseMessages[(j-1)*l + ind_l[rand_combination(l, activities)], i] = 1
+				sparseMessages[(j-1)*l + skelet2_rand_combination(l, activities), i] = 1
 			end
 		end
 		###############" Attention les messages n'ont plus aucun rapport avec les sparseMessages !!!!!!!

### 2014-07-16 sam.jl
Beaucoup plus rapide sparse

@@ -27,7 +27,9 @@ function rand_combination(n, m)
 end
 
 function skelet2_rand_combination(n, m)
-	int(collect(floyd_combination(n, m)))
+	a = int(collect(floyd_combination(n, m)))
+	sort!(a)
+	a
 end
 
 function skelet_rand_combination(n, m)
@@ -72,6 +74,11 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 
 	const n = l * c
 	const est_sparse = (csparse != c)
+	if est_sparse
+		println("Sparse.")
+	else
+		println("Non sparse.")
+	end
 	#if !useBitArray
 	if !est_sparse
 		sparseMessages = zeros(Bool, n, m)
@@ -81,7 +88,7 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 	#else	
 	#	sparseMessages = falses(m,n)
 	#end
-	if activities <= 1  # bad "if" but the goal is to keep different test files functioning
+	if activities <= 1  # bad "if" but the goal is to keep cache efficiency
 		messages = rand(1:l,m,(if !est_sparse c else csparse end))
 		if !est_sparse
 			for i=1:m
@@ -124,12 +131,14 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 		#	end
 		#end
 		#graine = vcat(ones(Bool, activities), zeros(Bool, l - activities))
-		const ind_l = [1:l]
+		#const ind_l = [1:l]
 		for i=1:m
-			for j = (if !est_sparse 1:c else skelet_rand_combination(c, csparse) end)
+			for j = (if !est_sparse 1:c else skelet2_rand_combination(c, csparse) end)
 				#sparseMessages[(j-1)*l+1:j*l, i] = rand_combination(l, activities)#shuffle(graine)
 				#sparseMessages[(j-1)*l + ind_l[rand_combination(l, activities)], i] = 1
-				sparseMessages[(j-1)*l + skelet2_rand_combination(l, activities), i] = 1
+				for k in skelet2_rand_combination(l, activities)
+					sparseMessages[(j-1)*l + k, i] = 1
+				end
 			end
 		end
 		###############" Attention les messages n'ont plus aucun rapport avec les sparseMessages !!!!!!!

### 2014-07-16 astat.r
...

@@ -27,6 +27,7 @@ spec = matrix(c(
 'ord', NA, 2, "character",
 'help' , 'h', 0, "logical",
 'clusters' , 'c', 2, "integer",
+'csparse' , NA, 2, "integer",
 'activities' , 'a', 2, "integer",
 'neurons' , 'l', 2, "integer",
 'messages' , 'm', 2, "integer",
@@ -113,6 +114,13 @@ if(is.null(opt$abs)) { opt$abs = "erasures" ; }
 if(is.null(opt$ord)) { opt$ord = "errorrate" ; }
 
 if(!is.null(opt$clusters)) { data = subset(data, c == opt$clusters) }
+if(!is.null(opt$csparse)) { 
+	if(opt$csparse == 0) {
+		data = subset(data, c == csparse)
+	} else {
+		data = subset(data, csparse == opt$csparse)
+	}
+}
 if(!is.null(opt$messages)) { data = subset(data, m == opt$messages) }
 if(!is.null(opt$neurons)) { data = subset(data, l == opt$neurons) }
 if(!is.null(opt$gamma)) { data = subset(data, gamma == opt$gamma) }

### 2014-07-16 sam.jl
...

@@ -89,18 +89,18 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 	#	sparseMessages = falses(m,n)
 	#end
 	if activities <= 1  # bad "if" but the goal is to keep cache efficiency
-		messages = rand(1:l,m,(if !est_sparse c else csparse end))
+		messages = rand(1:l,(if !est_sparse c else csparse end), m)
 		if !est_sparse
 			for i=1:m
 				for j=1:c
-					sparseMessages[(j-1)*l+messages[i,j], i] = 1
+					sparseMessages[(j-1)*l+messages[j,i], i] = 1
 				end
 			end
 		else
 			for i=1:m
 				k = 1
 				for j= skelet_rand_combination(c, csparse)
-					sparseMessages[(j-1)*l+messages[i,k], i] = 1
+					sparseMessages[(j-1)*l+messages[k,i], i] = 1
 					k += 1
 				end
 			end
@@ -167,7 +167,7 @@ function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree 
 				for j=1:c
 					for k=1:c
 						if j != k
-							network[(j-1)*l+messages[i,j],(k-1)*l+messages[i,k]] = 1
+							network[(j-1)*l+messages[j,i],(k-1)*l+messages[k,i]] = 1
 						end
 					end
 				end

### 2014-07-17 Articles/article.tex
...
....

@@
-\documentclass[english,11pt,twocolumn]{article}
+\documentclass[english,10pt,twocolumn]{IEEEtran}
 \usepackage[utf8]{inputenc}
@@
 %\usepackage[style=numeric,backend=bibtex]{biblatex}
-\pagestyle{myheadings}
+%\pagestyle{myheadings}
 
@@
 \renewcommand{\theenumi}{\roman{enumi})}
-\renewcommand{\thepart}{\Alph{part}}
+%\renewcommand{\thepart}{\Alph{part}}
 %\renewcommand{\thechapter}{\arabic{chapter}}
@@
 \renewcommand{\thetheoreme}{\arabic{section}.\arabic{theoreme}}
-\providecommand{\keywords}[1]{\textbf{Index terms---} #1}
+%\providecommand{\keywords}[1]{\textbf{Index terms---} #1}
 
@@
 
-	\keywords{associative memory, error correcting code, cliques, multipartite cliques, neural networks}
+	%\keywords{associative memory, error correcting code, cliques, multipartite cliques, neural networks}
 
@@
 	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and $m = | \mathcal{M} |$.
-Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or units.
-Messages are considered independent and identically distributed.
+Messages in $\mathcal{M}$ are stored in a neural network, of $c \cdot l$ units.
 
@@
 The parameter $a$ describing the number of activated units per cluster will be called number of activities.
+
+	$\tilde{W} = \max_{1\le i \le m} x_i x_i^\intercal$
+
+	$W_{kl} = \bigg \{
+  \begin{tabular}{ccc}
+  $0$ & if $\exists i\in [1, c ], \, (i-1)c+1 \le k,l \le ic$ \\
+  $\tilde{W}_{kl}$ & otherwise 
+  \end{tabular}
+  $
 
@@
 
-		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all units that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)
+		We make a small modification the classic retrieving rule to fully exploit the local regularity of the code (constant weight of $a$).
+We keep activated all units that achieve a score equal or greater than the $w$-th score.
+(where $w$ is a positive integer parameter)
 
@@
 
-		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $w$-th greater element in an array of $n$ elements is $O(n)$ in complexity.
+		%Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $w$-th greater element in an array of $n$ elements is $O(n)$ in complexity.
 
-		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$).
+		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$ as well).
 		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
@@
 
-	Since units representing messages are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$.
+	Since unit activations are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$.
 
@@
 		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
-		\caption{Theoretical and empirical densities}
+		\caption{Theoretical and empirical densities for a network of 8 clusters, 256 units per cluster and 4 activated units per cluster}
 			\label{densiteth}

### 2014-07-17 sam.jl

@@ -99,7 +99,7 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 		else
 			for i=1:m
 				k = 1
-				for j= skelet_rand_combination(c, csparse)
+				for j = skelet_rand_combination(c, csparse)
 					sparseMessages[(j-1)*l+messages[k,i], i] = 1
 					k += 1
 				end

### 2014-07-17 Articles/article.tex
....

@@
 
+	\begin{IEEEkeywords}
+	associative memory, error correcting code, cliques, multipartite cliques, neural networks
+	\end{IEEEkeywords}
 	\section{Introduction}
@@
 
-	Each message $x = (x_i)_{1 \le i \le c}$ is mapped to $y = (y_i)_{1 \le i \le c}$ where $y_i$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}
+	Each message $x = (x_j)_{1 \le j \le c}$ is mapped to $y = (y_j)_{1 \le j \le c}$ where $y_j$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}
 
@@
 
-	$\tilde{W} = \max_{1\le i \le m} x_i x_i^\intercal$
+	Units $k$ in cluster $j$ will be designated by index $l = (j-1)c+k$.
 
-	$W_{kl} = \bigg \{
+	The state of the network corresponds to a message.
+
+	$\tilde{W} = \max_{1\le i \le m} x^i x^{i\intercal}$
+
+	$W_{ll'} = \bigg \{
   \begin{tabular}{ccc}
-  $0$ & if $\exists i\in [1, c ], \, (i-1)c+1 \le k,l \le ic$ \\
-  $\tilde{W}_{kl}$ & otherwise 
+  $0$ & if $\exists j\in [1, c], \, (j-1)c+1 \le l,l' \le jc$ \\
+  $\tilde{W}_{ll'}$ & otherwise 
   \end{tabular}
@@
 		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
+
+		$x$
+
+		$\tilde{x}$
+
+		$s^{t} = \gamma \tilde{x^{t}} + W \tilde{x^{t}}$
+
 		\begin{algorithm}[!htb]

### 2014-07-17 sam.jl

@@ -25,6 +25,14 @@ function rand_combination(n, m)
 	end
 	res
 end
+function sprand_combination(n, m)
+	s = floyd_combination(n, m)
+	res = spzeros(Bool, n, 1)
+	for i in s
+		res[i] = 1
+	end
+	res
+end
 
 function skelet2_rand_combination(n, m)
 	a = int(collect(floyd_combination(n, m)))
@@ -99,7 +107,7 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 		else
 			for i=1:m
 				k = 1
-				for j = skelet_rand_combination(c, csparse)
+				for j = floyd_combination(c, csparse)
 					sparseMessages[(j-1)*l+messages[k,i], i] = 1
 					k += 1
 				end
@@ -132,12 +140,20 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 		#end
 		#graine = vcat(ones(Bool, activities), zeros(Bool, l - activities))
 		#const ind_l = [1:l]
-		for i=1:m
-			for j = (if !est_sparse 1:c else skelet2_rand_combination(c, csparse) end)
-				#sparseMessages[(j-1)*l+1:j*l, i] = rand_combination(l, activities)#shuffle(graine)
-				#sparseMessages[(j-1)*l + ind_l[rand_combination(l, activities)], i] = 1
-				for k in skelet2_rand_combination(l, activities)
-					sparseMessages[(j-1)*l + k, i] = 1
+		if !est_sparse
+			for i =1:m
+				for j =1:c
+					sparseMessages[(j-1)*l+1:j*l, i] = rand_combination(l, activities)
+				end
+			end
+		else
+			for i=1:m
+				for j in floyd_combination(c, csparse)
+					#sparseMessages[(j-1)*l+1:j*l, i] = sprand_combination(l, activities)
+					#sparseMessages[(j-1)*l + ind_l[rand_combination(l, activities)], i] = 1
+					for k in floyd_combination(l, activities)
+						sparseMessages[(j-1)*l + k, i] = 1
+					end
 				end
 			end
 		end

### 2014-07-17 Articles/article.tex
...

@@
 
-	\subsection{Learning messages}
+	An associative memory is able to retrieve a message through a partial version of it.
 
-	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and $m = | \mathcal{M} |$.
-Messages in $\mathcal{M}$ are stored in a neural network, of $c \cdot l$ units.
+	We first explain how we will store messages. Secondly we detail how messages are retrieved by a multipartite clustered network.
+
+	\subsection{Storing messages}
 
@@
 
-	Each message $x = (x_j)_{1 \le j \le c}$ is mapped to $y = (y_j)_{1 \le j \le c}$ where $y_j$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}
+	We will consider a set $\mathcal{M}$ of messages of fixed length $c$ over a finite alphabet $\mathcal{A}$.
+
+	Messages in $\mathcal{M}$ are stored in a clustered neural network, of $c$ clusters of $l$ units each.
+
+	Let $\mathcal{M}$ be a set of messages of length $c$ over a finite alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and $m = | \mathcal{M} |$.
+
+	binary constant weight codes of weight $a$.
+
+	States of the network are characterized by which neurons are activated. A message corresponds to one, and only one, state of the network. 
+	%Each message $x = (x_j)_{1 \le j \le c}$ is mapped to $y = (y_j)_{1 \le j \le c}$ where $y_j$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}
 
@@
 
-	$\tilde{W} = \max_{1\le i \le m} x^i x^{i\intercal}$
+	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$
 
@@
 
+  We obtain a binary symmetric matrix $W$ with null blocks on the diagonal.
+
+  As taking a maximum is associative and commutative, storing can be done online and is independent of the order of messages.
+
 	\subsection{Retrieving messages}
 
-		Retrieving messages occurs by message passing. We adapt the rule first developed in \cite{GriBer20117} to multipartite cliques.
+		Messages are retrieved by iterative application of a correcting rule. We adapt the rule first developed in \cite{GriBer20117} to multipartite cliques.
 
@@
 
-		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$ as well).
+		Intuitively the choice of $w = a$ is optimal (it it is the most natural one with $w = 1$ as well).
 		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
 
-		$x$
+		We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve. We set $\tilde{x}^0 = \tilde{x}$.
 
-		$\tilde{x}$
+		At each step $t$, we compute the scores $s^{t} = \gamma \tilde{x^{t}} + W \tilde{x^{t}}$
 
-		$s^{t} = \gamma \tilde{x^{t}} + W \tilde{x^{t}}$
+		$\mbox{select}(w, v)$ is equal to the $w$-th greatest element of $v$ (counting repetitions).\footnote{$\mbox{select}(3, [3,2,1,2,0]) = 2$}
+
+		$\tilde{x}^{t+1}_{(j-1)c+k} = \bigg \{
+  			\begin{tabular}{ccc}
+  			$1$ & if $s^t_{(j-1)c+k} \ge  \mbox{select}(w, (s^t_{(j-1)c+k'})_{1\le k' \le l})$ \\
+  			$0$ & otherwise 
+  		\end{tabular}
+  		$
 
@@
 
+	We now study the performance of the new retrieving rule on different problems of retrieving messages : first partially erased messages, then erroneous messages, finally partially erased messages when the network has been damaged.
+
 	\section{Retrieval performance}
+
+	Messages will be considered as independent and identically distributed according to the uniform distribution.
 
@@
 	\subsubsection{Analytical result}
+
+	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(l, l')$ to be present in the network (i.e.
+$W_{ll'} = 1$).
+We then express the theoretical error rate after one iteration of the retrieving rule in function of the density.
+All this computations are done assuming connections between units are independent, which is false but is a convenient approximation that gives results very close from empirical results.
 
@@
 	%edge : $(i, j)$
-	We generalise results on erasures obtained in \cite{GriBer20117} to multipartie cliques.
 
-	Suppose we are trying to recover a message where $c_e$ clusters have been erased (i.e. all units in those clusters are set to $0$).
+	%We generalise results on erasures obtained in \cite{GriBer20117} to multipartie cliques.
+	Erasures of a symbol in a message corresponds to an erased cluster in the network. An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.
 
-	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$.
+	Suppose we are trying to retrieve a message where $c_e$ clusters have been erased. %(i.e. all units in those clusters are set to $0$).
+
+	As the probability for $l$ and $l'$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(l,l')$ of not being added in the network for one message is $1 - \left(a/l\right)^2$.
 Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed as :
@@
 	In order to compare different networks using different alphabets, we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
-A perfect associative memory would use exactly the same number of bits than the original messages and recover messages by maximum likelihood (ambiguities causing errors).
+A perfect associative memory would use exactly the same number of bits than the original messages and retrieve messages by maximum likelihood (ambiguities causing errors).
 Efficiency is the amount of information retrieved divided by the hardness of the problem.

### 2014-07-18 Articles/article.tex
...

@@
 
-	An associative memory is able to retrieve a message through a partial version of it.
+	An associative memory is able to store messages and retrieve them through a partial versions of them.
 
-	We first explain how we will store messages. Secondly we detail how messages are retrieved by a multipartite clustered network.
+	We first describe how messages can be stored in a binary clustered network of multipartite cliques. Secondly we detail how messages can be retrieved after being stored in such a network.
 
@@
 	Messages in $\mathcal{M}$ are stored in a clustered neural network, of $c$ clusters of $l$ units each.
+Units can take two values $0$ (deactivated) and $1$ (activated).
+The network is therefore binary.
+A cluster will correspond to a symbol in a message and the pattern of unit activations in a cluster will determine which symbol in the alphabet the cluster represents.
 
-	Let $\mathcal{M}$ be a set of messages of length $c$ over a finite alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and $m = | \mathcal{M} |$.
+	Previous works (\cite{GriBer20114, GriBer20122}) considered the storage of binary constant weight codewords of weight $1$.
+We study the case of arbitrary weight.
+It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of weight $a$, where $a$ is a positive integer which we will call number of activities.
 
-	binary constant weight codes of weight $a$.
+	%Let $\mathcal{M}$ be a set of messages of length $c$ over a finite alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and 
+	We set $m = | \mathcal{M} |$.
 
-	States of the network are characterized by which neurons are activated. A message corresponds to one, and only one, state of the network. 
+	%binary constant weight codes of weight $a$.
+
+	States of the network are characterized by which neurons are activated.
+A message corresponds to one, and only one, state of the network.
+A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation.
+$x$ is separated in $c$ clusters of $l$ units.} We say the network is in state $x$ if for all $j\in [1, c]$, cluster $j$ in the network follows the activation pattern $x[(j-1)l+1\hdots jl]$.
+
 	%Each message $x = (x_j)_{1 \le j \le c}$ is mapped to $y = (y_j)_{1 \le j \le c}$ where $y_j$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}
 
-	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $i$ and $j$ such as $1 \le j \le l$ and $1 \le i \le c$, the unit $j$ in the cluster $i$ is activated if and only if $y_i[j] = 1$ ; then adding all connections between activated units excepting for units sharing the same cluster.
-Thus we obtain a multipartite clique between activated units representing a message.
-The parameter $a$ describing the number of activated units per cluster will be called number of activities.
+	Storing a message $y$ in the network amounts to consider the network in state $x$, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$ ; then adding all connections between activated units excepting for units sharing the same cluster.
+Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.
 
-	Units $k$ in cluster $j$ will be designated by index $l = (j-1)c+k$.
+	Unit $k$ in cluster $j$ thus corresponds to the index $l = (j-1)c+k$.
 
-	The state of the network corresponds to a message.
+	%The state of the network corresponds to a message.
 
-	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$
+	We can describe the network which is an undirected unweighted graph, by its adjacency matrix $W$.
+As for a message $x$, $x x^{\intercal}$ is the matrix describing the graph where all edges between active units exist, and only them, we can express $W$ in function of the following :
+
+	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where even edges between units in the same cluster have been added.
+	$W$ can now be expressed as :
 
@@
 
-	We now study the performance of the new retrieving rule on different problems of retrieving messages : first partially erased messages, then erroneous messages, finally partially erased messages when the network has been damaged.
+	We now study the performance of the new retrieving rule on distinct problems of retrieving messages : first partially erased messages, then erroneous messages, finally partially erased messages when the network has been damaged.
 
@@
 
-		Simulations agree with the analytical results for error rate, see Figure \ref{erasuresth}.
+		Simulations agree with the analytical results for error rate, see Figure \ref{erasuresth}. We observe a small shift.
 

### 2014-07-18 Articles/article.tex
...

@@
 We study the case of arbitrary weight.
-It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of weight $a$, where $a$ is a positive integer which we will call number of activities.
+It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of weight $a$, where $a$ is a positive integer parameter which we will call number of activities.
+We set $m = | \mathcal{M} |$.
 
 	%Let $\mathcal{M}$ be a set of messages of length $c$ over a finite alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and
-	We set $m = | \mathcal{M} |$.
 
@@
 
-	States of the network are characterized by which neurons are activated.
+	States of the network are characterized by which units are activated.
 A message corresponds to one, and only one, state of the network.
 A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation.
-$x$ is separated in $c$ clusters of $l$ units.} We say the network is in state $x$ if for all $j\in [1, c]$, cluster $j$ in the network follows the activation pattern $x[(j-1)l+1\hdots jl]$.
+$x$ is separated in $c$ clusters of $l$ units.} To sum up thje $k$-th unit in the $j$-th cluster corresponds to the index $l = (j-1)l+k$.
+We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+l] = 1$.
 
@@
 
-	Storing a message $y$ in the network amounts to consider the network in state $x$, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$ ; then adding all connections between activated units excepting for units sharing the same cluster.
+	Storing a message $y$ in the network amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$
+	; then adding all connections between activated units excepting for units sharing the same cluster.
 Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.
-
-	Unit $k$ in cluster $j$ thus corresponds to the index $l = (j-1)c+k$.
 
@@
 	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where even edges between units in the same cluster have been added.
-	$W$ can now be expressed as :
+	$W$ can now be expressed as :\vspace*{1mm}
 
@@
   $
+  \vspace*{1mm}
 
@@
 
-  As taking a maximum is associative and commutative, storing can be done online and is independent of the order of messages.
+  As taking a maximum is associative and commutative, storing can be done online and is independent of the order in which messages are stored.
 

### 2014-07-18 Articles/article.tex
...

@@
 
+	A binary constant weight code of weight $a$ is a code where all codewords have the same weight $a$, i.e.
+the same number of $1$ in them.
 Previous works (\cite{GriBer20114, GriBer20122}) considered the storage of binary constant weight codewords of weight $1$.
 We study the case of arbitrary weight.
-It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of weight $a$, where $a$ is a positive integer parameter which we will call number of activities.
+It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of length $l$ and of weight $a$, where $a$ is a positive integer parameter which we will call number of activities and which satisfies $a\le l$.
+We now have ${l \choose a} = |\mathcal{A}|$.
 We set $m = | \mathcal{M} |$.
@@
 A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation.
-$x$ is separated in $c$ clusters of $l$ units.} To sum up thje $k$-th unit in the $j$-th cluster corresponds to the index $l = (j-1)l+k$.
+$x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $l = (j-1)l+k$.
 We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+l] = 1$.
@@
 	Storing a message $y$ in the network amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$
-	; then adding all connections between activated units excepting for units sharing the same cluster.
+	; then adding all edges between activated units to the network excepting for units sharing the same cluster.
+Note that edges already present in the network remain unchanged.
 Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.
@@
 	We can describe the network which is an undirected unweighted graph, by its adjacency matrix $W$.
-As for a message $x$, $x x^{\intercal}$ is the matrix describing the graph where all edges between active units exist, and only them, we can express $W$ in function of the following :
+For a message $x$, $x x^{\intercal}$ is the matrix describing the graph where all edges between active units exist, and only them.
+Therefore we can express $W$ in function of the following :
 
-	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where even edges between units in the same cluster have been added.
+	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between units activated for each state $x$ in the same cluster have been added.
 	$W$ can now be expressed as :\vspace*{1mm}
@@
 		Intuitively the choice of $w = a$ is optimal (it it is the most natural one with $w = 1$ as well).
-		Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
+		%Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
 
@@
 
-		At each step $t$, we compute the scores $s^{t} = \gamma \tilde{x^{t}} + W \tilde{x^{t}}$
+		At each step $t$, we compute the scores, that is to mean the number of active units each unit is connected to, plus a memory effect $\gamma $ accounting for units begin already active.
+The array of scores at step $t$ is :  $s_{t} = \gamma \tilde{x_{t}} + W \tilde{x_{t}}$
 
-		$\mbox{select}(w, v)$ is equal to the $w$-th greatest element of $v$ (counting repetitions).\footnote{$\mbox{select}(3, [3,2,1,2,0]) = 2$}
+		To detail the final step of the retrieving rule, we introduce a function $\mbox{select}$ such as for an array $v$, $\mbox{select}(w, v)$ is equal to the $w$-th greatest element of $v$ (counting repetitions).\footnote{$\mbox{select}(3, [3,2,1,2,0]) = 2$}
 
-		$\tilde{x}^{t+1}_{(j-1)c+k} = \bigg \{
-  			\begin{tabular}{ccc}
-  			$1$ & if $s^t_{(j-1)c+k} \ge  \mbox{select}(w, (s^t_{(j-1)c+k'})_{1\le k' \le l})$ \\
+		\begin{align*}
+		%$
+		&\tilde{x}_{t+1}[(j-1)c+k] =\\ \bigg \{
+  			&\begin{tabular}{ccc}
+  			$1$ & if $s_t[(j-1)c+k] \ge  \mbox{select}(w, s_t[(j-1)l+1 \hdots jl)$ \\
   			$0$ & otherwise 
   		\end{tabular}
-  		$
+  		%$
+  		\end{align*}
 
-		\begin{algorithm}[!htb]
-		\caption{$w$-sum of sum \label{asumsum}}
-		\begin{algorithmic}[1]
-		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
-		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
-		%\Statex
-		\For{$s$ from $1$ to $S$}
-		\State $s \gets \gamma v + W v$
-		\For{$i$ from $1$ to $c$}
-			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
-			\For{$j$ from $1$ to $l$}
-			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
-			\EndFor
-		\EndFor
-		\EndFor
-		%\State\Return v
-		\EndProcedure
-		\end{algorithmic}
-		\end{algorithm}
+		We can for example fix a maximum number of steps to the algorithm or even stop at one point if $\tilde{x}_{t+1} = \tilde{x}_t$. The number of iterations can of course improve the retrieval rate.
 
-	We now study the performance of the new retrieving rule on distinct problems of retrieving messages : first partially erased messages, then erroneous messages, finally partially erased messages when the network has been damaged.
+%		\begin{algorithm}[!htb]
+%		\caption{$w$-sum of sum \label{asumsum}}
+%		\begin{algorithmic}[1]
+%		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network, $S$ the number of iterations, $\gamma$ memory effect}
+%		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
+%		%\Statex
+%		\For{$s$ from $1$ to $S$}
+%		\State $s \gets \gamma v + W v$
+%		\For{$i$ from $1$ to $c$}
+%			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
+%			\For{$j$ from $1$ to $l$}
+%			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
+%			\EndFor
+%		\EndFor
+%		\EndFor
+%		%\State\Return v
+%		\EndProcedure
+%		\end{algorithmic}
+%		\end{algorithm}
+
+	We now study the performance of the new retrieving rule on distinct problems of retrieval : first partially erased messages, then erroneous messages.%, finally partially erased messages when the network has been damaged.
 
@@
 	Messages will be considered as independent and identically distributed according to the uniform distribution.
+We compute theoretical error rates after one iteration of the retrieving rule.
+We compare those results to empirical error rates obtained through simulations.
+We also compare efficiencies of distinct networks for distinct values of the parameter $a$ (weight of the constant weight code) in the sense of information theory and show improvements over the case where $a = 1$.
 
@@
 	%We generalise results on erasures obtained in \cite{GriBer20117} to multipartie cliques.
+
 	Erasures of a symbol in a message corresponds to an erased cluster in the network. An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.

### 2014-07-18 Articles/article.tex
...

@@
 
-	We first describe how messages can be stored in a binary clustered network of multipartite cliques. Secondly we detail how messages can be retrieved after being stored in such a network.
+	We first describe how messages can be stored in a binary clustered network of multipartite cliques.
+Secondly we detail how messages can be retrieved after being stored in such a network, thereby showing how such a network can be used as an associative memory.
 
@@
 
-		We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve. We set $\tilde{x}^0 = \tilde{x}$.
+		We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve.
+We set $\tilde{x}^0 = \tilde{x}$.
+The network is in state $\tilde{x}$ at the beginning of the retrieving.
+The message will be successfully retrieved if at the end of the algorithm, the network is in state $x$.
 
@@
 
+	One can see a partial version of a message $x$ as the result of erasures of symbols of $x$.
+Some symbols of $x$ are replaced by the blank character $\intercal$.	Erasures of a symbol in a message corresponds to an "erased" cluster in the network.
+An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.
+
 	\subsubsection{Analytical result}
@@
 We then express the theoretical error rate after one iteration of the retrieving rule in function of the density.
-All this computations are done assuming connections between units are independent, which is false but is a convenient approximation that gives results very close from empirical results.
+All this computations (on error rates) are done assuming connections between units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.
 
@@
 	%We generalise results on erasures obtained in \cite{GriBer20117} to multipartie cliques.
-
-	Erasures of a symbol in a message corresponds to an erased cluster in the network. An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.
 

### 2014-07-18 Articles/article.tex
...

@@
 
-	Messages in $\mathcal{M}$ are stored in a clustered neural network, of $c$ clusters of $l$ units each.
-Units can take two values $0$ (deactivated) and $1$ (activated).
+	Messages of $\mathcal{M}$ are stored in a clustered neural network, of $c$ clusters of $l$ units each.
+Each unit can take two values $0$ (deactivated) and $1$ (activated).
 The network is therefore binary.
@@
 We now have ${l \choose a} = |\mathcal{A}|$.
-We set $m = | \mathcal{M} |$.
+We also set $m = | \mathcal{M} |$.
 
@@
 
-	Suppose we are trying to retrieve a message where $c_e$ clusters have been erased. %(i.e. all units in those clusters are set to $0$).
-
 	As the probability for $l$ and $l'$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(l,l')$ of not being added in the network for one message is $1 - \left(a/l\right)^2$.
@@
 	\end{align}		
+	, recalling that $m$ is the number of messages in $\mathcal{M}$.
 
-	Thanks to the memory effect $\gamma$, activated units in a non-erased cluster stay activated and are the only ones doing so in their cluster.
+	Suppose we are trying to retrieve a message where $c_e$ clusters have been erased. %(i.e. all units in those clusters are set to $0$).
+	Thanks to the memory effect $\gamma$, activated units in a non-erased cluster stay activated and are the only ones doing so in their cluster (as the others can't achieve a higher score thanks to not being already activated).
 For units in erased clusters, the maximum attainable score is $a(c - c_e)$.
 Units corresponding to the original message achieve this score.
-Besides the probability for a unit $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.
+Since scores follow a binomial law, the probability for a unit $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.
 
@@
 
-	In order to compare different networks using different alphabets, we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
+	In order to compare distinct networks using distinct alphabets (due to variations of the weight parameter $a$), we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
 A perfect associative memory would use exactly the same number of bits than the original messages and retrieve messages by maximum likelihood (ambiguities causing errors).

### 2014-07-18 Articles/article.tex
...

@@
 
-		We can for example fix a maximum number of steps to the algorithm or even stop at one point if $\tilde{x}_{t+1} = \tilde{x}_t$. The number of iterations can of course improve the retrieval rate.
+		We can for example fix a maximum number of steps to the algorithm or stop at one point if $\tilde{x}_{t+1} = \tilde{x}_t$.
+Increasing the number of iterations can of course improve the retrieval rate.
 
@@
 We then express the theoretical error rate after one iteration of the retrieving rule in function of the density.
-All this computations (on error rates) are done assuming connections between units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.
+All this computations (on error rates) are done assuming existences of edges between random units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.
 
@@
 	Suppose we are trying to retrieve a message where $c_e$ clusters have been erased. %(i.e. all units in those clusters are set to $0$).
-	Thanks to the memory effect $\gamma$, activated units in a non-erased cluster stay activated and are the only ones doing so in their cluster (as the others can't achieve a higher score thanks to not being already activated).
+	Thanks to the memory effect $\gamma$, activated units in a non-erased cluster stay activated and are the only ones being so in their cluster (as the others can't achieve a higher score thanks to not being already activated).
 For units in erased clusters, the maximum attainable score is $a(c - c_e)$.
-Units corresponding to the original message achieve this score.
-Since scores follow a binomial law, the probability for a unit $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.
+Units in erased clusters corresponding to the original message achieve this score.
+Since scores follow a binomial law, the probability for a random unit to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.
 
@@
 
-	As information on a message is shared across connections with multiple activated units per cluster, such networks are more resilient to damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
+	As information on a message is shared across edges with multiple activated units per cluster, such networks are more resilient to damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
 $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.

### 2014-07-18 Articles/article.tex
correction indice

@@
 A message corresponds to one, and only one, state of the network.
-A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation.
-$x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $l = (j-1)l+k$.
-We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+l] = 1$.
+A message $y$ of length $c$ can be seen as an array $x$ of length $c\cdot{} l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation.
+$x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $i = (j-1)l+k$.
+We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+k] = 1$.
+Taking into account this correspondence between messages $y$ in $\mathcal{M}$ and their clustered representation $x$, we will now also consider $x$ as messages.
 
@@
 	; then adding all edges between activated units to the network excepting for units sharing the same cluster.
-Note that edges already present in the network remain unchanged.
+Notice that edges already present in the network remain unchanged throughout the storing process.
 Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.
@@
 
-	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between units activated for each state $x$ in the same cluster have been added.
+	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between  activated units for each state $x$ in the same cluster have been added.
 	$W$ can now be expressed as :\vspace*{1mm}
 
-	$W_{ll'} = \bigg \{
+	$W_{ii'} = \bigg \{
   \begin{tabular}{ccc}
-  $0$ & if $\exists j\in [1, c], \, (j-1)c+1 \le l,l' \le jc$ \\
-  $\tilde{W}_{ll'}$ & otherwise 
+  $0$ & if $\exists j\in [1, c], \, (j-1)l+1 \le i,i' \le jl$ \\
+  $\tilde{W}_{ii'}$ & otherwise 
   \end{tabular}

### 2014-07-18 Articles/article.tex
...

@@
 
-	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between  activated units for each state $x$ in the same cluster have been added.
+	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal} = \bigvee_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between  activated units for each state $x$ in the same cluster have been added.
 	$W$ can now be expressed as :\vspace*{1mm}
@@
 
-  As taking a maximum is associative and commutative, storing can be done online and is independent of the order in which messages are stored.
+  As logical or ($\vee$) is associative and commutative, storing can be done online and is independent of the order in which messages are stored.
 
@@
 The network is in state $\tilde{x}$ at the beginning of the retrieving.
+The state of the network at the beginning of the step $t$ will be denoted by $\tilde{x}_t$.
 The message will be successfully retrieved if at the end of the algorithm, the network is in state $x$.
@@
 
-	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(l, l')$ to be present in the network (i.e.
-$W_{ll'} = 1$).
+	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(i, i')$ to be present in the network (i.e.
+$W_{ii'} = 1$).
 We then express the theoretical error rate after one iteration of the retrieving rule in function of the density.
@@
 
-	As the probability for $l$ and $l'$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are identically distributed, it follows that the probability for the edge $(l,l')$ of not being added in the network for one message is $1 - \left(a/l\right)^2$.
+	As the probability for $i$ (and $i'$) to be active in its cluster for one message $x$ is $\frac{a}{l}$ providing messages are uniformly distributed, it follows that the probability for the edge $(i,i')$ of not being added in the network for $x$ is $1 - \left(a/l\right)^2$.
 Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed as :

### 2014-07-18 Articles/article.tex
...

@@
 $x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $i = (j-1)l+k$.
-We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+k] = 1$.
+We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, unit $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+k] = 1$.
 Taking into account this correspondence between messages $y$ in $\mathcal{M}$ and their clustered representation $x$, we will now also consider $x$ as messages.
@@
 We keep activated all units that achieve a score equal or greater than the $w$-th score.
-(where $w$ is a positive integer parameter)
+(where $w$ is a positive integer parameter).
+$w = 1$ amounts to taking the maximum and so is exactly the same as the classic retrieving rule.
 
@@
 
-		Intuitively the choice of $w = a$ is optimal (it it is the most natural one with $w = 1$ as well).
+		Intuitively the choice of $w = a$ is optimal, as each cluster should eventually contain exactly $a$ active units to at least represent a symbol in $\mathcal{A}$.
+%(it it is the most natural one with $w = 1$ as well).
 		%Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
@@
 	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits.
-Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula).
-The information effectively stored in the network is $P_{retrieve} \times  \frac{2m \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.
+Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula).
+The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2m \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.
 
@@
 
-	The maximum information that can be stored in the network is therefore $\eta = \max_x \eta_x $, which we will define as the efficiency of the network.
+	The maximum ratio of information that can be stored in the network is therefore $\eta = \max_x \eta_x $, which we will define as the efficiency of the network.
 
 	\subsubsection{Simulations}
+
 		Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent,
 
-		Simulations agree with the analytical results for error rate, see Figure \ref{erasuresth}. We observe a small shift.
+		Simulations agree with the analytical results for error rate, albeit we can observe a small shift, see Figure \ref{erasuresth}.
+For one iteration, as long as the parameter $w$ is between $1$ and $a$, there is no effect on retrieving.
+However for $4$ iterations, the choice of $w = a$ allows a shift of about $5000$ messages stored on top of those stored for $w = 1$.
+The variant rule can thus be considered a significant improvement over the classic one for multipartite clique networks (recall that $w = 1$ amounts to the classic retrieving rule).
 
-	For one iteration (for erasures, not for errors), "winner takes all" is the same as "$a$-winners take all".
+	%For one iteration (for erasures, not for errors), "winner takes all" is the same as "$a$-winners take all".
 
-	For multiple iterations $a$-winners take all is a significant improvement.
+	%For multiple iterations $a$-winners take all is a significant improvement.
 	%The variant of the rule significantly improves the retrieval rate over multiple iterations. (For one iteration, is is the same as taking only maximum scores.)
@@
 
-		Figure \ref{comperth} shows improvements in capacities over unipartite cliques network. The more the problem is difficult, the more redundancies introduced by multipartite cliques are useful.
+		Thanks to the efficiency defined in the previous section, we can easily compare distinct choices of parameters $a$ (we now take $w = a$ since it is the most efficient choice in practice) over distinct number of erased clusters.
+Figure \ref{comperth} shows improvements in efficiencies over parameter $a =1$.
+The more difficult the problem is, the more redundancies introduced by multipartite cliques are useful.
 

### 2014-07-18 Articles/article.tex
...

@@
 		%$
-		&\tilde{x}_{t+1}[(j-1)c+k] =\\ \bigg \{
+		&\tilde{x}_{t+1}[(j-1)l+k] =\\ \bigg \{
   			&\begin{tabular}{ccc}
-  			$1$ & if $s_t[(j-1)c+k] \ge  \mbox{select}(w, s_t[(j-1)l+1 \hdots jl)$ \\
+  			$1$ & if $s_t[(j-1)l+k] \ge  \mbox{select}(w, s_t[(j-1)l+1 \hdots jl)$ \\
   			$0$ & otherwise 
@@
 We compute theoretical error rates after one iteration of the retrieving rule.
-We compare those results to empirical error rates obtained through simulations.
+We compare those results to empirical error rates obtained through simulations\footnote{Simulations are done by taking means on pool of five networks and messages sets, and each point is drawn for a different network and messages set.}.
 We also compare efficiencies of distinct networks for distinct values of the parameter $a$ (weight of the constant weight code) in the sense of information theory and show improvements over the case where $a = 1$.
@@
 		Simulations agree with the analytical results for error rate, albeit we can observe a small shift, see Figure \ref{erasuresth}.
+The theoretical error rate is a bit optimistic which is due to the connections not being independent.
+
 		 For one iteration, as long as the parameter $w$ is between $1$ and $a$, there is no effect on retrieving.
@@
 %	\newpage
+
+	Messages can suffer many types of alteration. Multipartite clique neural networks can also correct errors.
 

### 2014-07-18 Articles/article.tex
...

@@
 \usepackage{algpseudocode}
-
+\usepackage{tikz}
 \usepackage[autolanguage]{numprint}
@@
 
-	An associative memory is able to store messages and retrieve them through a partial versions of them.
+	An associative memory is able to store messages then retrieve them given a partial or corrupt probe.
 
-	We first describe how messages can be stored in a binary clustered network of multipartite cliques.
-Secondly we detail how messages can be retrieved after being stored in such a network, thereby showing how such a network can be used as an associative memory.
+	We first describe how messages can be stored in a recently introduced neural network based associative memory~\cite{}. Secondly, we detail how messages can be retrieved by these networks.
 
@@
 
-	Our goal is to store messages so as to be able to retrieve them from partial or erroneous versions of them.
+	Consider a set $\mathcal{M}$ of messages of fixed length $c$ over a finite alphabet $\mathcal{A}$.
 
-	We will consider a set $\mathcal{M}$ of messages of fixed length $c$ over a finite alphabet $\mathcal{A}$.
+	Messages in $\mathcal{M}$ can be stored in a clustered neural network made of $c$ clusters containing $\ell$ units each.
+Units can take binary values : $0$ (deactivated) or $1$ (activated).
+A message is represented by a set of activated units in the network.
+%% There is a natural transport between messages and active units in the network.
+This transport consists in A cluster correspond to a symbol in a message and the pattern of unit activations in a cluster will determine which symbol in the alphabet the cluster represents.
 
-	Messages of $\mathcal{M}$ are stored in a clustered neural network, of $c$ clusters of $l$ units each.
-Each unit can take two values $0$ (deactivated) and $1$ (activated).
-The network is therefore binary.
-A cluster will correspond to a symbol in a message and the pattern of unit activations in a cluster will determine which symbol in the alphabet the cluster represents.
+        One can choose the association between a message and its corresponding set of active units.
+In previous works~\cite{GriBer20114, GriBer20122}, each coordinate of a message $m$ is associated with a cluster.
+Inside a cluster, each unit is associated with a symbol in $\mathcal{A}$.
+As a consequence, to a message $m$ corresponds one active unit in each cluster of the network.
 
-	A binary constant weight code of weight $a$ is a code where all codewords have the same weight $a$, i.e.
-the same number of $1$ in them.
-Previous works (\cite{GriBer20114, GriBer20122}) considered the storage of binary constant weight codewords of weight $1$.
-We study the case of arbitrary weight.
-It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of length $l$ and of weight $a$, where $a$ is a positive integer parameter which we will call number of activities and which satisfies $a\le l$.
-We now have ${l \choose a} = |\mathcal{A}|$.
-We also set $m = | \mathcal{M} |$.
+        In this document, we are interested in assessing the performance of such systems when several units are associated with a given symbol for each cluster.
+To simplify this generalisation and allow for optimized retrieval strategies, we fix this number of activated units $a$ in each cluster.
+
+        Note that there are $\binom{\ell}{a}$ possible choices for $a$ activations among $\ell$ units, giving the following correspondance:
+\[
+\binom{\ell}{a} = | \mathcal{A} |\;.
+\]
+Without loss of generality, we therefore consider that $\mathcal{A}$ is composed of the list of all binary vectors containing exactly $a$ ones that we index from 1 to $\binom{\ell}{a}$: $\mathcal{A} = \{\mathcal{A}_1,\dots,\mathcal{A}_{\binom{\ell}{a}}\}$.
+
+Previous works~\cite{GriBer20114,GriBer20122} consider the case $a=1$.
 
@@
 
-	States of the network are characterized by which units are activated.
-A message corresponds to one, and only one, state of the network.
-A message $y$ of length $c$ can be seen as an array $x$ of length $c\cdot{} l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation.
+	To provide convenient notations, we propose to linearise messages using the following function mapping $f$:
+\[
+f: \left\{\begin{array}{rcl}\mathcal{A}^c &\rightarrow& \{0,1\}^{c\cdot{} \ell}\\m&\mapsto& \mu \big| \forall j, \mu[(j-1)\ell+1\dots j\times\ell] = m_j\end{array}\right.\;,
+\]
+where $\mu[a..b]$ is the subarray of $\mu$ from coordinate $a$ to coordinate $b$.
+
+By abusing notations, and since function $f$ is injective, we shall make no distinction between $m$ and $f(m)=\mu$.
+%% A message $m$ of length $c$ can be seen as an array $x$ of length $c\cdot{} l$ where for each $j\in [c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation.
 $x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $i = (j-1)l+k$.
@@
 
-	Storing a message $y$ in the network amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$
-	; then adding all edges between activated units to the network excepting for units sharing the same cluster.
+	To store a message $m$ in the network, we use the edges between units.
+More precisely, to store a message $\mu$ all edges between activated units are added to the network, with the exception of units in a same cluster.
+In other words, storing a message consists in printing a multipartite clique into the network.
+This process is depicted in Figure~\ref{fig:storage}.
+%% amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$
+	%% ; then adding all edges between activated units to the network excepting for units sharing the same cluster. 
         Notice that edges already present in the network remain unchanged throughout the storing process.
-Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.
+%% Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.
+
+\begin{figure}[!h]
+\centering
+\begin{tikzpicture}
+  \foreach \type/\fill/\xshift/\yshift in {circle/draw/-50pt/50pt,rectangle/draw/50pt/50pt,rectangle/fill/-50pt/-50pt,circle/fill/50pt/-50pt}{
+    \begin{scope}[xshift=\xshift,yshift=\yshift]
+    \tikzstyle{every node}=[\type,draw,\fill];
+    \foreach \i in {0,20pt,40pt,60pt}{
+      \foreach \j in {0,20pt,40pt,60pt}{
+        \node (node\type\fill\i\j) at (\i,\j) {};
+      }
+    }
+\end{scope}
+  }
+  %% \path
+  %% (nodecircledraw20pt40pt) edge (nodecirclefill040pt)
+  %% edge (noderectanglefill20pt20pt)
+  %% edge (noderectangledraw60pt60pt)
+  %% (nodecirclefill040pt) edge (noderectanglefill20pt20pt)
+  %% edge (noderectangledraw60pt60pt)
+  %% (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
+  %% ;
+  %% \path
+  %% (nodecircledraw60pt60pt) edge (nodecirclefill40pt20pt)
+  %% edge (noderectanglefill060pt)
+  %% edge (noderectangledraw20pt40pt)
+  %% (nodecirclefill40pt20pt) edge (noderectanglefill060pt)
+  %% edge (noderectangledraw20pt40pt)
+  %% (noderectanglefill060pt) edge (noderectangledraw20pt40pt)
+  %% ;
+  \path[ultra thick]
+  (nodecircledraw020pt) edge (nodecirclefill20pt20pt)
+  edge (noderectanglefill40pt60pt)
+  edge (noderectangledraw60pt60pt)
+  (nodecirclefill20pt20pt) edge (noderectanglefill40pt60pt)
+  edge (noderectangledraw60pt60pt)
+  (noderectanglefill40pt60pt) edge (noderectangledraw60pt60pt)
+  ;
+\end{tikzpicture}
+\caption{Illustration of the storage process of a message $\mu$. In this setting the number of clusters is $c=4$, each containing $\ell=16$ units. The parameter $a$ is 2.}
+\label{fig:storage}
+\end{figure}
+
+	Note that this representation is lossy, as the number of possible sets of messages is much larger than the number of possible networks.
 
@@
 
-	We can describe the network which is an undirected unweighted graph, by its adjacency matrix $W$.
-For a message $x$, $x x^{\intercal}$ is the matrix describing the graph where all edges between active units exist, and only them.
-Therefore we can express $W$ in function of the following :
+	Formally, we can describe the network using the adjacency matrix $W$ of the underlying graph.
+By construction this matrix is symmetric and binary.
+For a message $\mu$, note that $\mu \mu^{\intercal}$ is the cooccurence matrix associated with $\mu$.
+Before defining $W$, we first introduce the following matrix:
+\[
+	\overline{W} = \max_{\mu\in \mathcal{M}} \mu \mu^{\intercal} %% = \bigvee_{x\in \mathcal{M}} x x^{\intercal}
+        \;,
+\]
+where $\max$ is a coefficient-to-coefficient max function.
+$W$ is obtained from $\overline{W}$ by removing all edges connecting units in a same cluster.
+We obtain a binary symmetric matrix $W$ with null blocks on the diagonal.
+The reason why we remove intracluster connections will be discussed in the following section.
 
-	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal} = \bigvee_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between  activated units for each state $x$ in the same cluster have been added.
-	$W$ can now be expressed as :\vspace*{1mm}
+%% $ which is the matrix where all edges between  activated units for each state $x$ in the same cluster have been added.
+%% 	$W$ can now be expressed as :\vspace*{1mm}
+%% \[
 
-	$W_{ii'} = \bigg \{
-  \begin{tabular}{ccc}
-  $0$ & if $\exists j\in [1, c], \, (j-1)l+1 \le i,i' \le jl$ \\
-  $\tilde{W}_{ii'}$ & otherwise 
-  \end{tabular}
-  $
-  \vspace*{1mm}
+%% \]
 
-  We obtain a binary symmetric matrix $W$ with null blocks on the diagonal.
+%% 	$W_{ii'} = \bigg \{
+%%   \begin{tabular}{ccc}
+%%   $0$ & if $\exists j\in [1, c], \, (j-1)l+1 \le i,i' \le jl$ \\
+%%   $\tilde{W}_{ii'}$ & otherwise 
+%%   \end{tabular}
+%%   $
+%%   \vspace*{1mm}
 
-  As logical or ($\vee$) is associative and commutative, storing can be done online and is independent of the order in which messages are stored.
+  As $\max$ is associative and commutative, storing can be done online and is independent of the order in which messages are stored.
 
@@
 
-		Messages are retrieved by iterative application of a correcting rule. We adapt the rule first developed in \cite{GriBer20117} to multipartite cliques.
+        Once a set of messages has been stored in some matrix $W$, we are interested in retrieving a stored message given a partial or corrupt probe $\tilde{\mu}$.
+To perform this operation, we use an iterative algorithm derived from the one proposed in~\cite{GriBer20117}.
 
@@
 
-		We make a small modification the classic retrieving rule to fully exploit the local regularity of the code (constant weight of $a$).
-We keep activated all units that achieve a score equal or greater than the $w$-th score.
+        The algorithm relies on two steps.
+First it computes \emph{scores} for each unit in the network and then select which units should be activated based on their scores.
+For a review on different strategies for both steps in the classical case where $a=1$, consider~\cite{Ala}.
+To adapt this algorithm in the case $a\ge 2$, we only modify the second step for choosing which units to be activated.
+
+        There are several strategies for computing scores of the units, but our simulations suggest that their impact on performance is not significative.
+We therefore use what is called the SUM-OF-SUM rule in which scores are computed as follows:
+
+\[
+s = \gamma \tilde{\mu} + W \tilde{\mu}\;.
+\]
+
+In other words, the score of a unit is the number of activated units it is connected to, plus a memory effect with parameter $\gamma$.
+This memory effect can have significative impact on performance and its optimal value depends on the problem considered.
+This is the main reason why intracluster edges are forbidden.
+
+        Once scores are computed, we are interested in choosing which units to be activated.
+In order to account for the fact several units should be activated in each cluster, we propose to activate the $\alpha$ units achieving the maximum score in each cluster.
+Note that in case of equality of scores, we select all tied units resulting in possibly more than $\alpha$ units activated in each cluster.
+Intuitively, the best possible choice for $\alpha$ is $a$, but it implies to have some prior knowledge about the value of $a$.
+If one does not know the value of $a$, choosing $\alpha=1$ should lead to reasonable performance.
+
+		%% In order to account for the changes to the model, we make a small modification of the classic retrieving rule.
+Indeed, we keep activated all units that achieve a score equal or greater than the $w$-th score.
 (where $w$ is a positive integer parameter).
@@
 
-		Intuitively the choice of $w = a$ is optimal, as each cluster should eventually contain exactly $a$ active units to at least represent a symbol in $\mathcal{A}$.
+		%% Intuitively the choice of $w = a$ is optimal, as each cluster should eventually contain exactly $a$ active units to at least represent a symbol in $\mathcal{A}$.
 %(it it is the most natural one with $w = 1$ as well).
-		%Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
+		%% %Algorithm \ref{asumsum} is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
 
-		We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve.
+	Formally, we introduce a function $\mbox{select}$ such as for an array $\tilde{\mu}$, $\mbox{select}(\alpha, \tilde{\mu})$ is equal to the $\alpha$-th greatest element of $\mu$ (counting repetitions): as an example $\mbox{select}(3, [4,2,1,2,0,2]) = 2$.
+Then the selection of activated units is performed as follows:
+
+		\begin{align*}
+		&\tilde{\mu}'[(j-1)l+k] =\\ \bigg \{
+  			&\begin{tabular}{cl}
+  			$1$ & if $s[(j-1)l+k] \ge  \mbox{select}(\alpha, s[(j-1)\ell+1 \hdots j\ell])$ \\
+  			$0$ & otherwise 
+  		         \end{tabular}\;.
+  		\end{align*}
+                Thus we use an Heavyside function with a parameter depending on each cluster.
+$\tilde{\mu}'$ is the output of the algorithm after one iteration.
+The process can be repeated providing $\tilde{\mu}'$ as the new input to the network.
+Several stopping criterion can be used~\cite{Ala}.
+In the remaining of this work, we will consider the number of iterations to be fixed.
+Simulations show that increasing the number of iterations can result in significatively better performance.
+
+The network is considered to succeed if the final output of the algorithm matches the original message of which $\tilde{\mu}$ is a partial or corrupted version of.
+
+		%% We can for example fix a maximum number of steps to the algorithm or stop at one point if $\tilde{x}_{t+1} = \tilde{x}_t$.
+Increasing the number of iterations can of course improve the retrieval rate.
+
+		%% We consider an altered version $\tilde{x}$ of a message $x$ which we are trying to retrieve.
 We set $\tilde{x}^0 = \tilde{x}$.
@@
 
-		At each step $t$, we compute the scores, that is to mean the number of active units each unit is connected to, plus a memory effect $\gamma $ accounting for units begin already active.
+		%% At each step $t$, we compute the scores, that is to mean the number of active units each unit is connected to, plus a memory effect $\gamma $ accounting for units begin already active.
 The array of scores at step $t$ is :  $s_{t} = \gamma \tilde{x_{t}} + W \tilde{x_{t}}$
-
-		To detail the final step of the retrieving rule, we introduce a function $\mbox{select}$ such as for an array $v$, $\mbox{select}(w, v)$ is equal to the $w$-th greatest element of $v$ (counting repetitions).\footnote{$\mbox{select}(3, [3,2,1,2,0]) = 2$}
-
-		\begin{align*}
-		%$
-		&\tilde{x}_{t+1}[(j-1)l+k] =\\ \bigg \{
-  			&\begin{tabular}{ccc}
-  			$1$ & if $s_t[(j-1)l+k] \ge  \mbox{select}(w, s_t[(j-1)l+1 \hdots jl)$ \\
-  			$0$ & otherwise 
-  		\end{tabular}
-  		%$
-  		\end{align*}
-
-		We can for example fix a maximum number of steps to the algorithm or stop at one point if $\tilde{x}_{t+1} = \tilde{x}_t$.
-Increasing the number of iterations can of course improve the retrieval rate.
 

### 2014-07-18 Articles/article.tex
adaptation figure a = 2

@@
   %% ;
-  \path[ultra thick]
+  \path[thick]
+  %%%%
+  (nodecircledraw40pt60pt) edge (nodecirclefill20pt20pt)
+  edge (noderectanglefill40pt60pt)
+  edge (noderectanglefill20pt20pt)
+  edge (noderectangledraw40pt20pt)
+  edge (nodecirclefill60pt60pt)
+  %edge (noderectanglefill40pt40pt)
+  edge (noderectangledraw60pt60pt)
+  %%%%%%%%%%%
   (nodecircledraw020pt) edge (nodecirclefill20pt20pt)
   edge (noderectanglefill40pt60pt)
+  edge (noderectanglefill20pt20pt)
+  edge (noderectangledraw40pt20pt)
+  edge (nodecirclefill60pt60pt)
+  %edge (noderectanglefill40pt40pt)
   edge (noderectangledraw60pt60pt)
+  %%%%%%%%%%%%%%
   (nodecirclefill20pt20pt) edge (noderectanglefill40pt60pt)
   edge (noderectangledraw60pt60pt)
+  edge (noderectanglefill20pt20pt)
+  edge (noderectangledraw40pt20pt)
+  %%%%%
+  (nodecirclefill60pt60pt) edge (noderectanglefill40pt60pt)
+  edge (noderectangledraw60pt60pt)
+  edge (noderectanglefill20pt20pt)
+  edge (noderectangledraw40pt20pt)
+  %%%%%
   (noderectanglefill40pt60pt) edge (noderectangledraw60pt60pt)
+  edge (noderectangledraw40pt20pt)
+  %%%%%%%%%%%
+  (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
+  edge (noderectangledraw40pt20pt)
   ;
@@
   			&\begin{tabular}{cl}
-  			$1$ & if $s[(j-1)l+k] \ge  \mbox{select}(\alpha, s[(j-1)\ell+1 \hdots j\ell])$ \\
+  			$1$ & if $s[(j-1)\ell +k] \ge  \mbox{select}(\alpha, s[(j-1)\ell+1 \hdots j\ell])$ \\
   			$0$ & otherwise 
@@
 		\label{formula_density}
-		d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^m 
+		d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^M 
 	\end{align}		
-	, recalling that $m$ is the number of messages in $\mathcal{M}$.
+	, recalling that $M$ is the number of messages in $\mathcal{M}$.
 
@@
 	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits.
-Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula).
-The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2m \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.
+Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({l \choose a}^c)^M}{M!}) \mathop{=}_{M \rightarrow +\infty} M(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula).
+The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2M \left(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.
 
-	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{m-1}$.
+	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{M-1}$.
 
-	$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
+	$\eta_M = P_{retrieve}  \frac{2 M\left(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(M-1)}$
 	%\frac{c}{(c-c_e) \log_2{l \choose a }}

### 2014-07-18 Articles/article.tex
///

@@
 \[
-f: \left\{\begin{array}{rcl}\mathcal{A}^c &\rightarrow& \{0,1\}^{c\cdot{} \ell}\\m&\mapsto& \mu \big| \forall j, \mu[(j-1)\ell+1\dots j\times\ell] = m_j\end{array}\right.\;,
+f: \left\{\begin{array}{rcl}\mathcal{A}^c &\rightarrow& \{0,1\}^{c\cdot{} \ell}\\m&\mapsto& \mu \,\big| \forall j, \mu[(j-1)\ell+1\dots j\cdot \ell] = m_j\end{array}\right.\;,
 \]
-where $\mu[a..b]$ is the subarray of $\mu$ from coordinate $a$ to coordinate $b$.
+where $\mu[a\dots b]$ is the subarray of $\mu$ from coordinate $a$ to coordinate $b$.
 
@@
 		\begin{align*}
-		&\tilde{\mu}'[(j-1)l+k] =\\ \bigg \{
+		&\tilde{\mu}'[(j-1)\ell+k] =\\ \bigg \{
   			&\begin{tabular}{cl}
@@
 
-	As the probability for $i$ (and $i'$) to be active in its cluster for one message $x$ is $\frac{a}{l}$ providing messages are uniformly distributed, it follows that the probability for the edge $(i,i')$ of not being added in the network for $x$ is $1 - \left(a/l\right)^2$.
+	As the probability for $i$ (and $i'$) to be active in its cluster for one message $\mu$ is $a/\ell$ providing messages are uniformly distributed, it follows that the probability for the edge $(i,i')$ of not being added in the network for $\mu$ is $1 - \left(a/l\right)^2$.
 Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed as :
@@
 		\label{formula_density}
-		d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^M 
+		d = 1 - \left( 1 - \left(\frac{a}{\ell}\right)^2 \right)^M 
 	\end{align}		
@@
 
-	Since unit activations are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{l-a}$.
+	Since unit activations are independent (as messages are themselves independent), the probability for none of the vertices of one erased cluster, excepting the correct ones, to achieve the maximum is $\left(1 - d^	{a(c-c_e)}\right)^{\ell-a}$.
 
-	Scores in clusters being also independent, the probability for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective clusters is $\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)}$.
+	Scores in clusters being also independent, the probability for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective clusters is $\left(1 - d^	{a(c-c_e)}\right)^{c_e(\ell-a)}$.
 
@@
 	\begin{align}	
-	P_{err} = 1 -	\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)} 
+	P_{err} = 1 -	\left(1 - d^	{a(c-c_e)}\right)^{c_e(\ell-a)} 
 	\end{align}
@@
 
-	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits.
-Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({l \choose a}^c)^M}{M!}) \mathop{=}_{M \rightarrow +\infty} M(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula).
-The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2M \left(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.
+	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) \ell^2}{2}$ bits.
+Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({\ell \choose a}^c)^M}{M!}) \mathop{=}_{M \rightarrow +\infty} M(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula).
+The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2}$.
 
-	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{M-1}$.
+	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{\ell \choose a}^{c - c_e})^{M-1}$.
 
-	$\eta_M = P_{retrieve}  \frac{2 M\left(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(M-1)}$
+	$\eta_M = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times (1-(\frac{1}{{\ell \choose a}})^{c - c_e})^{-(M-1)}$
 	%\frac{c}{(c-c_e) \log_2{l \choose a }}
@@
 	Knowing the density of the network, which follows formula (\ref{formula_density}), we can compute the laws of probabilities for scores achieved by different type of units in different clusters.
-We can divide units in 5 groups.
+We can divide units in 5 groups with 3 characteristics.
 Subscript $g$ will indicate a unit being part of the message (it should be activated), subscript $b$ the contrary (the unit should not be activated).
@@
 		\begin{align*}
-	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_{ac}(x) P(n_{bc} < x)^{l-a} \right ]^{c - c_e}\\ 
-	 &\times \left [ \sum_{x = 1}^{a(c-1) +\gamma} P_e(x) P(n_{be} < x)^{l-2a} P(n_{abe} < x)^a \right ]^{c_e} \numberthis \label{from_err_th}
+	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_{ac}(x) P(n_{bc} < x)^{\ell-a} \right ]^{c - c_e}\\ 
+	 &\times \left [ \sum_{x = 1}^{a(c-1) +\gamma} P_e(x) P(n_{be} < x)^{\ell-2a} P(n_{abe} < x)^a \right ]^{c_e} \numberthis \label{from_err_th}
 	\end{align*}
 
-	with the approximation that there is few activated units that should be kept active in an erronenous cluster.
+	with the approximation that there is few activated units that should be kept active in an erroneous cluster.
 
@@
 
-		$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$
+		$\eta_m = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{\ell \choose a}} \right )^k \left (\frac{1}{{ell \choose a}} \right )^{c-k} \right ] ^{-(M-1)}$
 
@@
 	%If $\gamma$ is big enough,
-	It follows that $P(\mbox{no other vertex activated in one cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{l-a}$.%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
+	It follows that $P(\mbox{no other vertex activated in one cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{\ell-a}$.%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
 
@@
 	\begin{align}
-	P_{retrieve}=  \left( \sum_{x = 1}^{a ( c- c_e)} P_c(x) P(n_v <x)^{l-a} \right )^{c_e}
+	P_{retrieve}=  \left( \sum_{x = 1}^{a ( c- c_e)} P_c(x) P(n_v < x)^{\ell-a} \right )^{c_e}
 	\label{psi_formula_th}
@@
 Our new is efficiency is written as :
-	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
+	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{\ell \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{\ell \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
 
@@
 
-		The entropy of the messages set can be approximated as $H(\mathcal{M}) \approx m c \log_2 {l \choose a}$.
-From $d = 1 - \left (1- \left(\frac{a}{l}\right)^2 \right)^m$, we can deduce $m \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{l})^2)} \sim - \frac{l^2 \log_2(1-d) \log 2}{a^2}$.
-		We set $\log_2 {l \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$).
-It follows that $\eta \sim \frac{m c \log_2 {l \choose a}}{l^2 {c \choose 2}} \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
+		The entropy of the messages set can be approximated as $H(\mathcal{M}) \approx M c \log_2 {\ell \choose a}$.
+From $d = 1 - \left (1- \left(a/\ell\right)^2 \right)^M$, we can deduce $M \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{\ell})^2)} \sim - \frac{\ell^2 \log_2(1-d) \log 2}{a^2}$.
+		We set $\log_2 {\ell \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$).
+It follows that $\eta \sim \frac{M c \log_2 {\ell \choose a}}{\ell^2 {c \choose 2}} \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
 
@@
 		We can bound the probability $P_{\exists e}$ for a message being "wrongly present" in the network, that is to mean adding it will not add any edge to the network albeit it is not in $\mathcal{M}$.
-By union-bound $P_{\exists e} \le {l \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}$.
+By union-bound $P_{\exists e} \le {\ell \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}$.
 

### 2014-07-21 Articles/article.tex
...

@@
 
-        Note that there are $\binom{\ell}{a}$ possible choices for $a$ activations among $\ell$ units, giving the following correspondance:
+        Note that there are $\binom{\ell}{a}$ possible choices for $a$ activations among $\ell$ units, giving the following correspondence:
 \[
@@
 By construction this matrix is symmetric and binary.
-For a message $\mu$, note that $\mu \mu^{\intercal}$ is the cooccurence matrix associated with $\mu$.
+For a message $\mu$, note that $\mu \mu^{\intercal}$ is the co-occurrence matrix associated with $\mu$.
 Before defining $W$, we first introduce the following matrix:
@@
 
-	We now study the performance of the new retrieving rule on distinct problems of retrieval : first partially erased messages, then erroneous messages.%, finally partially erased messages when the network has been damaged.
+	We now describe some static properties of the networks as the density of edges.
 
-	\section{Retrieval performance}
+	\section{Static properties of multipartite clique networks}
 
-	Messages will be considered as independent and identically distributed according to the uniform distribution.
-We compute theoretical error rates after one iteration of the retrieving rule.
-We compare those results to empirical error rates obtained through simulations\footnote{Simulations are done by taking means on pool of five networks and messages sets, and each point is drawn for a different network and messages set.}.
-We also compare efficiencies of distinct networks for distinct values of the parameter $a$ (weight of the constant weight code) in the sense of information theory and show improvements over the case where $a = 1$.
+	We study the properties of the network after storing messages in it. We are interested in how much edges have been added to the network and if the process introduced confusion between messages.
 
-	\subsection{Retrieving partially erased messages}
+	Messages stored in the network will be considered independent and identically distributed according to the uniform distribution.
+This randomization allows us to compute the theoretical density of the network.
+%under the approximation that edges are independent.
+	Density is a crucial parameter of the network that can be used to predict retrieval rates for different problems. Moreover we compute asymptotic efficiency thanks to the formula for density.
 
-	One can see a partial version of a message $x$ as the result of erasures of symbols of $x$.
-Some symbols of $x$ are replaced by the blank character $\intercal$.	Erasures of a symbol in a message corresponds to an "erased" cluster in the network.
-An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.
+	\subsection{Density}
 
-	\subsubsection{Analytical result}
+	The density $d$ of the network is the proportion of edges present in the network : $d = \frac{\# \{(i, i') \} \, | W_{ii'} = 1 \}}{c(c-1)\ell^2}$.
 
-	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(i, i')$ to be present in the network (i.e.
-$W_{ii'} = 1$).
-We then express the theoretical error rate after one iteration of the retrieving rule in function of the density.
-All this computations (on error rates) are done assuming existences of edges between random units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.
+	\subsubsection{Theoretical density}
+
+	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(i, i')$ to be present in the network (i.e. $W_{ii'} = 1$).
 
@@
 	, recalling that $M$ is the number of messages in $\mathcal{M}$.
+
+	\subsubsection{Simulations}
+
+	Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent, 
+	\begin{figure}[!htb]
+		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
+		\caption{Theoretical and empirical densities for a network of 8 clusters, 256 units per cluster and 4 activated units per cluster}
+			\label{densiteth}
+	\end{figure}
+
+	\subsection{Accepting random messages}
+
+	\section{Maximum theoretical efficiency}
+		It was shown in \cite{Palm1980} that maximal asymptotic capacity of Willshaw networks is $\log 2$. We adapt this result to multipartite clique clustered networks.
+
+		The entropy of the messages set can be approximated as $H(\mathcal{M}) \approx M c \log_2 {\ell \choose a}$.
+From $d = 1 - \left (1- \left(a/\ell\right)^2 \right)^M$, we can deduce $M \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{\ell})^2)} \sim - \frac{\ell^2 \log_2(1-d) \log 2}{a^2}$.
+		We set $\log_2 {\ell \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$).
+It follows that $\eta \sim \frac{M c \log_2 {\ell \choose a}}{\ell^2 {c \choose 2}} \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
+
+		$\eta \sim - 2 k  a^{-2}\log 2 \times \log_2 (1-d)$.
+
+		We can bound the probability $P_{\exists e}$ for a message being "wrongly present" in the network, that is to mean adding it will not add any edge to the network albeit it is not in $\mathcal{M}$.
+By union-bound $P_{\exists e} \le {\ell \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}$.
+
+		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $P_{\exists e}$ and $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]
+
+		Multipartite cliques don't improve theoretical asymptotic efficiency (for not accepting messages that weren't previously seen by the network).
+
+	We now describe the distinct problems of messages retrieval that we study the performance of.
+
+	\section{Problems statements}
+
+	\subsection{Erasures}
+
+	\subsection{Random replacements}
+
+	\subsection{Resilience}
+
+	We now study the performance of the new retrieving rule on those distinct problems of retrieval : first partially erased messages, then erroneous messages.%, finally partially erased messages when the network has been damaged.
+
+	\section{Retrieval performance}
+
+	Thanks to the theoretical formula for density, we compute analytical error rates after one iteration of the retrieving rule.
+We compare those results to empirical error rates obtained through simulations\footnote{Simulations are done by taking means on pool of five networks and messages sets, and each point is drawn for a different network and messages set.}.
+We also compare efficiencies of distinct networks for distinct values of the parameter $a$ (weight of the constant weight code) in the sense of information theory and show improvements over the case where $a = 1$.
+
+	\subsection{Retrieving partially erased messages}
+
+	One can see a partial version of a message $x$ as the result of erasures of symbols of $x$.
+Some symbols of $x$ are replaced by the blank character $\intercal$.	Erasures of a symbol in a message corresponds to an "erased" cluster in the network.
+An erased cluster is a cluster of units which are all inactive, that is to mean set to $0$.
+
+	\subsubsection{Analytical result}
+
+	We then express the theoretical error rate after one iteration of the retrieving rule in function of the density.
+All this computations (on error rates) are done assuming existences of edges between random units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.
 
@@
 
-		Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent,
-
 		Simulations agree with the analytical results for error rate, albeit we can observe a small shift, see Figure \ref{erasuresth}.
@@
 
-	\begin{figure}[!htb]
-		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
-		\caption{Theoretical and empirical densities for a network of 8 clusters, 256 units per cluster and 4 activated units per cluster}
-			\label{densiteth}
-	\end{figure}
+%	\begin{figure}[!htb]
+%		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
+%		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result (for one iteration) in continuous black}
+%			\label{erasuresth}
+%		\end{figure}
 
 		\begin{figure}[!htb]
-		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
+		\includegraphics[width=8.5cm]{Courbes/fig3c4l512e2a2} %{comparaison_regles_pool5_a2c4l512e2}
 		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result (for one iteration) in continuous black}
@@
 
-		$\eta_m = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{\ell \choose a}} \right )^k \left (\frac{1}{{ell \choose a}} \right )^{c-k} \right ] ^{-(M-1)}$
+		$\eta_m = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{\ell \choose a}} \right )^k \left (\frac{1}{{\ell \choose a}} \right )^{c-k} \right ] ^{-(M-1)}$
 
@@
 Our new is efficiency is written as :
-	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{\ell \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{\ell \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
+	$\eta_{m, \psi} = P_{retrieve}  \frac{2 M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{\ell \choose a}^{c - c_e})^{-(M-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
 
@@
 	Figure \ref{comppsi} seems to indicate a linear relationship (after a transition for multiple activities) between $\eta_\psi -\eta_0$ and $\psi$.
-	\section{Maximum theoretical efficiency}
-		It was shown in \cite{Palm1980} that maximal asymptotic capacity of Willshaw networks is $\log 2$. We adapt this result to multipartite clique clustered networks.
-
-		The entropy of the messages set can be approximated as $H(\mathcal{M}) \approx M c \log_2 {\ell \choose a}$.
-From $d = 1 - \left (1- \left(a/\ell\right)^2 \right)^M$, we can deduce $M \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{\ell})^2)} \sim - \frac{\ell^2 \log_2(1-d) \log 2}{a^2}$.
-		We set $\log_2 {\ell \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$).
-It follows that $\eta \sim \frac{M c \log_2 {\ell \choose a}}{\ell^2 {c \choose 2}} \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
-
-		$\eta \sim - 2 k  a^{-2}\log 2 \times \log_2 (1-d)$.
-
-		We can bound the probability $P_{\exists e}$ for a message being "wrongly present" in the network, that is to mean adding it will not add any edge to the network albeit it is not in $\mathcal{M}$.
-By union-bound $P_{\exists e} \le {\ell \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}$.
-
-		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $P_{\exists e}$ and $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]
-
-		Multipartite cliques don't improve theoretical asymptotic efficiency (for not accepting messages that weren't previously seen by the network).
 

### 2014-07-21 astat.r

@@ -381,7 +381,7 @@ if (!is.null(opt$ther)) {
 						newd$Theory <- factor("Analytical error\n (corruptions)")
 						#qpl <- qpl + geom_point(data=tempd, color = "red")
 						#qpl <- qpl + geom_line(aes(y = newd$errorrate,  linetype = newd), data = newd, color = "black")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
-						qpl <- qpl + geom_line(aes(y = newd$errorrate,  color = "Analytical\n result\n (corruptions,\n 1 iter)"))
+						qpl <- qpl + geom_line(aes(y = newd$errorrate,  color = "Analytical\n result\n (1 iter)"))
 					}
 				}
 			}
@@ -423,7 +423,7 @@ if (!is.null(opt$thm)) {
 			for (erasures in unique(data$erasures)) {
 				for (activities in unique(data$activities)) {
 					print(activities)
-					qpl <- qpl + stat_function(fun = function(x) po(x, l, ci, erasures, activities), aes(color = "Analytical\n result\n (erasures,\n 1 iter)"))
+					qpl <- qpl + stat_function(fun = function(x) po(x, l, ci, erasures, activities), aes(color = "Analytical\n result\n (1 iter)"))
 					#qpl
 					#message("Press Return To Continue")
 					#invisible(readLines("stdin", n=1))

### 2014-07-21 sam.jl

@@ -17,6 +17,36 @@ function floyd_combination(n, m)
 	s
 end
 
+function create_comb(n, m, i, j, tab)
+	for k=n-m+1:n
+		t = rand(1:k)
+		if tab[j+t, i] == 0
+			tab[j+t, i] = 1
+		else
+			tab[j+k, i] = 1
+		end
+	end
+end
+
+function cree(n, m)
+	tab = zeros(Int, n)
+	for k=n-m+1:n
+		t = rand(1:k)
+		if tab[t] == 0 
+			tab[t] = 1
+		else
+			tab[k] = 1
+		end
+	end
+	tab
+end
+
+function create_line(n, m, i, lt, tab)
+	for j=0:n:lt
+		create_comb(n, m, i, j, tab)
+	end
+end
+
 function rand_combination(n, m)
 	s = floyd_combination(n, m)
 	res = zeros(Bool, n)
@@ -155,6 +185,7 @@ function create_messages(l, c, m, activities = 1, csparse = 0)#; useBitArray = f
 						sparseMessages[(j-1)*l + k, i] = 1
 					end
 				end
+			#	create_line(l, activities, i, n
 			end
 		end
 		###############" Attention les messages n'ont plus aucun rapport avec les sparseMessages !!!!!!!

### 2014-07-21 Articles/article.tex
...

@@
 		\includegraphics[width=8.5cm]{Courbes/fig3c4l512e2a2} %{comparaison_regles_pool5_a2c4l512e2}
-		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result (for one iteration) in continuous black}
+		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result (for one iteration) in continuous black}
 			\label{erasuresth}
@@
 	\begin{figure}[!htb]
-		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
-		\caption{2 activities per cluster, 4 clusters, 512 units per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
+		\includegraphics[width=8.5cm]{Courbes/fig4c4l512a2e1corr}%remplacement_figure3g1}
+		\caption{2 activities per cluster, 4 clusters, 512 units per cluster, one erroneous cluster, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
 		\label{corruptth}

### 2014-07-21 Articles/article.tex
...

@@
 	\subsubsection{Simulations}
-	See Figure \ref{corruptth} compares the two rules.
+	See Figure \ref{corruptth} compares the two choices $w = 1$ and $w = a$.
 	"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
@@
 	\begin{figure}[!htb]
-		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
-		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
+		\includegraphics[width=8.5cm]{Courbes/figpsic8l256e4psi2percent}%thpsi_c8l256e4}
+		\caption{$\psi = 0.02$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
 		\label{psith}

### 2014-07-21 astat.r

@@ -398,7 +398,8 @@ if (!is.null(opt$thpsi)) {
 					for(activities in unique(data$activities)) {
 						newd = data
 						newd$errorrate = sapply(data$m, function (x) { ((1 - ptotalpsi(x, ci, erasures, l, activities, psi))) })
-						qpl <- qpl + geom_line(aes(y = newd$errorrate), color = "black")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
+						#qpl <- qpl + geom_line(aes(y = newd$errorrate), color = "black")#, geom="line")#+ geom_line(aes(x = data$m, y=1-sapply(data$m, function(x) ptotal(x, 4, 1, 512)))) #
+						qpl <- qpl + geom_line(aes(y = newd$errorrate,  color = "Analytical\n result\n (1 iter)"))
 					}
 				}
 			}

### 2014-07-22 Articles/article.tex
Ajout figure + explications problèmes

@@
 
-	As the probability for $i$ (and $i'$) to be active in its cluster for one message $\mu$ is $a/\ell$ providing messages are uniformly distributed, it follows that the probability for the edge $(i,i')$ of not being added in the network for $\mu$ is $1 - \left(a/l\right)^2$.
+	The probability for $i$ (and $i'$) to be active in its cluster for one message $\mu$ is $a/\ell$ providing messages are uniformly distributed.
+It follows that the probability for the edge $(i,i')$ of not being added in the network after $\mu$ is being stored is $1 - \left(a/l\right)^2$.
 Since messages are independent, the density $d$, which is the probability for an edge to be in the network, can be expressed as :
@@
 
+	We are interested in distinct problems of messages retrieval.
+We detail what those problems are.
+Since those problems vary in hardness, we propose distinct measures for efficiencies.
+Efficiency measures the ratio of information effectively retrieved over the information used for storage.
+
 	\subsection{Erasures}
+
+	A message $m$ can be recovered from a partial probe $\tilde{m}$ where some symbols, say $c_e$, with indexes $\{j_1, \dots , j_{c_e} \}$ have been replaced by the blank symbol $\intercal$, with $\intercal \not\in\mathcal{A}$ (recall $\mathcal{A}$ is the alphabet we are working on).
+We have $\tilde{m} \in \left( \mathcal{A} \cup \{ \intercal \}\right)^c$.
+
+	We can extend the mapping $f$ to $\left( \mathcal{A} \cup \{ \intercal \}\right)^c$, by associating to the symbol $\intercal$ a cluster where none of the units are activated.
+If we consider the binary representation $\mu$ of $m$, erased symbols corresponds to erased clusters.
+An erased cluster is a cluster where none of the units are activated.
+Formally the partial probe $\tilde{\mu}$ is such that for all $j\in [c]$ and $k \in [\ell ]$, \[
+		\tilde{\mu}[(j-1)\ell+k] = \bigg \{ \begin{array}{cl} 0 & \mbox{if } j\in \{j_1, \dots , j_{c_e} \}\\
+													\mu[(j-1)\ell+k] & \mbox{otherwise}	
+	\end{array}\]
+
+	An erasure is tantamount to lack of information, but associative memories can also retrieve messages from corrupted probes.
 
@@
 
+	We propose one model of message corruption.
+As all symbols in $\mathcal{A}$ all contains exactly $a$ ones, symbols which do not belong to $\mathcal{A}$ can be easily detected.
+We therefore restrict ourselves to random replacements by symbols in $\mathcal{A}$.
+
+	A message $m$ can be recovered from a corrupt probe $\tilde{m}$ where some symbols, say $c_e$, with indexes $\{j_1, \dots , j_{c_e} \}$ have been replaced by random elements of $\mathcal{A}$.
+We have $\tilde{m} \in \mathcal{A}^c$.
+
+	Concerning the binary representation, we now have a corrupt probe $\tilde{\mu} = f(\tilde{m})$.
+
 	\subsection{Resilience}
+
+	The problem of resilience takes into account the possibility for the network of sustaining damages.
+Despite those, the network can still work as an associative memory, albeit with decreased performance.
 
@@
 
-	Thanks to the theoretical formula for density, we compute analytical error rates after one iteration of the retrieving rule.
-We compare those results to empirical error rates obtained through simulations\footnote{Simulations are done by taking means on pool of five networks and messages sets, and each point is drawn for a different network and messages set.}.
+	Thanks to the theoretical formula for density (\ref{formula_density}), we compute analytical error rates after one iteration of the retrieving rule.
+We compare those results to empirical error rates obtained through simulations\footnote{Simulations are done by taking means on pool of several networks and messages sets, and each point is drawn for different networks and messages sets.}.
 We also compare efficiencies of distinct networks for distinct values of the parameter $a$ (weight of the constant weight code) in the sense of information theory and show improvements over the case where $a = 1$.
@@
 
-	One can see a partial version of a message $x$ as the result of erasures of symbols of $x$.
+	One can see a partial version of a message $\mu$ as the result of erasures of symbols of $x$.
 Some symbols of $x$ are replaced by the blank character $\intercal$.	Erasures of a symbol in a message corresponds to an "erased" cluster in the network.
@@
 
-	We then express the theoretical error rate after one iteration of the retrieving rule in function of the density.
+	We express the theoretical error rate after one iteration of the retrieving rule in function of the density.
 All this computations (on error rates) are done assuming existences of edges between random units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.
@@
 
-	Knowing the density of the network, which follows formula (\ref{formula_density}), we can compute the laws of probabilities for scores achieved by different type of units in different clusters.
+	Knowing the density of the network, which follows formula (\ref{formula_density}), we can compute distributions for scores achieved by different type of units in different clusters.
 We can divide units in 5 groups with 3 characteristics.
@@
 
+	\section*{Annex}
+
+	\subsection*{Proof for asymtptotic efficiency}
+
+	\subsection*{Adapting other rules}
+
+	SUM-OF-MAX can be adapted to multipartie clique networks and still delivers improvements
+
+	\begin{figure}[!htb]
+		\includegraphics[width=8.5cm]{Courbes/comp_rulesmax}%thpsi_c8l256e4}
+		\caption{Comparison for different retrieval rules, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 5 networks with 1000 sampled messages}
+		\label{fmaxth}
+	\end{figure}
+
 	%Marche mieux pour de petits c --> le faire sur le sparse ?

### 2014-07-22 astat.r

@@ -135,7 +135,9 @@ if(!is.null(opt$winners)) {
 		data = subset(data, winners == opt$winners)
 	}
 }
-data = subset(data, maxiterations == 1 | maxiterations == 4)
+################################################################################
+#data = subset(data, maxiterations == 1 | maxiterations == 4)
+
 if(!is.null(opt$tests)) { data = subset(data, tests == opt$tests) }
 if(!is.null(opt$fsum)) { data = subset(data, fsum == opt$fsum) }
 if(!is.null(opt$fcorrupt)) { data = subset(data, fcorrupt == opt$fcorrupt) }

### 2014-07-22 Articles/article.tex
meilleure figure densités

@@
 	\begin{figure}[!htb]
-		\includegraphics[width=8.5cm]{Courbes/remplacement_densite_c8l256a4}
-		\caption{Theoretical and empirical densities for a network of 8 clusters, 256 units per cluster and 4 activated units per cluster}
+		\includegraphics[width=8.5cm]{Courbes/c5l256densities}%remplacement_densite_c8l256a4}
+		\caption{Theoretical and empirical densities for networks of 5 clusters, 256 units per cluster }
 			\label{densiteth}

### 2014-07-22 astat.r

@@ -442,7 +442,10 @@ if (!is.null(opt$thd)) {
 	for (l in unique(data$l)) {
 		for (c in unique(data$c)) {
 			for (activities in unique(data$activities)) {
-				qpl <- qpl + stat_function(fun = function(x) dens(x, l, activities), color = "black")
+				#qpl <- qpl + stat_function(fun = function(x) dens(x, l, activities), color = "black")
+				newd = data
+				#newd$activities[] <- "o"
+				qpl <- qpl + stat_function(fun = function(x) dens(x, l, activities), data = newd, aes(color = paste("Analytical\n density", sprintf("\n%d", activities))))
 			}
 		}
 	}

### 2014-07-22 Articles/article.tex
amélioration figure 1

@@
   (nodecircledraw40pt60pt) edge (nodecirclefill20pt20pt)
-  edge (noderectanglefill40pt60pt)
-  edge (noderectanglefill20pt20pt)
-  edge (noderectangledraw40pt20pt)
+  edge (noderectanglefill20pt60pt)
+  edge (noderectanglefill60pt20pt)
+  edge (noderectangledraw60pt20pt)
   edge (nodecirclefill60pt60pt)
   %edge (noderectanglefill40pt40pt)
-  edge (noderectangledraw60pt60pt)
+  edge (noderectangledraw20pt60pt)
   %%%%%%%%%%%
   (nodecircledraw020pt) edge (nodecirclefill20pt20pt)
-  edge (noderectanglefill40pt60pt)
-  edge (noderectanglefill20pt20pt)
-  edge (noderectangledraw40pt20pt)
+  edge (noderectanglefill20pt60pt)
+  edge (noderectanglefill60pt20pt)
+  edge (noderectangledraw60pt20pt)
   edge (nodecirclefill60pt60pt)
   %edge (noderectanglefill40pt40pt)
-  edge (noderectangledraw60pt60pt)
+  edge (noderectangledraw20pt60pt)
   %%%%%%%%%%%%%%
-  (nodecirclefill20pt20pt) edge (noderectanglefill40pt60pt)
-  edge (noderectangledraw60pt60pt)
-  edge (noderectanglefill20pt20pt)
-  edge (noderectangledraw40pt20pt)
+  (nodecirclefill20pt20pt) edge (noderectanglefill20pt60pt)
+  edge (noderectangledraw20pt60pt)
+  edge (noderectanglefill60pt20pt)
+  edge (noderectangledraw60pt20pt)
   %%%%%
-  (nodecirclefill60pt60pt) edge (noderectanglefill40pt60pt)
-  edge (noderectangledraw60pt60pt)
-  edge (noderectanglefill20pt20pt)
-  edge (noderectangledraw40pt20pt)
+  (nodecirclefill60pt60pt) edge (noderectanglefill20pt60pt)
+  edge (noderectangledraw60pt20pt)
+  edge (noderectanglefill60pt20pt)
+  edge (noderectangledraw20pt60pt)
   %%%%%
-  (noderectanglefill40pt60pt) edge (noderectangledraw60pt60pt)
-  edge (noderectangledraw40pt20pt)
+  (noderectanglefill20pt60pt) edge (noderectangledraw20pt60pt)
+  edge (noderectangledraw60pt20pt)
   %%%%%%%%%%%
-  (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
-  edge (noderectangledraw40pt20pt)
+  (noderectanglefill60pt20pt) edge (noderectangledraw20pt60pt)
+  edge (noderectangledraw60pt20pt)
   ;
@@
 	Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent, 
+	The higher $a$ is, the quicker density approaches $1$.
+
+	Multipartite cliques saturate quicker.
+
 	\begin{figure}[!htb]

### 2014-07-23 Articles/article.tex
...

@@
 
-	We study the properties of the network after storing messages in it. We are interested in how much edges have been added to the network and if the process introduced confusion between messages.
+	We study the properties of the network once some messages have been stored in it.
+We are interested in how much edges have been added to the network and if the process introduced confusion between messages.
 
@@
 
-	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(i, i')$ to be present in the network (i.e. $W_{ii'} = 1$).
+	We first compute the theoretical density of the network, that is to mean the probability for an edge $(i, i')$ to be present in the network (i.e. $W_{ii'} = 1$).
 
@@
 
-	Multipartite cliques saturate quicker.
+	Multipartite cliques saturate quicker, which was expected since they take much more edges.
 
@@
 
+	\subsection{Rate of the network}
+
+	The rate $R$ of the network measures how much information is stored in the network compared to what it takes to store it. Note it doesn't take into account how effectively messages are retrieved.
+
+		The matrix $W$ used to store the network is binary, symmetric, with null blocks of size $\ell^2$ on the diagonal. It can therefore be stored in memory as $\frac{c(c-1) \ell^2}{2}$ bits.
+
+		Since messages are not stored in an ordered fashion, the entropy $H(\mathcal{M})$ of the set of messages is $\log_2(\frac{({\ell \choose a}^c)^M}{M!}) \mathop{=}_{M \rightarrow +\infty} M(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2}) + O(\log_2(M)) $ (thanks to  Stirling's formula).% The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2}$.
+
+		$R$ can be written $\frac{2H(\mathcal{M})}{c(c-1) \ell^2}$.
+
+		A very good approximation is thereby $R = \frac{2M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2}$.
+
+		The efficiency of the network measures how much information can be retrieved compared to how much could be at the maximum. The efficiency is called $\eta$. $\eta = P_{retrieve} R  h^{-1}$.
+
 	\subsection{Accepting random messages}
 
-	\section{Maximum theoretical efficiency}
+	\subsection{Maximum theoretical efficiency}
 		It was shown in \cite{Palm1980} that maximal asymptotic capacity of Willshaw networks is $\log 2$. We adapt this result to multipartite clique clustered networks.
 
-		The entropy of the messages set can be approximated as $H(\mathcal{M}) \approx M c \log_2 {\ell \choose a}$.
-From $d = 1 - \left (1- \left(a/\ell\right)^2 \right)^M$, we can deduce $M \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{\ell})^2)} \sim - \frac{\ell^2 \log_2(1-d) \log 2}{a^2}$.
-		We set $\log_2 {\ell \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$).
-It follows that $\eta \sim \frac{M c \log_2 {\ell \choose a}}{\ell^2 {c \choose 2}} \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
-
-		$\eta \sim - 2 k  a^{-2}\log 2 \times \log_2 (1-d)$.
-
-		We can bound the probability $P_{\exists e}$ for a message being "wrongly present" in the network, that is to mean adding it will not add any edge to the network albeit it is not in $\mathcal{M}$.
-By union-bound $P_{\exists e} \le {\ell \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}$.
-
-		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $P_{\exists e}$ and $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]
+		Asymptotic efficiency of multipartite clique networks is also $\log 2$.
 
@@
 Since those problems vary in hardness, we propose distinct measures for efficiencies.
-Efficiency measures the ratio of information effectively retrieved over the information used for storage.
+We first compute the rate of the network.
+Efficiency measures the ratio of information effectively retrieved over the hardness of the problem.
+It can be expressed in function of the rate $R$, the retrieval rate $P_{retrieve}$ and some measure of hardness of the problem $h$.
+
+	To account for hardness of problems, we consider an "optimal" associative memory.
+We are interested in retrieving messages with a few iterations at most.
+However an "optimal" memory could store $\mathcal{M}$ with $H(\mathcal{M})$ bits and recover messages by maximum likelihood (with ambiguities causing errors in our study, to simplify the problem).
+We detail the performance of such a memory for each problem, which gives use a measure for the hardness of each problem.
 
@@
 
-	A message $m$ can be recovered from a partial probe $\tilde{m}$ where some symbols, say $c_e$, with indexes $\{j_1, \dots , j_{c_e} \}$ have been replaced by the blank symbol $\intercal$, with $\intercal \not\in\mathcal{A}$ (recall $\mathcal{A}$ is the alphabet we are working on).
+	\subsubsection{Model}
+
+	A message $m$ can be recovered from a partial probe $\tilde{m}$ where some symbols, say $c_e$, of indexes $\{j_1, \dots , j_{c_e} \}$, have been replaced by the blank symbol $\intercal$, with $\intercal \not\in\mathcal{A}$ (recall $\mathcal{A}$ is the alphabet we are working on).
 We have $\tilde{m} \in \left( \mathcal{A} \cup \{ \intercal \}\right)^c$.
@@
 If we consider the binary representation $\mu$ of $m$, erased symbols corresponds to erased clusters.
-An erased cluster is a cluster where none of the units are activated.
+An erased cluster is a cluster where all units are set to $0$.
 Formally the partial probe $\tilde{\mu}$ is such that for all $j\in [c]$ and $k \in [\ell ]$, \[
@@
 
-	An erasure is tantamount to lack of information, but associative memories can also retrieve messages from corrupted probes.
+	\subsubsection{Hardness of the problem}
+
+	An erasure is tantamount to lack of information, but associative memories can also retrieve messages from corrupt probes.
 
@@
 
+	\subsubsection{Model}	
 	We propose one model of message corruption.
@@
 
-	A message $m$ can be recovered from a corrupt probe $\tilde{m}$ where some symbols, say $c_e$, with indexes $\{j_1, \dots , j_{c_e} \}$ have been replaced by random elements of $\mathcal{A}$.
+	A message $m$ can be recovered from a corrupt probe $\tilde{m}$ where some symbols, say $c_e$, of indexes $\{j_1, \dots , j_{c_e} \}$ have been replaced by random elements of $\mathcal{A}$.
 We have $\tilde{m} \in \mathcal{A}^c$.
@@
 
+	\subsubsection{Hardness of the problem}
+
+	$\eta_m = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{\ell \choose a}} \right )^k \left (\frac{1}{{\ell \choose a}} \right )^{c-k} \right ] ^{-(M-1)}$
+
 	\subsection{Resilience}
+
+	\subsubsection{Model}
 
@@
 Despite those, the network can still work as an associative memory, albeit with decreased performance.
+
+	\subsubsection{Hardness of the problem}
 
@@
 
-	We provide a formula for error rate in case of messages with corrupted clusters.
+	We provide a formula for error rate in case of retrieving messages from a corrupt probe.
 
-	Messages can be corrupted, our models for errors is : given $c_e$ the number of erroneous clusters, we draw at random $c_e$ clusters and in each of these draw at random, uniformly, a new letter in the alphabet that will replace the old one (it could be the same).
+	%Messages can be corrupted, our models for errors is : given $c_e$ the number of erroneous clusters, we draw at random $c_e$ clusters and in each of these draw at random, uniformly, a new letter in the alphabet that will replace the old one (it could be the same).
 
 	Knowing the density of the network, which follows formula (\ref{formula_density}), we can compute distributions for scores achieved by different type of units in different clusters.
+
 	We can divide units in 5 groups with 3 characteristics.
-Subscript $g$ will indicate a unit being part of the message (it should be activated), subscript $b$ the contrary (the unit should not be activated).
-Subscript $a$ means the unit is already activated.
+Subscript $g$ will indicate a unit being part of the message (it should be activated for the message to be retrieved), subscript $b$ the contrary (the unit should not be activated).
+Subscript $a$ means the unit is already activated, subscript $d$ that it is deactivated at the beginning.
 Subscript $c$ corresponds to a correct cluster, $e$ to an erroneous cluster.
-	Correct units in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
+For example $s_{agc}$ designates the score achieved by an already \emph{a}ctivated unit (a) which should stay activated (g) in an uncorrupted cluster (c).
+Note that there is some redundancy.
+
+	Correctly activated units in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
 	Being connected to a given activated unit in a corrupted cluster occurs with probability $d$, since errors are identically distributed.
@@
 	Correct units in corrupted clusters achieve at least a score of $a(c - c_e)$. 
-	$P(n_{ge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
+	$P(n_{dge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
 
@@
 	%$P(n_{be} = x) = P(n_{bc} = x) = {c - 1 \choose x} d^x (1-d)^{c- 1 -x}$
-	Finally $P(n_{be} = x) = P(n_{bc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
+	Finally $P(n_{dbe} = x) = P(n_{dbc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
 
@@
 of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_{ac} (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp.
-$P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = x)^k P(n_{ge} > x)^{a-k}$)
+$P_e(x) = \sum_{k = 1}^a { a \choose k } P(s_{dge} = x)^k P(s_{dge} > x)^{a-k}$)
 
@@
 		\begin{align*}
-	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_{ac}(x) P(n_{bc} < x)^{\ell-a} \right ]^{c - c_e}\\ 
-	 &\times \left [ \sum_{x = 1}^{a(c-1) +\gamma} P_e(x) P(n_{be} < x)^{\ell-2a} P(n_{abe} < x)^a \right ]^{c_e} \numberthis \label{from_err_th}
+	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_{ac}(x) P(s_{dbc} < x)^{\ell-a} \right ]^{c - c_e}\\ 
+	 &\times \left [ \sum_{x = 1}^{a(c-1) +\gamma} P_e(x) P(s_{dbe} < x)^{\ell-2a} P(s_{abe} < x)^a \right ]^{c_e} \numberthis \label{from_err_th}
 	\end{align*}
@@
 
-	As information on a message is shared across edges with multiple activated units per cluster, such networks are more resilient to damages (for one message information is carried by $a^2 {c \choose 2}$ edges.
+	As information on a message is shared across edges, networks with higher values of $a$ are more resilient to damages (as information on one message is carried by $a^2 {c \choose 2}$ edges.
 $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.
@@
 
+	The entropy of the messages set can be approximated as $H(\mathcal{M}) \approx M c \log_2 {\ell \choose a}$.
+From $d = 1 - \left (1- \left(a/\ell\right)^2 \right)^M$, we can deduce $M \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{\ell})^2)} \sim - \frac{\ell^2 \log_2(1-d) \log 2}{a^2}$.
+		We set $\log_2 {\ell \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$).
+It follows that $\eta \sim \frac{M c \log_2 {\ell \choose a}}{\ell^2 {c \choose 2}} \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.
+
+		$\eta \sim - 2 k  a^{-2}\log 2 \times \log_2 (1-d)$.
+
+		We can bound the probability $P_{\exists e}$ for a message being "wrongly present" in the network, that is to mean adding it will not add any edge to the network albeit it is not in $\mathcal{M}$.
+By union-bound $P_{\exists e} \le {\ell \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}$.
+
+		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $P_{\exists e}$ and $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]
+
 	\subsection*{Adapting other rules}

### 2014-07-23 Articles/article.tex
...

@@
 
-	The rate $R$ of the network measures how much information is stored in the network compared to what it takes to store it. Note it doesn't take into account how effectively messages are retrieved.
+	The rate $R$ of the network measures how much information is stored in the network compared to what it takes to store the network itself.
+Note it doesn't take into account how effectively messages are retrieved (if we store too much messages in the network, the proportion of retrieved messages approaches $0$ but the rate is high)
 
@@
 
-		$R$ can be written $\frac{2H(\mathcal{M})}{c(c-1) \ell^2}$.
+		$R$ can be written as $\frac{2H(\mathcal{M})}{c(c-1) \ell^2}$.
 
-		A very good approximation is thereby $R = \frac{2M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2}$.
+		A very good approximation is thereby \begin{align}
+		R \approx \frac{2M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2}
+		\label{rateth}
+		\end{align}
 
-		The efficiency of the network measures how much information can be retrieved compared to how much could be at the maximum. The efficiency is called $\eta$. $\eta = P_{retrieve} R  h^{-1}$.
+		The efficiency of the network measures how much information can be retrieved compared to how much could be at the maximum. The efficiency is called $\eta$. $\eta = P_{retrieve} R  h$.
 
@@
 Since those problems vary in hardness, we propose distinct measures for efficiencies.
-We first compute the rate of the network.
 Efficiency measures the ratio of information effectively retrieved over the hardness of the problem.
@@
 
-	We can extend the mapping $f$ to $\left( \mathcal{A} \cup \{ \intercal \}\right)^c$, by associating to the symbol $\intercal$ a cluster where none of the units are activated.
+	We can extend the mapping $f$ to $\left( \mathcal{A} \cup \{ \intercal \}\right)^c$, by associating to the symbol $\intercal$ an "erased cluster" where none of the units are activated.
 If we consider the binary representation $\mu$ of $m$, erased symbols corresponds to erased clusters.
-An erased cluster is a cluster where all units are set to $0$.
+%An erased cluster is a cluster where all units are set to $0$.
 	Formally the partial probe $\tilde{\mu}$ is such that for all $j\in [c]$ and $k \in [\ell ]$, \[ 
@@
 	\subsubsection{Hardness of the problem}
+
+	We compute the probability for a message $m$ and a partial probe $\tilde{m}$ to engender confusion.
+
+	Let $j\not\in \{j_1, \dots , j_{c_e} \}$ be the index of a non-erased symbol in $\tilde{m}$.
+The probability for another message $m'$ in $\mathcal{M}$ to satisfy $m'_j = \tilde{m}_j$ is $1/|\mathcal{A}| = \binom{l}{a}^{-1}$.
+As symbols of a message are independent (since messages are uniformly distributed), the probability that for all $j\not\in \{j_1, \dots , j_{c_e} \}$, $m'_{j} = \tilde{m}_j$ is ${\ell \choose a}^{-(c - c_e)}$.
+Since messages are independent the probability for all other messages in $\mathcal{M}$ not to be equal to $\tilde{m}$ on non-erased symbols is $\left(1-{\ell \choose a}^{-(c - c_e)}\right)^{M-1}$.
+We define $h_{erasures}$ the hardness of the problem as the inverse of that last probability :
+
+	\begin{align}
+		h_{erasures} = \left(1-{\ell \choose a}^{-(c - c_e)}\right)^{-(M-1)}
+		\label{herrth}
+	\end{align}
+
+	Notice increasing the size of the alphabet makes the problem easier as confusion
 
@@
 Despite those, the network can still work as an associative memory, albeit with decreased performance.
+The network $W$ first sustains random binary noises of magnitude $\psi$.
+The new matrix is called $\tilde{W}$ and satisfies for all $i$ and $i'$ in $[c \cdot \ell ]$, %$W_{ii'} = \big \begin{array}{ccc} W & o\end{array}$
 

### 2014-07-23 Articles/article.tex
changement courbes + articles

@@
 We are interested in how much edges have been added to the network and if the process introduced confusion between messages.
+We also compute the rate of the network in the sense of information theory (ratio between information stored in the network and the information used to store the network)
 
-	Messages stored in the network will be considered independent and identically distributed according to the uniform distribution.
+	In this document, messages stored in the network will be considered independent and identically distributed according to the uniform distribution.
 This randomization allows us to compute the theoretical density of the network.
@@
 	The rate $R$ of the network measures how much information is stored in the network compared to what it takes to store the network itself.
-Note it doesn't take into account how effectively messages are retrieved (if we store too much messages in the network, the proportion of retrieved messages approaches $0$ but the rate is high)
+Note it doesn't take into account how effective messages retrieving is (if we store too much messages in the network, the proportion of retrieved messages approaches $0$ but the rate is high)
 
@@
 Since those problems vary in hardness, we propose distinct measures for efficiencies.
-Efficiency measures the ratio of information effectively retrieved over the hardness of the problem.
-It can be expressed in function of the rate $R$, the retrieval rate $P_{retrieve}$ and some measure of hardness of the problem $h$.
+Efficiency measures the ratio of information effectively retrieved times the hardness of the problem.
+It can be expressed as the product of the rate of the network $R$ (how much information is stored), the retrieval rate $P_{retrieve}$ (how much information is effectively retrieved) and some measure of hardness of the problem $h$ (how hard the problem really is).
+	\begin{align}
+		\eta = P_{retrieve} R \cdot h
+		\label{defeff}
+	\end{align}
 
 	To account for hardness of problems, we consider an "optimal" associative memory.
-We are interested in retrieving messages with a few iterations at most.
+In this document, we are interested in retrieving messages with a few iterations at most.
 However an "optimal" memory could store $\mathcal{M}$ with $H(\mathcal{M})$ bits and recover messages by maximum likelihood (with ambiguities causing errors in our study, to simplify the problem).
+For example, such a memory would scan over all messages to find all messages corresponding to a partial probe.
 We detail the performance of such a memory for each problem, which gives use a measure for the hardness of each problem.
@@
 
-	Notice increasing the size of the alphabet makes the problem easier as confusion
+	Notice increasing the size of the alphabet makes the problem easier as confusion is less likely.
 
@@
 
-	$\eta_m = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{\ell \choose a}} \right )^k \left (\frac{1}{{\ell \choose a}} \right )^{c-k} \right ] ^{-(M-1)}$
+	If a message $m'$ is equal to $\tilde{m}$ over $k$ symbols with $k > c - c_e$, the likelihood principle leads to the conclusion $\tilde{m}$ is more likely to be a probe for $m'$ than for $m$.
+This causes errors in the retrieving process.
+As ambiguities also causes errors in our model, there should not be a message $m' \neq m$ in $\mathcal{M}$ that is closer or as close as $m$ of $\tilde{m}$ for the Haaming distance (number of different indexes where symbols differ).
+
+	The probability for an index $j$ and a message $m'$ that $m'_j = \tilde{m}_j$ is $|\mathcal{A}|^{-1} = \binom{\ell}{a}^{-1}$.
+The number of symbols over which $m'$ and $\tilde{m}$ are equal follows a binomial law of Bernoulli parameter $\binom{\ell}{a}^{-1}$, therefore the probability that $m'$ is at a Hamming distance of at least $c_e +1$ of $\tilde{m}$ is $ \sum_{k=c_e+1}^c \binom{c}{k} \left (1-{\ell \choose a}^{-1} \right )^k {\ell \choose a}^{-(c-k)}$.
+As messages are independent we deduce :
+
+	\begin{align}
+	h_{corrupt} = \left [\sum_{k=c_e+1}^c \binom{c}{k} \left (1-{\ell \choose a}^{-1} \right )^k {\ell \choose a}^{-(c-k)} \right ] ^{-(M-1)}
+	\end{align}
+
+	%$\eta_M = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{\ell \choose a}} \right )^k \left (\frac{1}{{\ell \choose a}} \right )^{c-k} \right ] ^{-(M-1)}$
 
@@
 Despite those, the network can still work as an associative memory, albeit with decreased performance.
-The network $W$ first sustains random binary noises of magnitude $\psi$.
-The new matrix is called $\tilde{W}$ and satisfies for all $i$ and $i'$ in $[c \cdot \ell ]$, %$W_{ii'} = \big \begin{array}{ccc} W & o\end{array}$
+In our model, the network $W$ first sustains random binary noises of magnitude $\psi$.
+The new matrix is called $\tilde{W}$ and satisfies for all $i$ and $i'$ in $[c \cdot \ell ]$, $W_{ii'} = \Bigg \{ \begin{array}{ll}
+	0 = W_{ii'} & \mbox{if $i$ and $i'$ are in the same cluster}\\
+	1-W_{ii'} & \mbox{ with probability }  \psi\\
+	W_{ii'} & \mbox{with probability } 1 - \psi\end{array}$
+
+	%simulations faites avec erreurs non symétriques !!
 
@@
 
-	We now study the performance of the new retrieving rule on those distinct problems of retrieval : first partially erased messages, then erroneous messages.%, finally partially erased messages when the network has been damaged.
+	The resilience problem is composed of two problems : transmitting information (the matrix $W$) through a binary symmetric channel and retrieving messages with the output of the channel $\tilde{W}$.
+We therefore express $h_{resilience}$ as the product of the two respective hardnesses.
+The capacity $\mathcal{C}(\psi)$ of the binary symmetric channel (with noise $\psi$) measures how much information can be transmitted through this channel with vanishing probability of error.
+We have $C(\psi) = 1 - H(\psi) = 1 + \psi \log_2 (\psi) + (1-\psi) \log_2 (1-\psi)$.
+We choose its inverse to qualify the hardness of transmitting through this canal.
+We have already computed the hardness of the "erasures" problem (c.f.~(\ref{herrth})).
+Therefore :
+
+	\begin{align}
+		h_{resilience} = h_{erasures} \times \left( 1 - H(\psi) \right)^{-1}
+	\end{align}	
+	, where $H(\psi) = -(\psi \log_2 (\psi) + (1-\psi) \log_2 (1-\psi)$
+
+	\vspace*{1mm}We now study the performance of the new retrieving rule on those distinct problems of retrieval : first partially erased messages, then erroneous messages.%, finally partially erased messages when the network has been damaged.
 
@@
 
-	In order to compare distinct networks using distinct alphabets (due to variations of the weight parameter $a$), we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
+	In order to compare distinct networks using distinct alphabets (due to variations of the parameter $a$), we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
 A perfect associative memory would use exactly the same number of bits than the original messages and retrieve messages by maximum likelihood (ambiguities causing errors).
@@
 
-		 For one iteration, as long as the parameter $w$ is between $1$ and $a$, there is no effect on retrieving.
-However for $4$ iterations, the choice of $w = a$ allows a shift of about $5000$ messages stored on top of those stored for $w = 1$.
-The variant rule can thus be considered a significant improvement over the classic one for multipartite clique networks (recall that $w = 1$ amounts to the classic retrieving rule).
+		 For one iteration, as long as the parameter $w$ is between $1$ and $a$, there is no effect on retrieving (in this setting selecting amounts to take the maximum as all units of the original message achieve the same score).
+However for $4$ iterations, the choice of $\alpha = a$ allows a shift of about $5000$ messages stored on top of those stored for $\alpha = 1$.
+The variant rule can thus be considered a significant improvement over the classic one for multipartite clique networks (recall that $\alpha = 1$ amounts to the classic retrieving rule).
 
@@
 
-		Thanks to the efficiency defined in the previous section, we can easily compare distinct choices of parameters $a$ (we now take $w = a$ since it is the most efficient choice in practice) over distinct number of erased clusters.
+		Thanks to the efficiency defined in the previous section, we can easily compare distinct choices of parameters $a$ (we now take $\alpha = a$ since it is the most efficient choice in practice) over distinct number of erased clusters.
 Figure \ref{comperth} shows improvements in efficiencies over parameter $a =1$.
@@
 
-	Correctly activated units in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
+	%Correctly activated units in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$. 
 	Being connected to a given activated unit in a corrupted cluster occurs with probability $d$, since errors are identically distributed.
@@
 The probability it has to be connected to a random activated unit in an erroneous cluster is $d$.
-Thereby its law is :
+Thereby the law for its score $s_{agc}$ is :
 
 	%$P(n_{agc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$
-	$P(n_{agc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
+	$P(s_{agc} = a(c - c_e - 1) + \gamma + x) = {a c_e \choose x} d^x (1-d)^{a ce-x}$
 
 	Correct units in corrupted clusters achieve at least a score of $a(c - c_e)$. 
-	$P(n_{dge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
+	$P(s_{dge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
 
@@
 	Activated units benefits of the memory effect $\gamma$ :	\\
-	$P(n_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$
+	$P(s_{abe} = \gamma + x) = {a(c - 1) \choose x} d^x (1-d)^{a(c-1)-x}$
 	%$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$
@@
 	%$P(n_{be} = x) = P(n_{bc} = x) = {c - 1 \choose x} d^x (1-d)^{c- 1 -x}$
-	Finally $P(n_{dbe} = x) = P(n_{dbc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
+	Finally $P(s_{dbe} = x) = P(s_{dbc} = x) = {a(c - 1) \choose x} d^x (1-d)^{a(c- 1) -x}$
 
@@
 	\subsubsection{Simulations}
-	See Figure \ref{corruptth} compares the two choices $w = 1$ and $w = a$.
+	See Figure \ref{corruptth} compares the two choices $\alpha = 1$ and $\alpha = a$.
 	"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
@@
 
-	\section{Resilience}
-	\subsection{Analytical result}
+	\subsection{Resilience}
+	\subsubsection{Analytical result}
 	%Spéculations en Français 
@@
 
-	\subsection{Simulations}
+	\subsubsection{Simulations}
 
@@
 	\begin{figure}[!htb]
-		\includegraphics[width=8.5cm]{Courbes/figpsic8l256e4psi2percent}%thpsi_c8l256e4}
+		\includegraphics[width=8.5cm]{Courbes/fig2psic8l256e4psi2percent}%thpsi_c8l256e4}
 		\caption{$\psi = 0.02$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}

### 2014-07-23 astat.r

@@ -179,6 +179,7 @@ if(!is.null(opt$onlydrop)) { data = subset(data, onlydrop == "true" | pcons == 0
 #im <- with(x, interp(x$c, x$efficiency, x$errorrate))
 #with(im,, image(x$c, x$efficiency, x$errorrate))
 
+#data = subset(data, gamma == 1 & maxiterations == 4 | gamma == 100 & maxiterations == 1)
 
 print("Début plot :")
 print(opt$neurons)
@@ -232,7 +233,7 @@ if(!is.null(opt$size)) {
 		sdata = data[,opt$size]
 	}
 	qpl <- qpl + geom_point(aes(size = sdata)) + labs(size = opt$size) } # + scale_size(name=opt$size)  }
-if(!is.null(opt$shape)) { qpl <- qpl + geom_point(aes(shape = factor(data[,opt$shape])), size = 3) + labs(shape = opt$shape) }# + scale_shape(name=opt$shape)  }
+if(!is.null(opt$shape)) { qpl <- qpl + geom_point(aes(shape = factor(data[,opt$shape])), size = 3) + labs(shape = parse(text = opt$shape)) }# + scale_shape(name=opt$shape)  }
 #if(!is.null(opt$color)) { qpl <- qpl + geom_point(colour = data[opt$color]) }
 
 if(!is.null(opt$nsize)) {
@@ -241,7 +242,7 @@ if(!is.null(opt$nsize)) {
 
 
 if(!is.null(opt$nshape)) {
-	qpl <- qpl + labs(shape = opt$nshape)
+	qpl <- qpl + labs(shape=parse(text = opt$nshape))#shape = opt$nshape)
 }
 
 # Ajouter factor group si besoin est.
@@ -272,10 +273,10 @@ if(!is.null(opt$ordstep)) {
    qpl <- qpl + scale_y_continuous(breaks = seq(0.0, 1.0, by = 0.1))#, max(data[,opt$ord]), by = opt$ordstep))#,#pretty_breaks(n = length(data[,opt$abs]))) #min(data[,opt$ord])
 }
 if(!is.null(opt$xlab)) {
-	qpl <- qpl + xlab(opt$xlab)#expression(psi))#opt$xlab)
+	qpl <- qpl + xlab(opt$xlab)#parse(text = opt$xlab))#expression(psi))#opt$xlab)
 }
 if(!is.null(opt$ylab)) {
[…]

### 2014-07-23 sam.jl

@@ -256,10 +256,10 @@ function create_network(l, c, m, messages, sparseMessages, p_cons = 0.0, degree 
 
 	if p_cons > 0.0
 		for j=1:n
-			for i=1:n
+			for i=(j+1):n
 				if rand(Float64) <= p_cons
 					# Bon opérateur pour faire cette opération sur les booléens et les entiers à la fois ? (Au cas où on changerait le type du réseau.)
-					network[i, j] = (if network[i, j] == 1 || only_drop
+					network[i, j] = network[j, i] = (if network[i, j] == 1 || only_drop
 										0
 									else
 										1
@@ -566,7 +566,11 @@ const real_gamma = (if (gamma == -1) activities elseif (gamma == -2) activities 
 	ipeta = peta / info_alphabet
 	ipaeta = paeta / info_alphabet
 	# Deux mesures importantes
-	rceta = eta * exp(exp2((log2(m-1)- (c-erasures) * info_alphabet)))
+	rceta = eta * (if (fcorrupt == corrupt_clusters!) sum(map([(erasures+1):c]) do k
+						x = 1/binomial(l, activities)
+						binomial(c, k) * (1-x)^k * x^(c - k)
+					end
+		)^(-(m-1)) else  exp(exp2((log2(m-1)- (c-erasures) * info_alphabet))) end)
 	psieta = rceta / (1 + xlog2(p_cons) + xlog2(1-p_cons))
 	return [ res[1] res[2] res[3] l c m real_gamma erasures iterations tests res[4] "$fsum" "$fcorrupt" p_cons p_des degree activities alphabet_size (if winners > 0 winners else activities end) pool_size efficacy (efficacy/cap) proportion eta aeta peta paeta ipeta ipaeta ieta iaeta info_alphabet only_drop rceta psieta csparse ]
 end

### 2014-07-23 Articles/article.tex
...

@@
 	We study the properties of the network once some messages have been stored in it.
-We are interested in how much edges have been added to the network and if the process introduced confusion between messages.
+We are interested in how much edges have been added to the network %and if the process introduced confusion between messages.
 	We also compute the rate of the network in the sense of information theory (ratio between information stored in the network and the information used to store the network)
@@
 	Theoretical and empirical densities match very closely, see Figure \ref{densiteth}. %gap of theoretical density with density in simulations : under $1$ percent, 
-	The higher $a$ is, the quicker density approaches $1$.
-
-	Multipartite cliques saturate quicker, which was expected since they take much more edges.
+	The higher $a$ is, the quicker density approaches $1$ : multipartite cliques saturate quicker, which was expected since they take much more edges ($a^2 \binom{c}{2}$).
 
@@
 	The rate $R$ of the network measures how much information is stored in the network compared to what it takes to store the network itself.
-Note it doesn't take into account how effective messages retrieving is (if we store too much messages in the network, the proportion of retrieved messages approaches $0$ but the rate is high)
+Note it doesn't take into account how effective retrieving messages is (if we store too much messages in the network, the proportion of retrieved messages approaches $0$ but the rate is high)
 
@@
 
-	\subsection{Accepting random messages}
+	%\subsection{Accepting random messages}
 
@@
 
+	\label{pstat}
+
 	We are interested in distinct problems of messages retrieval.
@@
 Efficiency measures the ratio of information effectively retrieved times the hardness of the problem.
-It can be expressed as the product of the rate of the network $R$ (how much information is stored), the retrieval rate $P_{retrieve}$ (how much information is effectively retrieved) and some measure of hardness of the problem $h$ (how hard the problem really is).
+It can be expressed as the product of the rate of the network $R$ (how much information is stored, c.f.
+(\ref{rateth})), the retrieval rate $P_{retrieve}$ (how much is effectively retrieved) and some measure of hardness of the problem $h$ (how hard the problem is).
 	\begin{align}
-		\eta = P_{retrieve} R \cdot h
+		\eta_M = P_{retrieve} R\, h
 		\label{defeff}
 	\end{align}
-
+	However what we are really interested in is the maximum as we want to exploit the network at its best.
+The maximum efficiency attainable with a given retrieving rule, which we will call efficiency, is thereby \begin{align}
+		\eta = \max_{M \ge 1} \eta_M
+		\label{defmaxef}
+	\end{align}
 	To account for hardness of problems, we consider an "optimal" associative memory.
 In this document, we are interested in retrieving messages with a few iterations at most.
-However an "optimal" memory could store $\mathcal{M}$ with $H(\mathcal{M})$ bits and recover messages by maximum likelihood (with ambiguities causing errors in our study, to simplify the problem).
+However an "optimal" memory would store $\mathcal{M}$ with $H(\mathcal{M})$ bits and recover messages by maximum likelihood (with ambiguities causing errors in our study, to simplify the problem).
 For example, such a memory would scan over all messages to find all messages corresponding to a partial probe.
@@
 
-	We compute the probability for a message $m$ and a partial probe $\tilde{m}$ to engender confusion.
+	We compute the probability for a message $m$ and a partial probe $\tilde{m}$ to cause confusion.
 
@@
 	%simulations faites avec erreurs non symétriques !!
+	% mais apparemment cela joue très peu (de toute façon l'erreur théorique concordait avec le résultat des simulations (je suis en train de les refaire)
 
@@
 	\end{align}	
-	, where $H(\psi) = -(\psi \log_2 (\psi) + (1-\psi) \log_2 (1-\psi)$
+	, where $H(\psi) = -(\psi \log_2 (\psi) - (1-\psi) \log_2 (1-\psi)$.
 
@@
 We also compare efficiencies of distinct networks for distinct values of the parameter $a$ (weight of the constant weight code) in the sense of information theory and show improvements over the case where $a = 1$.
+Those efficiencies are computed using the empirical retrieval rate and formulas of section \ref{pstat}.
 
@@
 
-	One can see a partial version of a message $\mu$ as the result of erasures of symbols of $x$.
+	%One can see a partial version of a message $\mu$ as the result of erasures of symbols of $x$.
 Some symbols of $x$ are replaced by the blank character $\intercal$.	Erasures of a symbol in a message corresponds to an "erased" cluster in the network.
@@
 	\begin{align}	
-		P_{err} = 1 - \left(1 - d^	{a(c-c_e)}\right)^{c_e(\ell-a)} 
+		P_{err} = 1 - P_{retrieve} = 1 - \left(1 - d^	{a(c-c_e)}\right)^{c_e(\ell-a)} 
 	\end{align}
 
-	In order to compare distinct networks using distinct alphabets (due to variations of the parameter $a$), we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
+	%In order to compare distinct networks using distinct alphabets (due to variations of the parameter $a$), we define the efficiency of the network relatively to the hardness of the problem (how much it is efficient compared to a perfect associative memory).
 A perfect associative memory would use exactly the same number of bits than the original messages and retrieve messages by maximum likelihood (ambiguities causing errors).
@@
 
-	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) \ell^2}{2}$ bits.
+	%The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) \ell^2}{2}$ bits.
 Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({\ell \choose a}^c)^M}{M!}) \mathop{=}_{M \rightarrow +\infty} M(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula).
@@
 
-	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{\ell \choose a}^{c - c_e})^{M-1}$.
+	%Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{\ell \choose a}^{c - c_e})^{M-1}$.
 
-	$\eta_M = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times (1-(\frac{1}{{\ell \choose a}})^{c - c_e})^{-(M-1)}$
+	%In terms of efficiency, 
+	%$\eta_M = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times (1-(\frac{1}{{\ell \choose a}})^{c - c_e})^{-(M-1)}$
 	%\frac{c}{(c-c_e) \log_2{l \choose a }}
 
-	The maximum ratio of information that can be stored in the network is therefore $\eta = \max_x \eta_x $, which we will define as the efficiency of the network.
+	%The maximum ratio of information that can be stored in the network is therefore $\eta = \max_x \eta_x $, which we will define as the efficiency of the network.
 
@@
 		Simulations agree with the analytical results for error rate, albeit we can observe a small shift, see Figure \ref{erasuresth}.
-The theoretical error rate is a bit optimistic which is due to the connections not being independent.
+The theoretical error rate is slightly optimistic which is due to the connections not being independent.
 
-		 For one iteration, as long as the parameter $w$ is between $1$ and $a$, there is no effect on retrieving (in this setting selecting amounts to take the maximum as all units of the original message achieve the same score).
-However for $4$ iterations, the choice of $\alpha = a$ allows a shift of about $5000$ messages stored on top of those stored for $\alpha = 1$.
-The variant rule can thus be considered a significant improvement over the classic one for multipartite clique networks (recall that $\alpha = 1$ amounts to the classic retrieving rule).
+		 For one iteration, as long as the parameter $\alpha$ is between $1$ and $a$, there is no effect on retrieving (in this setting selecting amounts to take the maximum as all units of the original message achieve the same score).
+However for $4$ iterations, the choice of $\alpha = a$ allows a shift of almost $5000$ messages stored in addition to those stored for $\alpha = 1$.
+The variant rule can thus be considered as a significant improvement over the classic one for multipartite clique networks (recall that $\alpha = 1$ amounts to the classic retrieving rule).
 
@@
 
-	Messages can suffer many types of alteration. Multipartite clique neural networks can also correct errors.
+%	Messages can suffer many types of alteration. Multipartite clique neural networks can also correct errors.
+
+	We now examine the case of retrieving messages from corrupt probes.
 
@@
 	%Correctly activated units in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$.
-	Being connected to a given activated unit in a corrupted cluster occurs with probability $d$, since errors are identically distributed.
-Moreover corrects units see their scores shift, as do all activated units respectively thanks to being part of the original message and the memory effect $\gamma$.
-We can express those probability laws as :
+	We consider $a$ to be small in regard to $\ell$ which allows us to ignore the possibility for a random replacement cluster to share common activated units with the original.
+
+	Corrects units see their scores shift, as do all activated units respectively thanks to being part of the original message and the memory effect $\gamma$.
+	Being connected to a given activated unit in a corrupted cluster occurs with probability $d$, since errors are identically distributed. Moreover  We can express those probability laws as : 
 	For example an \textbf{a}ctivated \textbf{g}ood unit in a \textbf{c}orrect cluster starts with a base score of $ a(c - c_e - 1) + \gamma$.
@@
 
-	$P_{err} = 1 - P_{retrieve}$
+	We can of course compute the error rate : $P_{err} = 1 - P_{retrieve}$
 
 	\subsubsection{Simulations}
-	See Figure \ref{corruptth} compares the two choices $\alpha = 1$ and $\alpha = a$.
-	"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
+	Figure \ref{corruptth} compares the two choices $\alpha = 1$ and $\alpha = a$. The choice of $\alpha = a$ is a considerable improvement over $\alpha = 1$ for retrieving messages from corrupt probe.
+	%"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.
+
+	The analytical error rate is close to the empirical one, albeit slightly optimistic.
 
@@
 
-		$\eta_m = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{\ell \choose a}} \right )^k \left (\frac{1}{{\ell \choose a}} \right )^{c-k} \right ] ^{-(M-1)}$
+		%$\eta_m = P_{retrieve}  \frac{2 M\left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)\ell^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{\ell \choose a}} \right )^k \left (\frac{1}{{\ell \choose a}} \right )^{c-k} \right ] ^{-(M-1)}$
+
+	We now study the influence of the parameter $a$ on retrieving messages from partial probes after the network has sustained damages.
 
@@
 	%gamma = infini meilleur sur une itération
-	We assume $\gamma = \infty$ for one iteration as it prevents activated neurons to be deactivated.
-	With probability $1 - \psi$, one correct vertex is still connected to a given activated unit in an intact cluster.
-Thus $P(n_{v_c} = x ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$
+	We take $\gamma = \infty$ (or big enough) for one iteration as it prevents activated neurons to be deactivated. Another good choice is $\gamma = a$ in practice.
+
+	With probability $1 - \psi$, a correct vertex is still connected to a given activated unit in an intact cluster.
+Thus $P(s_{g} = x ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$
 
@@
 	The probability for an edge to be present in the network after damages is : $P_+ = \psi (1 - d) + (1 - \psi) d$.
-So for other units $P(n_v = x) = {a (c - c_e) \choose x} P_+^x (1-P_+)^{a (c - c_e) -x }$.
+So for other units $P(s_b = x) = {a (c - c_e) \choose x} P_+^x (1-P_+)^{a (c - c_e) -x }$.
 
@@
 
-	The probability for all correct units to achieve a score equal or greater than $x$, with at least one achieving a score of $x$ is $P_c (x) =\sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = x)^k P(n_{v_c} > x)^{a-k} $
+	The probability for all correct units to achieve a score equal or greater than $x$, with at least one achieving a score of $x$ is $P_g (x) =\sum_{k = 1}^{a} { a \choose k }   P(s_g = x)^k P(s_g > x)^{a-k} $
 
 	%If $\gamma$ is big enough,
-	It follows that $P(\mbox{no other vertex activated in one cluster})= \sum_{x = 1}^{a (c - c_e)} P_c(x) P(n_v < x)^{\ell-a}$.%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
+	It follows that $P(\mbox{no other vertex activated in one cluster})= \sum_{x = 1}^{a (c - c_e)} P_g(x) P(s_b < x)^{\ell-a}$.%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$
 
@@
 	\begin{align}
-	P_{retrieve}=  \left( \sum_{x = 1}^{a ( c- c_e)} P_c(x) P(n_v < x)^{\ell-a} \right )^{c_e}
+	P_{retrieve}=  \left( \sum_{x = 1}^{a ( c- c_e)} P_g(x) P(s_b < x)^{\ell-a} \right )^{c_e}
 	\label{psi_formula_th}
@@
 
-	With random noise on edges, hardness of the problem must take into account the capacity of the binary symmetric channel (the closer $\psi$ is of $0.5$, the harder the problem is).
+%	With random noise on edges, hardness of the problem must take into account the capacity of the binary symmetric channel (the closer $\psi$ is of $0.5$, the harder the problem is).
 Our new is efficiency is written as :
-	$\eta_{m, \psi} = P_{retrieve}  \frac{2 M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{\ell \choose a}^{c - c_e})^{-(M-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
-
-	$\eta_\psi = max_x \, \eta_{x, \psi}$
+%	$\eta_{m, \psi} = P_{retrieve}  \frac{2 M \left(c \log_2{\ell \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{\ell \choose a}^{c - c_e})^{-(M-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $
+%	
+%	$\eta_\psi = max_x \, \eta_{x, \psi}$
 	\begin{figure}[!htb]
